\documentclass[a4, landscape, 12pt]{article}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[margin=2cm]{geometry}
\usepackage{amssymb}
\usepackage{pifont}
\usepackage{hyperref}
\newcommand{\cmark}{\ding{51}}%
%\newcommand{\xmark}{\ding{55}}%
\newcommand{\checkbox}{$\square$}%
%\newcommand{\checked}{ \rlap{$\square$}{\hspace{1pt}\cmark} }
\newcommand{\checked}{\rlap{\raisebox{0.3ex}{\hspace{0.4ex}\tiny \ding{52}}}$\square$}
\title{Computer Science and Software Development Roadmap}
\author{Isaac Riley}
\date{Last edited on \today}
\begin{document}
\maketitle
\begin{itemize}
\item [\checkbox]  First Year in Code | \textbf{ 0. Introduction
}
\item [\checkbox]  First Year in Code | \textbf{ 1. Different Learning Pathways into Tech
}
\item [\checkbox]  First Year in Code | \textbf{ 2. How (Not) to Learn
}
\item [\checkbox]  First Year in Code | \textbf{ 3. How to Code (in One Chapter)
}
\item [\checkbox]  First Year in Code | \textbf{ 4. Step to Better Code
}
\item [\checkbox]  First Year in Code | \textbf{ 5. Programming Tools
}
\item [\checkbox]  First Year in Code | \textbf{ 6. You Are an Interpreter
}
\item [\checkbox]  First Year in Code | \textbf{ 7. What to Learn First
}
\item [\checkbox]  First Year in Code | \textbf{ 8. Learning to Learn
}
\item [\checkbox]  First Year in Code | \textbf{ 9. Make the Most of Side Projects
}
\item [\checkbox]  First Year in Code | \textbf{ 10. Getting Your First Job
}
\item [\checkbox]  First Year in Code | \textbf{ 11. My First Job
}
\item [\checkbox]  First Year in Code | \textbf{ 12. I Got My Dream Job. Now What?
}
\item [\checkbox]  First Year in Code | \textbf{ 13. Burnout, Part 1
}
\item [\checkbox]  First Year in Code | \textbf{ 14. Burnout, Part 2
}
\item [\checkbox]  First Year in Code | \textbf{ 15. Do I Fit In?
}
\item [\checkbox]  First Year in Code | \textbf{ 16. Women in Code
}
\item [\checkbox]  First Year in Code | \textbf{ 17. What to Do When You're Stuck
}
\item [\checkbox]  First Year in Code | \textbf{ 18. Choosing a Job Title
}
\item [\checkbox]  First Year in Code | \textbf{ 19. The DevOps Introduction I Wish I Had
}
\item [\checkbox]  First Year in Code | \textbf{ 20. A Coder's Code of Ethics
}
\item [\checkbox]  First Year in Code | \textbf{ 21. Software Development beyond the Keyboard
}
\item [\checkbox]  First Year in Code | \textbf{ 22. Code Reviews
}
\item [\checkbox]  First Year in Code | \textbf{ A. A Coder's Vocabulary 
}
\item [\checkbox]  First Year in Code | \textbf{ B. To Make This, Learn That
}
\item [\checkbox]  First Year in Code | \textbf{ C. Recommended Reading
}
\item [\checkbox]  The Linux Command Line | \textbf{ 1. What Is the Shell?
}
\item [\checkbox]  The Linux Command Line | \textbf{ 2. Navigation
}
\item [\checkbox]  The Linux Command Line | \textbf{ 3. Exploring the System
}
\item [\checkbox]  The Linux Command Line | \textbf{ 4. Manipulating Files and Directories
}
\item [\checkbox]  The Linux Command Line | \textbf{ 5. Working with Commands
}
\item [\checkbox]  The Linux Command Line | \textbf{ 6. Redirection
}
\item [\checkbox]  The Linux Command Line | \textbf{ 7. Seeing the World as the Shell Sees It
}
\item [\checkbox]  The Linux Command Line | \textbf{ 8. Advanced Keyboard Tricks
}
\item [\checkbox]  The Linux Command Line | \textbf{ 9. Permissions
}
\item [\checkbox]  The Linux Command Line | \textbf{ 10. Processes
}
\item [\checkbox]  The Linux Command Line | \textbf{ 11. The Environment
}
\item [\checkbox]  The Linux Command Line | \textbf{ 12. A Gentle Introduction to vi
}
\item [\checkbox]  The Linux Command Line | \textbf{ 13. Customizing the Prompt
}
\item [\checkbox]  The Linux Command Line | \textbf{ 14. Package Management
}
\item [\checkbox]  The Linux Command Line | \textbf{ 15. Storage Media
}
\item [\checkbox]  The Linux Command Line | \textbf{ 16. Networking
}
\item [\checkbox]  The Linux Command Line | \textbf{ 17. Searching for Files
}
\item [\checkbox]  The Linux Command Line | \textbf{ 18. Archiving and Backup
}
\item [\checkbox]  The Linux Command Line | \textbf{ 19. Regular Expressions
}
\item [\checkbox]  The Linux Command Line | \textbf{ 20. Text Processing
}
\item [\checkbox]  The Linux Command Line | \textbf{ 21. Formatting Output
}
\item [\checkbox]  The Linux Command Line | \textbf{ 22. Printing
}
\item [\checkbox]  The Linux Command Line | \textbf{ 23. Compiling Programs
}
\item [\checkbox]  The Linux Command Line | \textbf{ 24. Writing Your First Script
}
\item [\checkbox]  The Linux Command Line | \textbf{ 25. Starting a Project
}
\item [\checkbox]  The Linux Command Line | \textbf{ 26. Top-Down Design
}
\item [\checkbox]  The Linux Command Line | \textbf{ 27. Flow Control: Branching with if
}
\item [\checkbox]  The Linux Command Line | \textbf{ 28. Reading Keyboard Input
}
\item [\checkbox]  The Linux Command Line | \textbf{ 29. Flow Control: Looping with while/until
}
\item [\checkbox]  The Linux Command Line | \textbf{ 30. Troubleshooting
}
\item [\checkbox]  The Linux Command Line | \textbf{ 31. Flow Control: Branching with case
}
\item [\checkbox]  The Linux Command Line | \textbf{ 32. Positional Parameters
}
\item [\checkbox]  The Linux Command Line | \textbf{ 33. Flow Control: Looping with for
}
\item [\checkbox]  The Linux Command Line | \textbf{ 34. Strings and Numbers
}
\item [\checkbox]  The Linux Command Line | \textbf{ 35. Arrays
}
\item [\checkbox]  The Linux Command Line | \textbf{ 36. Exocitica
}
\item [\checkbox]  Learn Vim Tonight | \textbf{ 1. Productivity at the Speed of Vim
}
\item [\checkbox]  Learn Vim Tonight | \textbf{ 2. Installing Vim
}
\item [\checkbox]  Learn Vim Tonight | \textbf{ 3. Running and Exiting Vim
}
\item [\checkbox]  Learn Vim Tonight | \textbf{ 4. Files: Opening, Discarding, Reverting, and Saving
}
\item [\checkbox]  Learn Vim Tonight | \textbf{ 5. Undo and Redo
}
\item [\checkbox]  Learn Vim Tonight | \textbf{ 6. Using Vim Help
}
\item [\checkbox]  Learn Vim Tonight | \textbf{ 7. Using the Vim Tutorial
}
\item [\checkbox]  Learn Vim Tonight | \textbf{ 8. Simple Vim Movements in Edit Mode
}
\item [\checkbox]  Learn Vim Tonight | \textbf{ 9. Insert Mode
}
\item [\checkbox]  Learn Vim Tonight | \textbf{ 10. Simple Edit Mode Commands
}
\item [\checkbox]  Learn Vim Tonight | \textbf{ 11. Search
}
\item [\checkbox]  Learn Vim Tonight | \textbf{ 12. Visual Mode (Highlighting)
}
\item [\checkbox]  Learn Vim Tonight | \textbf{ 13. Cut and Paste
}
\item [\checkbox]  Learn Vim Tonight | \textbf{ 14. Search and Replace Basics
}
\item [\checkbox]  Learn Vim Tonight | \textbf{ 15.ex Mode Basics
}
\item [\checkbox]  Learn Vim Tonight | \textbf{ 16. Editing Multiple Files
}
\item [\checkbox]  Learn Vim Tonight | \textbf{ 17. What Else Can Vim Do?
}
\item [\checkbox]  Learn Vim Tonight | \textbf{ 18.  Now Do It!
}
\item [\checkbox]  Mastering Vim Quickly | \textbf{ 1. Instead of Preface
}
\item [\checkbox]  Mastering Vim Quickly | \textbf{ 2. Introduction
}
\item [\checkbox]  Mastering Vim Quickly | \textbf{ 3. Mastering Vim - Basics
}
\item [\checkbox]  Mastering Vim Quickly | \textbf{ 4. Your First Vim Session
}
\item [\checkbox]  Mastering Vim Quickly | \textbf{ 5. Vim Concepts
}
\item [\checkbox]  Mastering Vim Quickly | \textbf{ 6. Working with Files
}
\item [\checkbox]  Mastering Vim Quickly | \textbf{ 7. Personalizing Vim
}
\item [\checkbox]  Mastering Vim Quickly | \textbf{ 8. Undo and Redo
}
\item [\checkbox]  Mastering Vim Quickly | \textbf{ 9. Do You Speak Vim?
}
\item [\checkbox]  Mastering Vim Quickly | \textbf{ 10. Subsitution
}
\item [\checkbox]  Mastering Vim Quickly | \textbf{ 11. Registers
}
\item [\checkbox]  Mastering Vim Quickly | \textbf{ 12. Buffers
}
\item [\checkbox]  Mastering Vim Quickly | \textbf{ 13. Windows, Tabs, and Sessions
}
\item [\checkbox]  Mastering Vim Quickly | \textbf{ 14. Macros
}
\item [\checkbox]  Mastering Vim Quickly | \textbf{ 15. The Power of Visual Modes
}
\item [\checkbox]  Mastering Vim Quickly | \textbf{ 16. Mappings
}
\item [\checkbox]  Mastering Vim Quickly | \textbf{ 17. Folding
}
\item [\checkbox]  Mastering Vim Quickly | \textbf{ 18. Effective Multiple File Editing
}
\item [\checkbox]  Mastering Vim Quickly | \textbf{ 19. Productivity Tips
}
\item [\checkbox]  Mastering Vim Quickly | \textbf{ 20. Plugins
}
\item [\checkbox]  Mastering Vim Quickly | \textbf{ 21. What Now
}
\item [\checkbox]  \href{https://www.nano-editor.org/dist/latest/cheatsheet.html}{\textbf{Nano Cheatsheet}}

\item [\checkbox]  Nano Docs | \href{https://www.nano-editor.org/dist/latest/nano.html}{\textbf{ 1. Introduction}
}
\item [\checkbox]  Nano Docs | \href{https://www.nano-editor.org/dist/latest/nano.html}{\textbf{ 2. Invoking
}}
\item [\checkbox]  Nano Docs | \href{https://www.nano-editor.org/dist/latest/nano.html}{\textbf{ 3. Command-line Options
}}
\item [\checkbox]  Nano Docs | \href{https://www.nano-editor.org/dist/latest/nano.html}{\textbf{ 4. Editor Basics
}}
\item [\checkbox]  Nano Docs | \href{https://www.nano-editor.org/dist/latest/nano.html}{\textbf{ 5. Built-in Help
}}
\item [\checkbox]  Nano Docs | \href{https://www.nano-editor.org/dist/latest/nano.html}{textbf{ 6. The File Browser
}}
\item [\checkbox]  Nano Docs | \href{https://www.nano-editor.org/dist/latest/nano.html}{\textbf{ 7. Feature Toggles
}}
\item [\checkbox]  Nano Docs | \href{https://www.nano-editor.org/dist/latest/nano.html}{\textbf{ 8. Nanorc Files
}}
\item [\checkbox]  Nano Docs | \href{https://www.nano-editor.org/dist/latest/nano.html}{\textbf{ 9. Pico Compatibility
}}
\item [\checkbox]  Nano Docs | \href{https://www.nano-editor.org/dist/latest/nano.html}{\textbf{ 10. Building and Configure Options
}}
\item [\checkbox]  \href{https://www.gnu.org/software/emacs/tour/}{\textbf{Emacs Tour}
}
\item [\checkbox]  GNU Emacs Manual | \textbf{ 1. Distrib
}
\item [\checkbox]  GNU Emacs Manual | \textbf{ 2. Intro
}
\item [\checkbox]  GNU Emacs Manual | \textbf{ 3. Screen
}
\item [\checkbox]  GNU Emacs Manual | \textbf{ 4. User Input
}
\item [\checkbox]  GNU Emacs Manual | \textbf{ 5. Keys
}
\item [\checkbox]  GNU Emacs Manual | \textbf{ 6. Commands
}
\item [\checkbox]  GNU Emacs Manual | \textbf{ 7. Entering Emacs
}
\item [\checkbox]  GNU Emacs Manual | \textbf{ 8. Exiting
}
\item [\checkbox]  GNU Emacs Manual | \textbf{ 9. Basic
}
\item [\checkbox]  GNU Emacs Manual | \textbf{ 10. Minibuffer
}
\item [\checkbox]  GNU Emacs Manual | \textbf{ 11. M-x
}
\item [\checkbox]  GNU Emacs Manual | \textbf{ 12. Help
}
\item [\checkbox]  GNU Emacs Manual | \textbf{ 13. Mark
}
\item [\checkbox]  GNU Emacs Manual | \textbf{ 14. Killing
}
\item [\checkbox]  GNU Emacs Manual | \textbf{ 15. Registers
}
\item [\checkbox]  GNU Emacs Manual | \textbf{ 16. Display
}
\item [\checkbox]  GNU Emacs Manual | \textbf{ 17. Search
}
\item [\checkbox]  GNU Emacs Manual | \textbf{ 18. Fixit
}
\item [\checkbox]  GNU Emacs Manual | \textbf{ 19. Keyboard Macros
}
\item [\checkbox]  GNU Emacs Manual | \textbf{ 20. Files
}
\item [\checkbox]  GNU Emacs Manual | \textbf{ 21. Buffers
}
\item [\checkbox]  GNU Emacs Manual | \textbf{ 22. Windows
}
\item [\checkbox]  GNU Emacs Manual | \textbf{ 23. Frames
}
\item [\checkbox]  GNU Emacs Manual | \textbf{ 24. International
}
\item [\checkbox]  \href{https://guides.github.com/introduction/git-handbook/}{\textbf{Git Handbook}}

\item [\checkbox]  \href{https://git-scm.com/docs/gittutorial}{\textbf{Git Tutorial}}

\item [\checkbox]  \href{https://learngitbranching.js.org/?locale=es_AR}{\textbf{Learn Git Branching}}

\item [\checkbox]  \href{https://training.github.com/downloads/github-git-cheat-sheet/}{\textbf{Git Cheat Sheet}}

\item [\checkbox]  \href{https://lab.github.com/githubtraining/introduction-to-github}{\textbf{Intro to Github}}

\item [\checkbox]  \href{https://lab.github.com/githubtraining/reviewing-pull-requests}{\textbf{Reviewing Pull Requests}}

\item [\checkbox]  Code (Petzold) | \textbf{ 1. Best Friends
}
\item [\checkbox]  Code (Petzold) | \textbf{ 2. Codes and Combinations
}
\item [\checkbox]  Code (Petzold) | \textbf{ 3. Braille and Binary Codes
}
\item [\checkbox]  Code (Petzold) | \textbf{ 4. Anatomy of a Flashlight
}
\item [\checkbox]  Code (Petzold) | \textbf{ 5. Seeing around Corners
}
\item [\checkbox]  Code (Petzold) | \textbf{ 6. Telegraphs and Relays
}
\item [\checkbox]  Code (Petzold) | \textbf{ 7. Our Ten Digits
}
\item [\checkbox]  Code (Petzold) | \textbf{ 8. Alternatives to Ten
}
\item [\checkbox]  Code (Petzold) | \textbf{ 9. Bit by Bit by Bit
}
\item [\checkbox]  Code (Petzold) | \textbf{ 10. Logic and Switches
}
\item [\checkbox]  Code (Petzold) | \textbf{ 11. Gates (Not Bill)
}
\item [\checkbox]  Code (Petzold) | \textbf{ 12. A Binary Adding Machine
}
\item [\checkbox]  Code (Petzold) | \textbf{ 13. But What about Subtraction?
}
\item [\checkbox]  Code (Petzold) | \textbf{ 14. Feedback and Flip-Flops
}
\item [\checkbox]  Code (Petzold) | \textbf{ 15. Bytes and Hex
}
\item [\checkbox]  Code (Petzold) | \textbf{ 16. An Assemblage of Memory
}
\item [\checkbox]  Code (Petzold) | \textbf{ 17. Automation
}
\item [\checkbox]  Code (Petzold) | \textbf{ 18. From Abaci to Chips
}
\item [\checkbox]  Code (Petzold) | \textbf{ 19. Two Classic Microprocessors
}
\item [\checkbox]  Code (Petzold) | \textbf{ 20. ASCII and a Cast of Characters
}
\item [\checkbox]  Code (Petzold) | \textbf{ 21. Get on the Bus
}
\item [\checkbox]  Code (Petzold) | \textbf{ 22. The Operating System
}
\item [\checkbox]  Code (Petzold) | \textbf{ 23. Fixed Point, Floating Point
}
\item [\checkbox]  Code (Petzold) | \textbf{ 24. Languages High and Low
}
\item [\checkbox]  Code (Petzold) | \textbf{ 25. The Graphical Revolution
}
\item [\checkbox]  Elements of Computing Systems  | \textbf{ 1. Boolean Logic
}
\item [\checkbox]  Elements of Computing Systems  | \textbf{ 2. Boolean Arithmetic
}
\item [\checkbox]  Elements of Computing Systems  | \textbf{ 3. Sequential Logic
}
\item [\checkbox]  Elements of Computing Systems  | \textbf{ 4. Machine Language
}
\item [\checkbox]  Elements of Computing Systems  | \textbf{ 5. Computer Architecture
}
\item [\checkbox]  Elements of Computing Systems  | \textbf{ 6. Assembler
}
\item [\checkbox]  Elements of Computing Systems  | \textbf{ 7. Virtual Machine I: Stack Arithmetic
}
\item [\checkbox]  Elements of Computing Systems  | \textbf{ 8. Virtual Machine II: Program Control
}
\item [\checkbox]  Elements of Computing Systems  | \textbf{ 9. High-Level Language
}
\item [\checkbox]  Elements of Computing Systems  | \textbf{ 10. Compiler I: Syntax Analysis
}
\item [\checkbox]  Elements of Computing Systems  | \textbf{ 11. Compiler II: Code Generation
}
\item [\checkbox]  Elements of Computing Systems  | \textbf{ 12. Operating System
}
\item [\checkbox]  Elements of Computing Systems  | \textbf{ 13. Postscript: More Fun to Go
}
\item [\checkbox]  Elements of Computing Systems  | \textbf{ 14. Appendix A: HDL
}
\item [\checkbox]  Elements of Computing Systems  | \textbf{ 15. Appendix B: Test Scripting Language
}
\item [\checkbox]  Computer Science Distilled | \textbf{ 1 BASICS
}
\item [\checkbox]  Computer Science Distilled | \textbf{ 1.1 Ideas
}
\item [\checkbox]  Computer Science Distilled | \textbf{ 1.2 Logic
}
\item [\checkbox]  Computer Science Distilled | \textbf{ 1.3 Counting
}
\item [\checkbox]  Computer Science Distilled | \textbf{ 1.4 Probability
}
\item [\checkbox]  Computer Science Distilled | \textbf{ 2 COMPLEXITY
}
\item [\checkbox]  Computer Science Distilled | \textbf{ 2.1 Counting Time
}
\item [\checkbox]  Computer Science Distilled | \textbf{ 2.2 The Big-O Notation
}
\item [\checkbox]  Computer Science Distilled | \textbf{ 2.3 Exponentials
}
\item [\checkbox]  Computer Science Distilled | \textbf{ 2.4 Counting Memory
}
\item [\checkbox]  Computer Science Distilled | \textbf{ 3 STRATEGY
}
\item [\checkbox]  Computer Science Distilled | \textbf{ 3.1 Iteration
}
\item [\checkbox]  Computer Science Distilled | \textbf{ 3.2 Recursion
}
\item [\checkbox]  Computer Science Distilled | \textbf{ 3.3 Brute Force
}
\item [\checkbox]  Computer Science Distilled | \textbf{ 3.4 Backtracking
}
\item [\checkbox]  Computer Science Distilled | \textbf{ 3.5 Heuristics
}
\item [\checkbox]  Computer Science Distilled | \textbf{ 3.6 Divide and Conquer
}
\item [\checkbox]  Computer Science Distilled | \textbf{ 3.7 Dynamic Programming
}
\item [\checkbox]  Computer Science Distilled | \textbf{ 3.8 Branch and Bound
}
\item [\checkbox]  Computer Science Distilled | \textbf{ 4 DATA
}
\item [\checkbox]  Computer Science Distilled | \textbf{ 4.1 Abstract Data Types
}
\item [\checkbox]  Computer Science Distilled | \textbf{ 4.2 Common Abstractions
}
\item [\checkbox]  Computer Science Distilled | \textbf{ 4.3 Structures
}
\item [\checkbox]  Computer Science Distilled | \textbf{ 5 ALGORITHMS
}
\item [\checkbox]  Computer Science Distilled | \textbf{ 5.1 Sorting
}
\item [\checkbox]  Computer Science Distilled | \textbf{ 5.2 Searching
}
\item [\checkbox]  Computer Science Distilled | \textbf{ 5.3 Graphs
}
\item [\checkbox]  Computer Science Distilled | \textbf{ 5.4 Operations Research
}
\item [\checkbox]  Computer Science Distilled | \textbf{ 6 DATABASES
}
\item [\checkbox]  Computer Science Distilled | \textbf{ 6.1 Relational
}
\item [\checkbox]  Computer Science Distilled | \textbf{ 6.2 Non-Relational
}
\item [\checkbox]  Computer Science Distilled | \textbf{ 6.3 Distributed
}
\item [\checkbox]  Computer Science Distilled | \textbf{ 6.4 Geographical
}
\item [\checkbox]  Computer Science Distilled | \textbf{ 6.5 Serialization Formats
}
\item [\checkbox]  Computer Science Distilled | \textbf{ 7 COMPUTERS
}
\item [\checkbox]  Computer Science Distilled | \textbf{ 7.1 Architecture
}
\item [\checkbox]  Computer Science Distilled | \textbf{ 7.2 Compilers
}
\item [\checkbox]  Computer Science Distilled | \textbf{ 7.3 Memory Hierarchy
}
\item [\checkbox]  Computer Science Distilled | \textbf{ 8 PROGRAMMING
}
\item [\checkbox]  Computer Science Distilled | \textbf{ 8.1 Linguistics
}
\item [\checkbox]  Computer Science Distilled | \textbf{ 8.2 Variables
}
\item [\checkbox]  Computer Science Distilled | \textbf{ 8.3 Paradigms
}
\item [\checkbox]  Computer Science Distilled | \textbf{ 9. CONCLUSION
}
\item [\checkbox]  Computer Science Distilled | \textbf{ A. Numerical Bases
}
\item [\checkbox]  Computer Science Distilled | \textbf{ B. Gauss’ trick66
}
\item [\checkbox]  Computer Science Distilled | \textbf{ C. Sets67
}
\item [\checkbox]  Computer Science Distilled | \textbf{ D. Kadane’s Algorithm
}
\item [\checkbox]  Computer Systems - A Programmer's Perspective  | \textbf{ 1. A Tour of Computer Systems
}
\item [\checkbox]  Computer Systems - A Programmer's Perspective  | \textbf{ 2. Representing and Manipulating Information
}
\item [\checkbox]  Computer Systems - A Programmer's Perspective  | \textbf{ 3. Machine-Level Representation of Programs
}
\item [\checkbox]  Computer Systems - A Programmer's Perspective  | \textbf{ 4. Processor Architecture
}
\item [\checkbox]  Computer Systems - A Programmer's Perspective  | \textbf{ 5. Optimizing Program Performance
}
\item [\checkbox]  Computer Systems - A Programmer's Perspective  | \textbf{ 6. The Memory Hierarchy
}
\item [\checkbox]  Computer Systems - A Programmer's Perspective  | \textbf{ 7. Linking
}
\item [\checkbox]  Computer Systems - A Programmer's Perspective  | \textbf{ 8. Exceptional Control Flow
}
\item [\checkbox]  Computer Systems - A Programmer's Perspective  | \textbf{ 9. Virtual Memory
}
\item [\checkbox]  Computer Systems - A Programmer's Perspective  | \textbf{ 10. System-Level I/O
}
\item [\checkbox]  Computer Systems - A Programmer's Perspective  | \textbf{ 11. Network Programming
}
\item [\checkbox]  Computer Systems - A Programmer's Perspective  | \textbf{ 12. Concurrent Programming
}
\item [\checkbox]  Write Great Code 1 | \textbf{ 1. What You Need to Know to Write Great Code
}
\item [\checkbox]  Write Great Code 1 | \textbf{ 2. Numeric Representation
}
\item [\checkbox]  Write Great Code 1 | \textbf{ 3. Binary Arithmetic and Bit Operations
}
\item [\checkbox]  Write Great Code 1 | \textbf{ 4. Floating-Point Representation
}
\item [\checkbox]  Write Great Code 1 | \textbf{ 5. Character Representation
}
\item [\checkbox]  Write Great Code 1 | \textbf{ 6. Memory Organization and Access
}
\item [\checkbox]  Write Great Code 1 | \textbf{ 7. Composite Data Types and Memory Objects
}
\item [\checkbox]  Write Great Code 1 | \textbf{ 8. Boolean Logic and Digital Design
}
\item [\checkbox]  Write Great Code 1 | \textbf{ 9. CPU Architecture
}
\item [\checkbox]  Write Great Code 1 | \textbf{ 10. Instruction Set Architecture
}
\item [\checkbox]  Write Great Code 1 | \textbf{ 11. Memory Architecture and Organization
}
\item [\checkbox]  Write Great Code 1 | \textbf{ 12. Input and Output
}
\item [\checkbox]  Write Great Code 1 | \textbf{ 13. Computer Peripheral Buses
}
\item [\checkbox]  Write Great Code 1 | \textbf{ 14. Mass Storage Devices and Filesystems
}
\item [\checkbox]  Write Great Code 1 | \textbf{ 15. Miscellaneous Input and Output Devices
}
\item [\checkbox]  Write Great Code 1 | \textbf{ 16. Thinking Low-Level, Writing High-Level
}
\item [\checkbox]  Write Great Code 1 | \textbf{ A. ASCII Character Set
}
\item [\checkbox]  Write Great Code 2 | \textbf{ 1. Thinking Low-Level, Writing High-Level
}
\item [\checkbox]  Write Great Code 2 | \textbf{ 2. Shouldn’t You Learn Assembly Language?
}
\item [\checkbox]  Write Great Code 2 | \textbf{ 3. 80x86 Assembly for the HLL Programmer
}
\item [\checkbox]  Write Great Code 2 | \textbf{ 4. Compiler Operation and Code Generation
}
\item [\checkbox]  Write Great Code 2 | \textbf{ 5. Tools for Analyzing Compiler Output
}
\item [\checkbox]  Write Great Code 2 | \textbf{ 6. Constants and High-Level Languages
}
\item [\checkbox]  Write Great Code 2 | \textbf{ 7. Variables in a High-Level Language
}
\item [\checkbox]  Write Great Code 2 | \textbf{ 8. Array Data Types
}
\item [\checkbox]  Write Great Code 2 | \textbf{ 9:Pointer Data Types
}
\item [\checkbox]  Write Great Code 2 | \textbf{ 10. String Data Types
}
\item [\checkbox]  Write Great Code 2 | \textbf{ 11. Record, Union, and Class Data Types
}
\item [\checkbox]  Write Great Code 2 | \textbf{ 12. Arithmetic and Logical Expressions
}
\item [\checkbox]  Write Great Code 2 | \textbf{ 13. Control Structures and Programmatic Decisions
}
\item [\checkbox]  Write Great Code 2 | \textbf{ 14. Iterative Control Structures
}
\item [\checkbox]  Write Great Code 2 | \textbf{ 15. Functions and Procedures
}
\item [\checkbox]  Write Great Code 2 | \textbf{ 16. Afterword. Engineering Software
}
\item [\checkbox]  Write Great Code 2 | \textbf{ 17. Glossary
}
\item [\checkbox]  Write Great Code 2 | \textbf{ A. Appendices
}
\item [\checkbox]  How Software Works | \textbf{ 1. Encyption
}
\item [\checkbox]  How Software Works | \textbf{ 2. Passwords
}
\item [\checkbox]  How Software Works | \textbf{ 3. Web Security
}
\item [\checkbox]  How Software Works | \textbf{ 4. Movie CGI
}
\item [\checkbox]  How Software Works | \textbf{ 5. Game Graphics
}
\item [\checkbox]  How Software Works | \textbf{ 6. Data Compression
}
\item [\checkbox]  How Software Works | \textbf{ 7. Search
}
\item [\checkbox]  How Software Works | \textbf{ 8. Concurrency
}
\item [\checkbox]  How Software Works | \textbf{ 9. Map Routes
}
\item [\checkbox]  Computing with Data | \textbf{ 2. Essential Knowledge: Hardware
}
\item [\checkbox]  Computing with Data | \textbf{ 3. Essential Knowledge: Operating Systems
}
\item [\checkbox]  Computing with Data | \textbf{ 4. Learning C++
}
\item [\checkbox]  Computing with Data | \textbf{ 5. Learning Java
}
\item [\checkbox]  Computing with Data | \textbf{ 6. Learning Python and a Few More Things
}
\item [\checkbox]  Computing with Data | \textbf{ 7. Learning R
}
\item [\checkbox]  Computing with Data | \textbf{ 8. Visualizing Data in R and Python
}
\item [\checkbox]  Computing with Data | \textbf{ 9. Processing Data in R and Python
}
\item [\checkbox]  Computing with Data | \textbf{ 10. Essential Knowledge: Parallel Programming
}
\item [\checkbox]  Computing with Data | \textbf{ 11. Essential Knowledge: Testing
}
\item [\checkbox]  Computing with Data | \textbf{ 12. A Few More Things about Programming
}
\item [\checkbox]  Computing with Data | \textbf{ 13. Essential Knowledge: Data Stores
}
\item [\checkbox]  Computing with Data | \textbf{ 14. Thoughts on System Design for Big Data
}
\item [\checkbox]  Computing with Data | \textbf{ 15. Thoughts on Software Craftsmanship
}
\item [\checkbox]  Foundations of Computer Science | \textbf{ 1. Computer Science: The Mechanization of Abstraction
}
\item [\checkbox]  Foundations of Computer Science | \textbf{ 2. Iteration, Induction, and Recursion
}
\item [\checkbox]  Foundations of Computer Science | \textbf{ 3. The Running Time of Programs
}
\item [\checkbox]  Foundations of Computer Science | \textbf{ 4. Combinatorics and Probability
}
\item [\checkbox]  Foundations of Computer Science | \textbf{ 5. The Tree Data Model
}
\item [\checkbox]  Foundations of Computer Science | \textbf{ 6. The List Data Model
}
\item [\checkbox]  Foundations of Computer Science | \textbf{ 7. The Set Data Model
}
\item [\checkbox]  Foundations of Computer Science | \textbf{ 8. The Relational Data Model
}
\item [\checkbox]  Foundations of Computer Science | \textbf{ 9. The Graph Data Model
}
\item [\checkbox]  Foundations of Computer Science | \textbf{ 10. Patterns, Automata, and Regular Expressions
}
\item [\checkbox]  Foundations of Computer Science | \textbf{ 11. Recursive Description Patterns
}
\item [\checkbox]  Foundations of Computer Science | \textbf{ 12. Propositional Logic
}
\item [\checkbox]  Foundations of Computer Science | \textbf{ 13. Using Logic to Design Computer Components
}
\item [\checkbox]  Foundations of Computer Science | \textbf{ 14. Predicate Logic
}
\item [\checkbox]  Structure and Interpretation of Computer Programs  | \textbf{ 1. Building Abstractions with Procedures
}
\item [\checkbox]  Structure and Interpretation of Computer Programs  | \textbf{ 2. Building Abstractions with Data
}
\item [\checkbox]  Structure and Interpretation of Computer Programs  | \textbf{ 3. Modularity, Objects, and State
}
\item [\checkbox]  Structure and Interpretation of Computer Programs  | \textbf{ 4. Metalinguistic Abstraction
}
\item [\checkbox]  Structure and Interpretation of Computer Programs  | \textbf{ 5. Computing with Register Machines
}
\item [\checkbox]  Compilers (Aho et al. 2E)  | \textbf{ 1. Introduction
}
\item [\checkbox]  Compilers (Aho et al. 2E)  | \textbf{ 2. A Simple Syntax-Directed Translator
}
\item [\checkbox]  Compilers (Aho et al. 2E)  | \textbf{ 3. Lexical Analysis
}
\item [\checkbox]  Compilers (Aho et al. 2E)  | \textbf{ 4. Syntax Analysis
}
\item [\checkbox]  Compilers (Aho et al. 2E)  | \textbf{ 5. Syntax-Directed Translation
}
\item [\checkbox]  Compilers (Aho et al. 2E)  | \textbf{ 6. Intermediate-Code Generation
}
\item [\checkbox]  Compilers (Aho et al. 2E)  | \textbf{ 7. Run-Time Environments
}
\item [\checkbox]  Compilers (Aho et al. 2E)  | \textbf{ 8. Code Generation
}
\item [\checkbox]  Compilers (Aho et al. 2E)  | \textbf{ 9. Machine-Independent Optimizations
}
\item [\checkbox]  Compilers (Aho et al. 2E)  | \textbf{ 10. Instruction-Level Parallelism
}
\item [\checkbox]  Compilers (Aho et al. 2E)  | \textbf{ 11. Optimizing for Parallelism and Locality
}
\item [\checkbox]  Compilers (Aho et al. 2E)  | \textbf{ 12. Interprocedural Analysis
}
\item [\checkbox]  Compilers (Aho et al. 2E)  | \textbf{ A. Complete Front End
}
\item [\checkbox]  Compilers (Aho et al. 2E)  | \textbf{ B. Finding Linearly Independent Solutions
}
\item [\checkbox]  Computing Systems (Elahi)  | \textbf{ 1. Signals and Number Systems
}
\item [\checkbox]  Computing Systems (Elahi)  | \textbf{ 2. Boolean Logics and Logic Gates
}
\item [\checkbox]  Computing Systems (Elahi)  | \textbf{ 3. Midterms, MAxterms, Karnaugh Map, and Universal Gates
}
\item [\checkbox]  Computing Systems (Elahi)  | \textbf{ 4. Combinational Logic
}
\item [\checkbox]  Computing Systems (Elahi)  | \textbf{ 5. Synchronous Sequential Logic
}
\item [\checkbox]  Computing Systems (Elahi)  | \textbf{ 6. Introduction to Computer Architecture
}
\item [\checkbox]  Computing Systems (Elahi)  | \textbf{ 7. Memory ☐ CS 8. Assembly Language and ARM Instructions Part I
}
\item [\checkbox]  Computing Systems (Elahi)  | \textbf{ 9. ARM Instructions Part II
}
\item [\checkbox]  Computing Systems (Elahi)  | \textbf{ 10. ARM Assembly Language Programming Using Keil Developing Tools
}
\item [\checkbox]  Linux Bible | \textbf{ 0. Introduction
}
\item [\checkbox]  Linux Bible | \textbf{ 1. Starting with Linux
}
\item [\checkbox]  Linux Bible | \textbf{ 2. Creating the Perfect Linux Desktop
}
\item [\checkbox]  Linux Bible | \textbf{ 3. Using the Shell
}
\item [\checkbox]  Linux Bible | \textbf{ 4. Moving Around the Filesystem
}
\item [\checkbox]  Linux Bible | \textbf{ 5. Working with Text Files
}
\item [\checkbox]  Linux Bible | \textbf{ 6. Managing Running Processes
}
\item [\checkbox]  Linux Bible | \textbf{ 7. Writing Simple Shell Scripts
}
\item [\checkbox]  Linux Bible | \textbf{ 8. Learning System Administration
}
\item [\checkbox]  Linux Bible | \textbf{ 9. Installing Linux
}
\item [\checkbox]  Linux Bible | \textbf{ 10. Getting and Managing Software
}
\item [\checkbox]  Linux Bible | \textbf{ 11. Managing User Accounts
}
\item [\checkbox]  Linux Bible | \textbf{ 12. Managing Disks and Filesystems
}
\item [\checkbox]  Linux Bible | \textbf{ 13. Understanding Server Administration
}
\item [\checkbox]  Linux Bible | \textbf{ 14. Administering Networking
}
\item [\checkbox]  Linux Bible | \textbf{ 15. Starting and Stopping Services
}
\item [\checkbox]  Linux Bible | \textbf{ 16. Configuring a Print Server
}
\item [\checkbox]  Linux Bible | \textbf{ 17. Configuring a Web Server
}
\item [\checkbox]  Linux Bible | \textbf{ 18. Configuring an FTP Server
}
\item [\checkbox]  Linux Bible | \textbf{ 19. Configuring a Windows File Sharing (Samba) Server
}
\item [\checkbox]  Linux Bible | \textbf{ 20. Configuring an NFS File Server
}
\item [\checkbox]  Linux Bible | \textbf{ 21. Troubleshooting Linux
}
\item [\checkbox]  Linux Bible | \textbf{ 22. Understanding Basic Linux Security
}
\item [\checkbox]  Linux Bible | \textbf{ 23. Understanding Advanced Linux Security
}
\item [\checkbox]  Linux Bible | \textbf{ 24. Enhancing Linux Security with SELinux
}
\item [\checkbox]  Linux Bible | \textbf{ 25. Securing Linux on a Network
}
\item [\checkbox]  Linux Bible | \textbf{ 26. Shifting to Clouds and Containers
}
\item [\checkbox]  Linux Bible | \textbf{ 27. Using Linux for Cloud Computing
}
\item [\checkbox]  Linux Bible | \textbf{ 28. Deploying Linux to the Cloud
}
\item [\checkbox]  Linux Bible | \textbf{ 29. Automating Apps and Infrastructure with Ansible
}
\item [\checkbox]  Linux Bible | \textbf{ 30. Deploying Applications as Containers with Kubernetes
}
\item [\checkbox]  Linux Bible | \textbf{ A. Media
}
\item [\checkbox]  Linux Bible | \textbf{ B. Exercise Answers
}
\item [\checkbox]  Introduction to Digital Electronics | \textbf{ 1. Fundamentals
}
\item [\checkbox]  Introduction to Digital Electronics | \textbf{ 2. Arithmetic and Digital Electronics
}
\item [\checkbox]  Introduction to Digital Electronics | \textbf{ 3. Combinatorial Logic Basics
}
\item [\checkbox]  Introduction to Digital Electronics | \textbf{ 4. Combinatorial Logic Circuits
}
\item [\checkbox]  Introduction to Digital Electronics | \textbf{ 5. Asynchronous Sequential Logic
}
\item [\checkbox]  Introduction to Digital Electronics | \textbf{ 6. Flip-Flops and Flip-Flop Based Circuits
}
\item [\checkbox]  Introduction to Digital Electronics | \textbf{ 7. Counters
}
\item [\checkbox]  Introduction to Digital Electronics | \textbf{ 8. Synchronous Sequential Circuits
}
\item [\checkbox]  Introduction to Digital Electronics | \textbf{ 9. Choosing a Means of Implementation
}
\item [\checkbox]  Introduction to Digital Electronics | \textbf{ 10. Semiconductor Memories
}
\item [\checkbox]  Introduction to Digital Electronics | \textbf{ 11. Selecting a Design Route
}
\item [\checkbox]  Introduction to Digital Electronics | \textbf{ 12. Answers
}
\item [\checkbox]  How to Design, Build and Program Your Own Working Computer System  | \textbf{ 1. The Basic Approach
}
\item [\checkbox]  How to Design, Build and Program Your Own Working Computer System  | \textbf{ 2. Main-Frame Construction
}
\item [\checkbox]  How to Design, Build and Program Your Own Working Computer System  | \textbf{ 3. The Central Processor
}
\item [\checkbox]  How to Design, Build and Program Your Own Working Computer System  | \textbf{ 4. The Control Panel & First System Test
}
\item [\checkbox]  How to Design, Build and Program Your Own Working Computer System  | \textbf{ 5. The Read/Write Memory Board
}
\item [\checkbox]  How to Design, Build and Program Your Own Working Computer System  | \textbf{ 6. A Serial I/O Board
}
\item [\checkbox]  How to Design, Build and Program Your Own Working Computer System  | \textbf{ 7. Read-Only Memory Cards
}
\item [\checkbox]  How to Design, Build and Program Your Own Working Computer System  | \textbf{ 8. Expanding Your Computer
}
\item [\checkbox]  Digital Computer Electronics | \textbf{ 1. Digital Principles
}
\item [\checkbox]  Digital Computer Electronics | \textbf{ 2. Gates
}
\item [\checkbox]  Digital Computer Electronics | \textbf{ 3. More Logic Gates
}
\item [\checkbox]  Digital Computer Electronics | \textbf{ 4. TTL Circuits
}
\item [\checkbox]  Digital Computer Electronics | \textbf{ 5. Boolean algebra and Karnaugh Maps
}
\item [\checkbox]  Digital Computer Electronics | \textbf{ 6. Arithmetic-Logic Units
}
\item [\checkbox]  Digital Computer Electronics | \textbf{ 7. Flip-Flops
}
\item [\checkbox]  Digital Computer Electronics | \textbf{ 8. Registers and Counters
}
\item [\checkbox]  Digital Computer Electronics | \textbf{ 9. Memories
}
\item [\checkbox]  Digital Computer Electronics | \textbf{ 10. SAP-1
}
\item [\checkbox]  Digital Computer Electronics | \textbf{ 11. SAP-2
}
\item [\checkbox]  Digital Computer Electronics | \textbf{ 12. SAP-3
}
\item [\checkbox]  Digital Computer Electronics | \textbf{ 13. Introduction to Microprocessors
}
\item [\checkbox]  Digital Computer Electronics | \textbf{ 14. Programming and Languages
}
\item [\checkbox]  Digital Computer Electronics | \textbf{ 15. System Overview
}
\item [\checkbox]  Digital Computer Electronics | \textbf{ 16. Data Transfer Instructions
}
\item [\checkbox]  Digital Computer Electronics | \textbf{ 17. Addressing Modes - I
}
\item [\checkbox]  Digital Computer Electronics | \textbf{ 18. Arithmetic and Flags
}
\item [\checkbox]  Digital Computer Electronics | \textbf{ 19. Logical Instructions
}
\item [\checkbox]  Digital Computer Electronics | \textbf{ 20. Shift and Rotate Instructions
}
\item [\checkbox]  Digital Computer Electronics | \textbf{ 21. Addressing Modes - 2
}
\item [\checkbox]  Digital Computer Electronics | \textbf{ 22. Branching and Loops
}
\item [\checkbox]  Digital Computer Electronics | \textbf{ 23. Subroutine and Stack Instructions
}
\item [\checkbox]  Digital Computer Electronics | \textbf{ 24. Microprocessor Instruction Set Tables
}
\item [\checkbox]  Digital Computer Electronics | \textbf{ A. Appendices
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 1. Inductive Sets of Data
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 1.1. Recursively Specified Data
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 1.2. Deriving Recursive Programs
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 1.3. Auxiliary Procedures and Context Arguments
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 1.4. Exercises
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 2. Data Abstraction
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 2.1. Specifying Data via Interfaces
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 2.2. Representation Strategies for Data Types
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 2.3. Interfaces for Recursive Data Types
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 2.4. A Tool for Defining Recursive Data Types
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 2.5. Abstract Syntax and Its Representation
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 3. Expressions
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 3.1. Specification and Implementation Strategy
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 3.2. LET: A Simple Language
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 3.3. PROC: A Language with Procedures
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 3.4. LETREC: A Language with Recursive Procedures
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 3.5. Scoping and Binding of Variables
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 3.6. Eliminating Variable Names
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 3.7. Implementing Lexical Addressing
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 4. State
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 4.1. Computational Effects
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 4.2. EXPLICIT-REFS: A Language with Explicit References
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 4.3. IMPLICIT-REFS: A Language with Implicit References
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 4.4. MUTABLE-PAIRS: A Language with Mutable Pairs
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 4.5. Parameter-Passing Variations
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 5. Continuation-Passing Interpreters
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 5.1. A Continuation-Passing Interpreter
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 5.2. A Trampolined Interpreter
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 5.3. An Imperative Interpreter
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 5.4. Exceptions
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 5.5. Threads
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 6. Continuation-Passing Style
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 6.1. Writing Programs in Continuation-Passing Style
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 6.2. Tail Form
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 6.3. Converting to Continuation-Passing Style
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 6.4. Modeling Computational Effects
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 7. Types
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 7.1. Values and Their Types
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 7.2. Assigning a Type to an Expression
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 7.3. CHECKED: A Type-Checked Language
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 7.4. INFERRED: A Language with Type Inference
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 8. Modules
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 8.1. The Simple Module System
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 8.2. Modules That Declare Types
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 8.3. Module Procedures
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 9. Objects and Classes
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 9.1. Object-Oriented Programming
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 9.2. Inheritance
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 9.3. The Language
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 9.4. The Interpreter
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 9.5. A Typed Language
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ 9.6. The Type Checker
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ A. For Further Reading
}
\item [\checkbox]  Essentials of Programming Languages | \textbf{ B. The SLLGEN Parsing System
}
\item [\checkbox]  The Healthy Programmer | \textbf{ 0. Preface
}
\item [\checkbox]  The Healthy Programmer | \textbf{ 1. Making Changes
}
\item [\checkbox]  The Healthy Programmer | \textbf{ 2. Bootstrapping Your Health
}
\item [\checkbox]  The Healthy Programmer | \textbf{ 3. A Farewell to Chairs?
}
\item [\checkbox]  The Healthy Programmer | \textbf{ 4. Agile Dieting
}
\item [\checkbox]  The Healthy Programmer | \textbf{ 5. Preventing Headaches and Eye Strain
}
\item [\checkbox]  The Healthy Programmer | \textbf{ 6. Preventing Back Pain
}
\item [\checkbox]  The Healthy Programmer | \textbf{ 7. Preventing Wrist Pain
}
\item [\checkbox]  The Healthy Programmer | \textbf{ 8. Making Exercise Pragmatic
}
\item [\checkbox]  The Healthy Programmer | \textbf{ 9. Thinking Outside the Cube
}
\item [\checkbox]  The Healthy Programmer | \textbf{ 10. Refactoring Your Fitness
}
\item [\checkbox]  The Healthy Programmer | \textbf{ 11. Teaming Up
}
\item [\checkbox]  The Healthy Programmer | \textbf{ 12. Onward, Healthy Programmer
}
\item [\checkbox]  The Healthy Programmer | \textbf{ A1. Goals
}
\item [\checkbox]  The Healthy Programmer | \textbf{ A2. Examples
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ I Practical Algorithm Design
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 1 Introduction to Algorithm Design
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 1.1 Robot Tour Optimization
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 1.2 Selecting the Right Jobs
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 1.3 Reasoning about Correctness
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 1.4 Modeling the Problem
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 1.5 About the War Stories
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 1.6 War Story: Psychic Modeling
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 1.7 Exercises
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 2 Algorithm Analysis
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 2.1 The RAM Model of Computation
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 2.2 The Big Oh Notation
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 2.3 Growth Rates and Dominance Relations
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 2.4 Working with the Big Oh
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 2.5 Reasoning About Efficiency
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 2.6 Logarithms and Their Applications
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 2.7 Properties of Logarithms
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 2.8 War Story: Mystery of the Pyramids
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 2.9 Advanced Analysis (*)
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 2.10 Exercises
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 3 Data Structures
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 3.1 Contiguous vs. Linked Data Structures
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 3.2 Stacks and Queues
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 3.3 Dictionaries
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 3.4 Binary Search Trees
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 3.5 Priority Queues
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 3.6 War Story: Striping Triangulations
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 3.7 Hashing and Strings
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 3.8 Specialized Data Structures
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 3.9 War Story: String ’em Up
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 3.10 Exercises
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 4 Sorting and Searching
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 4.1 Applications of Sorting
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 4.2 Pragmatics of Sorting
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 4.3 Heapsort: Fast Sorting via Data Structures
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 4.4 War Story: Give me a Ticket on an Airplane
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 4.5 Mergesort: Sorting by Divide-and-Conquer
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 4.6 Quicksort: Sorting by Randomization
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 4.7 Distribution Sort: Sorting via Bucketing
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 4.8 War Story: Skiena for the Defense
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 4.9 Binary Search and Related Algorithms
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 4.10 Divide-and-Conquer
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 4.11 Exercises
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 5 Graph Traversal
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 5.1 Flavors of Graphs
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 5.2 Data Structures for Graphs
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 5.3 War Story: I was a Victim of Moore’s Law
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 5.4 War Story: Getting the Graph
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 5.5 Traversing a Graph
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 5.6 Breadth-First Search
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 5.7 Applications of Breadth-First Search
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 5.8 Depth-First Search
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 5.9 Applications of Depth-First Search
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 5.10 Depth-First Search on Directed Graphs
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 5.11 Exercises
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 6 Weighted Graph Algorithms
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 6.1 Minimum Spanning Trees
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 6.2 War Story: Nothing but Nets
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 6.3 Shortest Paths
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 6.4 War Story: Dialing for Documents
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 6.5 Network Flows and Bipartite Matching
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 6.6 Design Graphs, Not Algorithms
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 6.7 Exercises
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 7 Combinatorial Search and Heuristic Methods
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 7.1 Backtracking
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 7.2 Search Pruning
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 7.3 Sudoku
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 7.4 War Story: Covering Chessboards
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 7.5 Heuristic Search Methods
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 7.6 War Story: Only it is Not a Radio
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 7.7 War Story: Annealing Arrays
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 7.8 Other Heuristic Search Methods
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 7.9 Parallel Algorithms
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 7.10 War Story: Going Nowhere Fast
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 7.11 Exercises
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 8 Dynamic Programming
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 8.1 Caching vs. Computation
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 8.2 Approximate String Matching
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 8.3 Longest Increasing Sequence
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 8.4 War Story: Evolution of the Lobster
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 8.5 The Partition Problem
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 8.6 Parsing Context-Free Grammars
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 8.7 Limitations of Dynamic Programming: TSP
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 8.8 War Story: What’s Past is Prolog
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 8.9 War Story: Text Compression for Bar Codes
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 8.10 Exercises
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 9 Intractable Problems and Approximation Algorithms
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 9.1 Problems and Reductions
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 9.2 Reductions for Algorithms
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 9.3 Elementary Hardness Reductions
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 9.4 Satisfiability
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 9.5 Creative Reductions
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 9.6 The Art of Proving Hardness
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 9.7 War Story: Hard Against the Clock
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 9.8 War Story: And Then I Failed
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 9.9 P vs. NP
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 9.10 Dealing with NP-complete Problems
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 9.11 Exercises
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 10 How to Design Algorithms
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ II The Hitchhiker’s Guide to Algorithms
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 11 A Catalog of Algorithmic Problems
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 12 Data Structures
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 12.1 Dictionaries
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 12.2 Priority Queues
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 12.3 Suffix Trees and Arrays
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 12.4 Graph Data Structures
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 12.5 Set Data Structures
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 12.6 Kd-Trees
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 13 Numerical Problems
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 13.1 Solving Linear Equations
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 13.2 Bandwidth Reduction
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 13.3 Matrix Multiplication
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 13.4 Determinants and Permanents
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 13.5 Constrained and Unconstrained Optimization
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 13.6 Linear Programming
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 13.7 Random Number Generation
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 13.8 Factoring and Primality Testing
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 13.9 Arbitrary-Precision Arithmetic
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 13.10 Knapsack Problem
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 13.11 Discrete Fourier Transform
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 14 Combinatorial Problems
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 14.1 Sorting
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 14.2 Searching
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 14.3 Median and Selection
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 14.4 Generating Permutations
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 14.5 Generating Subsets
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 14.6 Generating Partitions
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 14.7 Generating Graphs
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 14.8 Calendrical Calculations
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 14.9 Job Scheduling
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 14.10 Satisfiability
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 15 Graph Problems: Polynomial-Time
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 15.1 Connected Components
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 15.2 Topological Sorting
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 15.3 Minimum Spanning Tree
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 15.4 Shortest Path
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 15.5 Transitive Closure and Reduction
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 15.6 Matching
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 15.7 Eulerian Cycle/Chinese Postman
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 15.8 Edge and Vertex Connectivity
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 15.9 Network Flow
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 15.10 Drawing Graphs Nicely
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 15.11 Drawing Trees
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 15.12 Planarity Detection and Embedding
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 16 Graph Problems: Hard Problems
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 16.1 Clique
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 16.2 Independent Set
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 16.3 Vertex Cover
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 16.4 Traveling Salesman Problem
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 16.5 Hamiltonian Cycle
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 16.6 Graph Partition
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 16.7 Vertex Coloring
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 16.8 Edge Coloring
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 16.9 Graph Isomorphism
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 16.10 Steiner Tree
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 16.11 Feedback Edge/Vertex Set
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 17 Computational Geometry
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 17.1 Robust Geometric Primitives
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 17.2 Convex Hull
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 17.3 Triangulation
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 17.4 Voronoi Diagrams
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 17.5 Nearest Neighbor Search
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 17.6 Range Search
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 17.7 Point Location
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 17.8 Intersection Detection
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 17.9 Bin Packing
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 17.10 Medial-Axis Transform
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 17.11 Polygon Partitioning
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 17.12 Simplifying Polygons
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 17.13 Shape Similarity
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 17.14 Motion Planning
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 17.15 Maintaining Line Arrangements
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 17.16 Minkowski Sum
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 18 Set and String Problems
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 18.1 Set Cover
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 18.2 Set Packing
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 18.3 String Matching
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 18.4 Approximate String Matching
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 18.5 Text Compression
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 18.6 Cryptography
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 18.7 Finite State Machine Minimization
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 18.8 Longest Common Substring/Subsequence
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 18.9 Shortest Common Superstring
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 19 Algorithmic Resources
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 19.1 Software Systems
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 19.2 Data Sources
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 19.3 Online Bibliographic Resources
}
\item [\checkbox]  The Algorithm Design Manual | \textbf{ 19.4 Professional Consulting Services
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 0. Introduction
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 1. The Role of Algorithms in Computing
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 1.1. Algorithms
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 1.2. Algorithms as a technology
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 2. Getting Started
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 2.1. Insertion sort
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 2.2. Analyzing algorithms
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 2.3. Designing algorithms
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 3. Growth of Functions
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 3.1. Asymptotic notation
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 3.2. Standard notations and common functions
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 4. Divide-and-Conquer
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 4.1. The maximum-subarray problem
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 4.2. Strassen’s algorithm for matrix multiplication
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 4.3. The substitution method for solving recurrences
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 4.4. The recursion-tree method for solving recurrences
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 4.5. The master method for solving recurrences
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 4.6. Proof of the master theorem
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 5. Probabilistic Analysis and Randomized Algorithms
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 5.1. The hiring problem
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 5.2. Indicator random variables
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 5.3. Randomized algorithms
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 5.4. Probabilistic analysis and further uses of indicator random variables
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 6. Heapsort
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 6.1. Heaps
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 6.2. Maintaining the heap property
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 6.3. Building a heap
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 6.4. The heapsort algorithm
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 6.5. Priority queues
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 7. Quicksort
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 7.1. Description of quicksort
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 7.2. Performance of quicksort
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 7.3. A randomized version of quicksort
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 7.4. Analysis of quicksort
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 8. Sorting in Linear Time
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 8.1. Lower bounds for sorting
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 8.2. Counting sort
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 8.3. Radix sort
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 8.4. Bucket sort
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 9. Medians and Order Statistics
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 9.1. Minimum and maximum
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 9.2. Selection in expected linear time
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 9.3. Selection in worst-case linear time
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 10. Elementary Data Structures
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 10.1. Stacks and queues
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 10.2. Linked lists
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 10.3. Implementing pointers and objects
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 10.4. Representing rooted trees
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 11. Hash Tables
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 11.1. Direct-address tables
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 11.2. Hash tables
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 11.3. Hash functions
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 11.4. Open addressing
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 11.5. Perfect hashing
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 12. Binary Search Trees
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 12.1. What is a binary search tree?
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 12.2. Querying a binary search tree
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 12.3. Insertion and deletion
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 12.4. Randomly built binary search trees
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 13. Red-Black Trees
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 13.1. Properties of red-black trees
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 13.2. Rotations
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 13.3. Insertion
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 13.4. Deletion
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 14. Augmenting Data Structures
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 14.1. Dynamic order statistics
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 14.2. How to augment a data structure
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 14.3. Interval trees
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 15. Dynamic Programming
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 15.1. Rod cutting
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 15.2. Matrix-chain multiplication
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 15.3. Elements of dynamic programming
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 15.4. Longest common subsequence
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 15.5. Optimal binary search trees
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 16. Greedy Algorithms
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 16.1. An activity-selection problem
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 16.2. Elements of the greedy strategy
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 16.3. Huffman codes
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 16.4. Matroids and greedy methods
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 16.5. A task-scheduling problem as a matroid
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 17. Amortized Analysis
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 17.1. Aggregate analysis
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 17.2. The accounting method
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 17.3. The potential method
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 17.4. Dynamic tables
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 18. B-Trees
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 18.1. Definition of B-trees
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 18.2. Basic operations on B-trees
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 18.3. Deleting a key from a B-tree
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 19. Fibonacci Heaps
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 19.1. Structure of Fibonacci heaps
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 19.2. Mergeable-heap operations
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 19.3. Decreasing a key and deleting a node
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 19.4. Bounding the maximum degree
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 20. van Emde Boas Trees
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 20.1. Preliminary approaches
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 20.2. A recursive structure
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 20.3. The van Emde Boas tree
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 21. Data Structures for Disjoint Sets
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 21.1. Disjoint-set operations
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 21.2. Linked-list representation of disjoint sets
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 21.3. Disjoint-set forests
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 21.4. Analysis of union by rank with path compression
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 22. Elementary Graph Algorithms
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 22.1. Representations of graphs
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 22.2. Breadth-first search
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 22.3. Depth-first search
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 22.4. Topological sort
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 22.5. Strongly connected components
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 23. Minimum Spanning Trees
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 23.1. Growing a minimum spanning tree
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 23.2. The algorithms of Kruskal and Prim
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 24. Single-Source Shortest Paths
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 24.1. The Bellman-Ford algorithm
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 24.2. Single-source shortest paths in directed acyclic graphs
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 24.3. Dijkstra’s algorithm
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 24.4. Difference constraints and shortest paths
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 24.5. Proofs of shortest-paths properties
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 25. All-Pairs Shortest Paths
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 25.1. Shortest paths and matrix multiplication
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 25.2. The Floyd-Warshall algorithm
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 25.3. Johnson’s algorithm for sparse graphs
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 26. Maximum Flow
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 26.1. Flow networks
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 26.2. The Ford-Fulkerson method
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 26.3. Maximum bipartite matching
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 26.4. Push-relabel algorithms
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 26.5. The relabel-to-front algorithm
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 27. Multithreaded Algorithms
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 27.1. The basics of dynamic multithreading
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 27.2. Multithreaded matrix multiplication
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 27.3. Multithreaded merge sort
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 28. Matrix Operations
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 28.1. Solving systems of linear equations
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 28.2. Inverting matrices
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 28.3. Symmetric positive-definite matrices and least-squares approximation
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 29. Linear Programming
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 29.1. Standard and slack forms
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 29.2. Formulating problems as linear programs
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 29.3. The simplex algorithm
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 29.4. Duality
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 29.5. The initial basic feasible solution
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 30. Polynomials and the FFT
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 30.1. Representing polynomials
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 30.2. The DFT and FFT
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 30.3. Efficient FFT implementations
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 31. Number-Theoretic Algorithms
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 31.1. Elementary number-theoretic notions
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 31.2. Greatest common divisor
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 31.3. Modular arithmetic
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 31.4. Solving modular linear equations
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 31.5. The Chinese remainder theorem
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 31.6. Powers of an element
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 31.7. The RSA public-key cryptosystem
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 31.8. Primality testing
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 31.9. Integer factorization
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 32. String Matching
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 32.1. The naive string-matching algorithm
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 32.2. The Rabin-Karp algorithm
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 32.3. String matching with finite automata
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 32.4. The Knuth-Morris-Pratt algorithm
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 33. Computational Geometry
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 33.1. Line-segment properties
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 33.2. Determining whether any pair of segments intersects
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 33.3. Finding the convex hull
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 33.4 Finding the closest pair of points
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 34. NP-Completeness
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 34.1. Polynomial time
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 34.2. Polynomial-time verification
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 34.3. NP-completeness and reducibility
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 34.4. NP-completeness proofs
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 34.5. NP-complete problems
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 35. Approximation Algorithms
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 35.1. The vertex-cover problem
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 35.2. The traveling-salesman problem
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 35.3. The set-covering problem
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 35.4. Randomization and linear programming
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ 35.5. The subset-sum problem
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ A. Summations
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ B. Sets, Etc.
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ C. Counting and Probability
}
\item [\checkbox]  Introduction to Algorithms | \textbf{ D. Matrices
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 1. Preliminaries
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 1.1. Machine Models
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 1.1.1. Turing Machine Model
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 1.1.2. RAM Model
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 1.1.3. Other Machine Models
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 1.2. Efficiency of Algorithm
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 1.2.1. Evaluation of Algorithms on Turing 
Machine Model

\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 1.2.2. Evaluation of Algorithms on RAM Model
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 1.2.3. Evaluation of Algorithms on Other Models
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 1.2.4. Computational Complexity in the Worst Case
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 1.3. Data Structures
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 1.3.1. Variable
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 1.3.2. Array
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 1.3.3. Multi-dimensional Array
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 1.3.4. Queues and Stacks
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 1.4. The Big-O Notation and Related Notations
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 1.4.1. Warning
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 1.4.2. Big-O Notation
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 1.4.3. Other Notations Related to the Big-O Notation
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 1.5. Polynomial, Exponential, and Logarithmic Functions
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 1.5.1. Harmonic Number
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 1.6. Graph
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 1.6.1. Representations of a Graph
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 2. Recursive Call
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 2.1. Tower of Hanoi
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 2.1.1. Analysis of the Tower of Hanoi
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 2.1.2. Recurrent Call Mechanism
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 2.2. Fibonacci Numbers
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 2.2.1. Computing Fibonacci Numbers FðnÞ 
}
\item [\checkbox]  Arising from Recursive Calls
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 2.2.2. Execution Time of Fibr Based on Recursive Calls
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 2.2.3. Fast Method for Computing Fibonacci Numbers
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 2.2.4. Extremely Fast Method to Compute Fibonacci Numbers
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 2.3. Divide-and-Conquer and Dynamic Programming
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 3. Algorithms for Searching and Sorting
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 3.1. Searching
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 3.1.1. Linear Search and Its Running Time
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 3.1.2. Searching in Pre-sorted Data
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 3.1.3. Block Search and Its Analysis
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 3.1.4. From Recursion to Binary Search
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 3.2. Hashing
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 3.3. Sorting
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 3.3.1. Bubble Sort
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 3.3.2. Merge Sort
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 3.3.3. Quick Sort
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 3.3.4. Analyses and Properties of Sorting
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 3.3.5. Essential Complexity of Sorting
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 3.3.6. Extremely Fast Bucket Sort and Machine Model
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 4. Searching on Graphs
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 4.1. Problems on Graphs
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 4.2. Reachability: Depth-First Search on Graphs
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 4.2.1 Search Trees and Depth-First Search
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 4.3. Shortest Paths: Breadth-First Search on Graphs
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 4.4. Lowest Cost Paths: Searching on Graphs Using Dijkstra’s Algorithm
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 4.4.1. Implementations of Dijkstra’s Algorithm
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 4.4.2. Analysis of Dijkstra’s Algorithm
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 5. Backtracking
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 5.1. The Eight Queen Puzzle
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 5.1.1. Case Study
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 5.1.2. Case Study
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 5.1.3. Backtracking Algorithm and Its Analysis
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 5.2. Knight’s Tour
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 5.2.1. Case Study
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 5.2.2. Case Study
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 5.2.3. Case Study
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 5.2.4. Knight Tours on Board of Size
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 6. Randomized Algorithms
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 6.1. Random Numbers
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 6.2. Shuffling Problem
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 6.2.1. Naive Algorithm
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 6.2.2. Elegant Algorithm
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 6.3. Coupon Collector’s Problem
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 7. References
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 7.1. For Beginners
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 7.2. For Intermediates
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 7.3. For Experts
}
\item [\checkbox]  First Course in Algorithms through Puzzles | \textbf{ 8. Answers to Exercises
}
\item [\checkbox]  The Docker Handbook | \textbf{ 1. Introduction to Containerization and Docker
}
\item [\checkbox]  The Docker Handbook | \textbf{ 2. How to Install Docker
}
\item [\checkbox]  The Docker Handbook | \textbf{ 3. Hello World in Docker - Intro to Docker Basics
}
\item [\checkbox]  The Docker Handbook | \textbf{ 4. Docker Container Manipulation Basics
}
\item [\checkbox]  The Docker Handbook | \textbf{ 5. Docker Image Manipulation Basics
}
\item [\checkbox]  The Docker Handbook | \textbf{ 6. How to Containerize a JavaScript Application
}
\item [\checkbox]  The Docker Handbook | \textbf{ 7. Network Manipulation Basics in Docker
}
\item [\checkbox]  The Docker Handbook | \textbf{ 8. How to Containerize a Multi-Container JavaScript Application
}
\item [\checkbox]  The Docker Handbook | \textbf{ 9. How to Compose Projects Using Docker-Compose
}
\item [\checkbox]  The Docker Handbook | \textbf{ 10. Conclusion
}
\item [\checkbox]  Learn Docker in a Month of Lunches | \textbf{ 1. Before You Begin
}
\item [\checkbox]  Learn Docker in a Month of Lunches | \textbf{ 2. Understanding Docker and Running Hello World
}
\item [\checkbox]  Learn Docker in a Month of Lunches | \textbf{ 3. Building Your Own Docker Images
}
\item [\checkbox]  Learn Docker in a Month of Lunches | \textbf{ 4. Packaging Applications from Source Code to Docker Images
}
\item [\checkbox]  Learn Docker in a Month of Lunches | \textbf{ 5. Sharing Images with Docker Hub and Other Registries
}
\item [\checkbox]  Learn Docker in a Month of Lunches | \textbf{ 6. Using Docker Volumes for Persistent Storage
}
\item [\checkbox]  Learn Docker in a Month of Lunches | \textbf{ 7. Running Multi-Container Apps with Docker Compose
}
\item [\checkbox]  Learn Docker in a Month of Lunches | \textbf{ 8. Supporting Reliability with Health Checks and Dependency Checks
}
\item [\checkbox]  Learn Docker in a Month of Lunches | \textbf{ 9. Adding Observability with Containerized Monitoring
}
\item [\checkbox]  Learn Docker in a Month of Lunches | \textbf{ 10. Running Multiple Environments with Docker Compose
}
\item [\checkbox]  Learn Docker in a Month of Lunches | \textbf{ 11. Building and Testing Applications with Docker and Docker Compose
}
\item [\checkbox]  Learn Docker in a Month of Lunches | \textbf{ 12. Understanding Orchestration: Docker Swarm and Kubernetes
}
\item [\checkbox]  Learn Docker in a Month of Lunches | \textbf{ 13. Deploying Distributed Applications as Stacks in Docker Swarm
}
\item [\checkbox]  Learn Docker in a Month of Lunches | \textbf{ 14. Automating Releases with Upgrades and Rollbacks
}
\item [\checkbox]  Learn Docker in a Month of Lunches | \textbf{ 15. Configuring Docker for Secure Remote Access and CI/CD
}
\item [\checkbox]  Learn Docker in a Month of Lunches | \textbf{ 16. Building Docker Images That Run Anywhere: Linux, Windows, Intel, and ARM
}
\item [\checkbox]  Learn Docker in a Month of Lunches | \textbf{ 17. Optimizing Your Docker Images for Size, Speed, and Security
}
\item [\checkbox]  Learn Docker in a Month of Lunches | \textbf{ 18. Application Configuration Management in Containers
}
\item [\checkbox]  Learn Docker in a Month of Lunches | \textbf{ 19. Writing and Managing Application Logs with Docker
}
\item [\checkbox]  Learn Docker in a Month of Lunches | \textbf{ 20. Controlling HTTP Traffic to Containers with a Reverse Proxy
}
\item [\checkbox]  Learn Docker in a Month of Lunches | \textbf{ 21. Asynchronous Communication with a Message Queue
}
\item [\checkbox]  Learn Docker in a Month of Lunches | \textbf{ 22. Never the End
}
\item [\checkbox]  Docker in Action | \textbf{ 1. Welcome to Docker
}
\item [\checkbox]  Docker in Action | \textbf{ 2. Running Software in Containers
}
\item [\checkbox]  Docker in Action | \textbf{ 3. Software Installation Simplified
}
\item [\checkbox]  Docker in Action | \textbf{ 4. Working with Storage and Volumes
}
\item [\checkbox]  Docker in Action | \textbf{ 5. Single-Host Networking
}
\item [\checkbox]  Docker in Action | \textbf{ 6. Limiting Risk with Resource Controls
}
\item [\checkbox]  Docker in Action | \textbf{ 7. Packaging Software in Images
}
\item [\checkbox]  Docker in Action | \textbf{ 8. Building Images Automatically with Dockerfiles
}
\item [\checkbox]  Docker in Action | \textbf{ 9. Public and Private Software Distribution
}
\item [\checkbox]  Docker in Action | \textbf{ 10. Image Pipelines
}
\item [\checkbox]  Docker in Action | \textbf{ 11. Services with Docker and Compose
}
\item [\checkbox]  Docker in Action | \textbf{ 12. First-Class Configuration Abstractions
}
\item [\checkbox]  Docker in Action | \textbf{ 13. Orchestrating Services on a Cluster of Docker Hosts with Swarm
}
\item [\checkbox]  Fundamentals of Software Architecture  | \textbf{ 1. Introduction
}
\item [\checkbox]  Fundamentals of Software Architecture  | \textbf{ 2. Architectural Thinking
}
\item [\checkbox]  Fundamentals of Software Architecture  | \textbf{ 3. Modularity
}
\item [\checkbox]  Fundamentals of Software Architecture  | \textbf{ 4. Architecture Characteristics Defined
}
\item [\checkbox]  Fundamentals of Software Architecture  | \textbf{ 5. Identifying Architecture Characteristics
}
\item [\checkbox]  Fundamentals of Software Architecture  | \textbf{ 6. Measuring and Governing Architecture Characteristics
}
\item [\checkbox]  Fundamentals of Software Architecture  | \textbf{ 7. Scope of Architecture Characteristics
}
\item [\checkbox]  Fundamentals of Software Architecture  | \textbf{ 8. Component-Based Thinking
}
\item [\checkbox]  Fundamentals of Software Architecture  | \textbf{ 9. Architecture Styles
}
\item [\checkbox]  Fundamentals of Software Architecture  | \textbf{ 10. Layered Architecture Style
}
\item [\checkbox]  Fundamentals of Software Architecture  | \textbf{ 11. Pipeline Architecture
}
\item [\checkbox]  Fundamentals of Software Architecture  | \textbf{ 12. Microkernel Architecture
}
\item [\checkbox]  Fundamentals of Software Architecture  | \textbf{ 13. Service-Based Architecture
}
\item [\checkbox]  Fundamentals of Software Architecture  | \textbf{ 14. Event-Driven Architecture Style
}
\item [\checkbox]  Fundamentals of Software Architecture  | \textbf{ 15. Space-Based Architecture
}
\item [\checkbox]  Fundamentals of Software Architecture  | \textbf{ 16. Orchestration-Driven Service-Oriented Architecture
}
\item [\checkbox]  Fundamentals of Software Architecture  | \textbf{ 17. Microservices Architecture
}
\item [\checkbox]  Fundamentals of Software Architecture  | \textbf{ 18. Choosing the Appropriate Architecture Style
}
\item [\checkbox]  Fundamentals of Software Architecture  | \textbf{ 19. Architecture Decisions
}
\item [\checkbox]  Fundamentals of Software Architecture  | \textbf{ 20. Analyzing Architecture Risk
}
\item [\checkbox]  Fundamentals of Software Architecture  | \textbf{ 21. Diagramming and Presenting Architecture
}
\item [\checkbox]  Fundamentals of Software Architecture  | \textbf{ 22. Making Teams Effective
}
\item [\checkbox]  Fundamentals of Software Architecture  | \textbf{ 23. Negotiation and Leadership Skills
}
\item [\checkbox]  Fundamentals of Software Architecture  | \textbf{ 24. Developing a Career Path
}
\item [\checkbox]  Cloud Computing Theory and Practice | \textbf{ 1. Introduction
}
\item [\checkbox]  Cloud Computing Theory and Practice | \textbf{ 2. Concurrency - Basic Concepts
}
\item [\checkbox]  Cloud Computing Theory and Practice | \textbf{ 3. Parallel and Distributed Systems
}
\item [\checkbox]  Cloud Computing Theory and Practice | \textbf{ 4. Cloud Service Providers and the Cloud Ecosystem
}
\item [\checkbox]  Cloud Computing Theory and Practice | \textbf{ 5. Cloud Access
}
\item [\checkbox]  Cloud Computing Theory and Practice | \textbf{ 6. Cloud Data Storage
}
\item [\checkbox]  Cloud Computing Theory and Practice | \textbf{ 7. Cloud Hardware and Software
}
\item [\checkbox]  Cloud Computing Theory and Practice | \textbf{ 8. Cloud Applications
}
\item [\checkbox]  Cloud Computing Theory and Practice | \textbf{ 9. Challenges Posed by Big Data and Mobile Applications
}
\item [\checkbox]  Cloud Computing Theory and Practice | \textbf{ 10. Cloud Security
}
\item [\checkbox]  Cloud Computing Theory and Practice | \textbf{ 11. Cloud Resource Virtualization
}
\item [\checkbox]  Cloud Computing Theory and Practice | \textbf{ 12. Cloud Resource Management and Scheduling
}
\item [\checkbox]  Cloud Computing Theory and Practice | \textbf{ 13. Advanced Topics
}
\item [\checkbox]  Cloud Computing (Ruparelia) | \textbf{ 1. Introduction
}
\item [\checkbox]  Cloud Computing (Ruparelia) | \textbf{ 2. Types of Cloud Computing
}
\item [\checkbox]  Cloud Computing (Ruparelia) | \textbf{ 3. Cloud Computing: A Paradigm Shift?
}
\item [\checkbox]  Cloud Computing (Ruparelia) | \textbf{ 4. Price and Value Models
}
\item [\checkbox]  Cloud Computing (Ruparelia) | \textbf{ 5. Security and Governance
}
\item [\checkbox]  Cloud Computing (Ruparelia) | \textbf{ 6. Use Case Pattern #1: IaaS and PaaS
}
\item [\checkbox]  Cloud Computing (Ruparelia) | \textbf{ 7. Use Case Pattern #2: SaaS
}
\item [\checkbox]  Cloud Computing (Ruparelia) | \textbf{ 8. Use Case Pattern #3: INaaS
}
\item [\checkbox]  Cloud Computing (Ruparelia) | \textbf{ 9. Use Case Pattern #4: BPaaS
}
\item [\checkbox]  Cloud Computing (Ruparelia) | \textbf{ 10. Transitioning to the Cloud
}
\item [\checkbox]  Cloud Computing (Ruparelia) | \textbf{ 11. Future Outlook
}
\item [\checkbox]  Cloud Computing (Ruparelia) | \textbf{ 12. Afterword: What the Author Thinks
}
\item [\checkbox]  Python Docs | \textbf{ 1. Introduction
}
\item [\checkbox]  Python Docs | \textbf{ 2. Lexical analysis
}
\item [\checkbox]  Python Docs | \textbf{ 3. Data model
}
\item [\checkbox]  Python Docs | \textbf{ 4. Execution model
}
\item [\checkbox]  Python Docs | \textbf{ 5. The import system
}
\item [\checkbox]  Python Docs | \textbf{ 6. Expressions
}
\item [\checkbox]  Python Docs | \textbf{ 7. Simple statements
}
\item [\checkbox]  Python Docs | \textbf{ 8. Compound statements
}
\item [\checkbox]  Python Docs | \textbf{ 9. Top-level components
}
\item [\checkbox]  Python Docs | \textbf{ 10. Full Grammar specification
}
\item [\checkbox]  Python Contribution | \textbf{ Getting Started
}
\item [\checkbox]  Python Contribution | \textbf{ Where to Get Help
}
\item [\checkbox]  Python Contribution | \textbf{ Lifecycle of a Pull Request
}
\item [\checkbox]  Python Contribution | \textbf{ Running & Writing Tests
}
\item [\checkbox]  Python Contribution | \textbf{ Fixing “easy” Issues (and Beyond)
}
\item [\checkbox]  Python Contribution | \textbf{ Following Python’s Development
}
\item [\checkbox]  Python Contribution | \textbf{ Git Bootcamp and Cheat Sheet
}
\item [\checkbox]  Python Contribution | \textbf{ Helping with Documentation
}
\item [\checkbox]  Python Contribution | \textbf{ Documenting Python
}
\item [\checkbox]  Python Contribution | \textbf{ Style guide
}
\item [\checkbox]  Python Contribution | \textbf{ reStructuredText Primer
}
\item [\checkbox]  Python Contribution | \textbf{ Translating
}
\item [\checkbox]  Python Contribution | \textbf{ Issue Tracking
}
\item [\checkbox]  Python Contribution | \textbf{ Triaging an Issue
}
\item [\checkbox]  Python Contribution | \textbf{ Helping Triage Issues
}
\item [\checkbox]  Python Contribution | \textbf{ Experts Index
}
\item [\checkbox]  Python Contribution | \textbf{ How to Become a Core Developer
}
\item [\checkbox]  Python Contribution | \textbf{ Developer Log
}
\item [\checkbox]  Python Contribution | \textbf{ Accepting Pull Requests
}
\item [\checkbox]  Python Contribution | \textbf{ Development Cycle
}
\item [\checkbox]  Python Contribution | \textbf{ Core Developer Motivations and Affiliations
}
\item [\checkbox]  Python Contribution | \textbf{ Core Developers Office Hours
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 1. A Tutorial Introduction
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 1.1. Getting Started
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 1.2. Variables and Arithmetic Expressions
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 1.3. The For Statement
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 1.4. Symbolic Constants
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 1.5. Character Input and Output
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 1.6. Arrays
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 1.7. Functions
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 1.8. Arguments-Call by Value
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 1.9. Character Arrays
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 1.10. External Variables and Scope
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 2. Types, Operators, and Expressions
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 2.1. Variable Names
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 2.2. Data Types and Sizes
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 2.3. Constants
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 2.4. Declarations
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 2.5. Arithmetic Operators
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 2.6. Relational and Logical Operators
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 2.7. Type Conversions
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 2.8. Increment and Decrement Operators
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 2.9. Bitwise Operators
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 2.10. Assignment Operators and Expressions
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 2.11. Conditional Expressions
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 2.12. Precedence and Order of Evaluation
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 3. Control Flow
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 3.1. Statements and Blocks
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 3.2. If-Else
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 3.3. Else-If
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 3.4. Switch
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 3.5. Loops- While and For
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 3.6. Loops- Do-while
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 3.7. Break and Continue
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 3.8. Goto and Labels
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 4. Functions and Program Structure
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 4.1. Basicsof Functions
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 4.2. Functions Returning Non-integers
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 4.3. External Variables
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 4.4. Scope Rules
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 4.5. Header Files
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 4.6. Static Variables
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 4.7. Register Variables
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 4.8. BlockStructure
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 4.9. Initialization
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 4.10. Recursion
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 4.11. The C Preprocessor
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 5. Pointers and Arrays
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 5.1. Pointers and Addresses
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 5.2. Pointers and Function Arguments
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 5.3. Pointers and Arrays
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 5.4. Address Arithmetic
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 5.5. Character Pointers and Functions
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 5.6. Pointer Arrays; Pointers to Pointers
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 5.7. Multi-dimensionalArrays
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 5.8. Initialization of Pointer Arrays
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 5.9. Pointers vs. Multi-dimensionalArrays
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 5.10. Command-line Arguments
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 5.11. Pointers to Functions
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 5.12. Complicated Declarations
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 6. Structures
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 6.1. Basics of Structures
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 6.2. Structures and Functions
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 6.3. Arrays of Structures
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 6.4. Pointers to Structures
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 6.5. Self-referential Structures
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 6.6. Table Lookup
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 6.7. Typedef
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 6.8. Unions
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 6.9. Bit-fields
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 7. Input and Output
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 7.1. Standard Input and Output
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 7.2. Formatted Output-Printf
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 7.3. Variable-length Argument Lists
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 7.4. Formatted Input-Scanf
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 7.5. File Access
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 7.6. Error Handling-Stderr and Exit
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 7.7. Line Input and Output
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 7.8. Miscellaneous Functions
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 8. The UNIX System Interface
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 8.1. File Descriptors
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 8.2. Low Level I/O-Read and Write
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 8.3. Open, Creat, Close, Unlink
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 8.4. Random Access- Lseek
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 8.5. Example-An Implementation of Fopen and Getc
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 8.6. Example - Listing Directories
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ 8.7. Example- A Storage Allocator
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ A. Reference Manual
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ A1. Introduction
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ A2. Lexical Conventions
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ A3. Syntax Notation
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ A4. Meaning of Identifiers
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ A5. Objects and Values
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ A6. Conversions
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ A7. Expressions
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ A8. Declarations
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ A9. Statements
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ A10. External Declarations
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ A11. Scope and Linkage
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ A12. Preprocessing
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ A13. Grammar
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ B1. Input and Output: <stdio.h>
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ B2. Character Class Tests: <ctype.h>
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ B3. String Functions: < string.h >
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ B4. Mathematical Functions: <rnath.h>
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ B5. Utility Functions: <stdlib.h>
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ B6. Diagnostics: < assert.h >
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ B7. Variable Argument Lists: <stdarg.h>
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ B8. Non-local Jumps: <setjmp.h>
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ B9. Signals: <signal.h>
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ B10. Date and Time Functions: < time.h >
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ B11. Implementation-defined Limits: <limits.h> and <float.h>
}
\item [\checkbox]  The C Programming Language, 2E | \textbf{ C. Summary of Changes
}
\item [\checkbox]  Python Tutorial | \textbf{ 1. Whetting Your Appetite
}
\item [\checkbox]  Python Tutorial | \textbf{ 2. Using the Python Interpreter
}
\item [\checkbox]  Python Tutorial | \textbf{ 2.1. Invoking the Interpreter
}
\item [\checkbox]  Python Tutorial | \textbf{ 2.2. The Interpreter and Its Environment
}
\item [\checkbox]  Python Tutorial | \textbf{ 3. An Informal Introduction to Python
}
\item [\checkbox]  Python Tutorial | \textbf{ 3.1. Using Python as a Calculator
}
\item [\checkbox]  Python Tutorial | \textbf{ 3.2. First Steps Towards Programming
}
\item [\checkbox]  Python Tutorial | \textbf{ 4. More Control Flow Tools
}
\item [\checkbox]  Python Tutorial | \textbf{ 4.1. if Statements
}
\item [\checkbox]  Python Tutorial | \textbf{ 4.2. for Statements
}
\item [\checkbox]  Python Tutorial | \textbf{ 4.3. The range() Function
}
\item [\checkbox]  Python Tutorial | \textbf{ 4.4. break and continue Statements, and else Clauses on Loops
}
\item [\checkbox]  Python Tutorial | \textbf{ 4.5. pass Statements
}
\item [\checkbox]  Python Tutorial | \textbf{ 4.6. Defining Functions
}
\item [\checkbox]  Python Tutorial | \textbf{ 4.7. More on Defining Functions
}
\item [\checkbox]  Python Tutorial | \textbf{ 4.8. Intermezzo: Coding Style
}
\item [\checkbox]  Python Tutorial | \textbf{ 5. Data Structures
}
\item [\checkbox]  Python Tutorial | \textbf{ 5.1. More on Lists
}
\item [\checkbox]  Python Tutorial | \textbf{ 5.2. The del statement
}
\item [\checkbox]  Python Tutorial | \textbf{ 5.3. Tuples and Sequences
}
\item [\checkbox]  Python Tutorial | \textbf{ 5.4. Sets
}
\item [\checkbox]  Python Tutorial | \textbf{ 5.5. Dictionaries
}
\item [\checkbox]  Python Tutorial | \textbf{ 5.6. Looping Techniques
}
\item [\checkbox]  Python Tutorial | \textbf{ 5.7. More on Conditions
}
\item [\checkbox]  Python Tutorial | \textbf{ 5.8. Comparing Sequences and Other Types
}
\item [\checkbox]  Python Tutorial | \textbf{ 6. Modules
}
\item [\checkbox]  Python Tutorial | \textbf{ 6.1. More on Modules
}
\item [\checkbox]  Python Tutorial | \textbf{ 6.2. Standard Modules
}
\item [\checkbox]  Python Tutorial | \textbf{ 6.3. The dir() Function
}
\item [\checkbox]  Python Tutorial | \textbf{ 6.4. Packages
}
\item [\checkbox]  Python Tutorial | \textbf{ 7. Input and Output
}
\item [\checkbox]  Python Tutorial | \textbf{ 7.1. Fancier Output Formatting
}
\item [\checkbox]  Python Tutorial | \textbf{ 7.2. Reading and Writing Files
}
\item [\checkbox]  Python Tutorial | \textbf{ 8. Errors and Exceptions
}
\item [\checkbox]  Python Tutorial | \textbf{ 8.1. Syntax Errors
}
\item [\checkbox]  Python Tutorial | \textbf{ 8.2. Exceptions
}
\item [\checkbox]  Python Tutorial | \textbf{ 8.3. Handling Exceptions
}
\item [\checkbox]  Python Tutorial | \textbf{ 8.4. Raising Exceptions
}
\item [\checkbox]  Python Tutorial | \textbf{ 8.5. Exception Chaining
}
\item [\checkbox]  Python Tutorial | \textbf{ 8.6. User-defined Exceptions
}
\item [\checkbox]  Python Tutorial | \textbf{ 8.7. Defining Clean-up Actions
}
\item [\checkbox]  Python Tutorial | \textbf{ 8.8. Predefined Clean-up Actions
}
\item [\checkbox]  Python Tutorial | \textbf{ 9. Classes
}
\item [\checkbox]  Python Tutorial | \textbf{ 9.1. A Word About Names and Objects
}
\item [\checkbox]  Python Tutorial | \textbf{ 9.2. Python Scopes and Namespaces
}
\item [\checkbox]  Python Tutorial | \textbf{ 9.3. A First Look at Classes
}
\item [\checkbox]  Python Tutorial | \textbf{ 9.4. Random Remarks
}
\item [\checkbox]  Python Tutorial | \textbf{ 9.5. Inheritance
}
\item [\checkbox]  Python Tutorial | \textbf{ 9.6. Private Variables
}
\item [\checkbox]  Python Tutorial | \textbf{ 9.7. Odds and Ends
}
\item [\checkbox]  Python Tutorial | \textbf{ 9.8. Iterators
}
\item [\checkbox]  Python Tutorial | \textbf{ 9.9. Generators
}
\item [\checkbox]  Python Tutorial | \textbf{ 9.10. Generator Expressions
}
\item [\checkbox]  Python Tutorial | \textbf{ 10. Brief Tour of the Standard Library
}
\item [\checkbox]  Python Tutorial | \textbf{ 10.1. Operating System Interface
}
\item [\checkbox]  Python Tutorial | \textbf{ 10.2. File Wildcards
}
\item [\checkbox]  Python Tutorial | \textbf{ 10.3. Command Line Arguments
}
\item [\checkbox]  Python Tutorial | \textbf{ 10.4. Error Output Redirection and Program Termination
}
\item [\checkbox]  Python Tutorial | \textbf{ 10.5. String Pattern Matching
}
\item [\checkbox]  Python Tutorial | \textbf{ 10.6. Mathematics
}
\item [\checkbox]  Python Tutorial | \textbf{ 10.7. Internet Access
}
\item [\checkbox]  Python Tutorial | \textbf{ 10.8. Dates and Times
}
\item [\checkbox]  Python Tutorial | \textbf{ 10.9. Data Compression
}
\item [\checkbox]  Python Tutorial | \textbf{ 10.10. Performance Measurement
}
\item [\checkbox]  Python Tutorial | \textbf{ 10.11. Quality Control
}
\item [\checkbox]  Python Tutorial | \textbf{ 10.12. Batteries Included
}
\item [\checkbox]  Python Tutorial | \textbf{ 11. Brief Tour of the Standard Library — Part II
}
\item [\checkbox]  Python Tutorial | \textbf{ 11.1. Output Formatting
}
\item [\checkbox]  Python Tutorial | \textbf{ 11.2. Templating
}
\item [\checkbox]  Python Tutorial | \textbf{ 11.3. Working with Binary Data Record Layouts
}
\item [\checkbox]  Python Tutorial | \textbf{ 11.4. Multi-threading
}
\item [\checkbox]  Python Tutorial | \textbf{ 11.5. Logging
}
\item [\checkbox]  Python Tutorial | \textbf{ 11.6. Weak References
}
\item [\checkbox]  Python Tutorial | \textbf{ 11.7. Tools for Working with Lists
}
\item [\checkbox]  Python Tutorial | \textbf{ 11.8. Decimal Floating Point Arithmetic
}
\item [\checkbox]  Python Tutorial | \textbf{ 12. Virtual Environments and Packages
}
\item [\checkbox]  Python Tutorial | \textbf{ 12.1. Introduction
}
\item [\checkbox]  Python Tutorial | \textbf{ 12.2. Creating Virtual Environments
}
\item [\checkbox]  Python Tutorial | \textbf{ 12.3. Managing Packages with pip
}
\item [\checkbox]  Python Tutorial | \textbf{ 13. What Now?
}
\item [\checkbox]  Python Tutorial | \textbf{ 14. Interactive Input Editing and History Substitution
}
\item [\checkbox]  Python Tutorial | \textbf{ 14.1. Tab Completion and History Editing
}
\item [\checkbox]  Python Tutorial | \textbf{ 14.2. Alternatives to the Interactive Interpreter
}
\item [\checkbox]  Python Tutorial | \textbf{ 15. Floating Point Arithmetic: Issues and Limitations
}
\item [\checkbox]  Python Tutorial | \textbf{ 15.1. Representation Error
}
\item [\checkbox]  Python Tutorial | \textbf{ 16. Appendix
}
\item [\checkbox]  Python Tutorial | \textbf{ 16.1. Interactive Mode
}
\item [\checkbox]  Python FAQs | \textbf{ General Python FAQ
}
\item [\checkbox]  Python FAQs | \textbf{ Programming FAQ
}
\item [\checkbox]  Python FAQs | \textbf{ Design and History FAQ
}
\item [\checkbox]  Python FAQs | \textbf{ Library and Extension FAQ
}
\item [\checkbox]  Python FAQs | \textbf{ Extending/Embedding FAQ
}
\item [\checkbox]  Python FAQs | \textbf{ Python on Windows FAQ
}
\item [\checkbox]  Python FAQs | \textbf{ Graphic User Interface FAQ
}
\item [\checkbox]  Python FAQs | \textbf{ “Why is Python Installed on my Computer?” FAQ
}
\item [\checkbox]  Python Standard Library | \textbf{ Introduction
}
\item [\checkbox]  Python Standard Library | \textbf{ Built-in Functions
}
\item [\checkbox]  Python Standard Library | \textbf{ Built-in Constants
}
\item [\checkbox]  Python Standard Library | \textbf{ Built-in Types
}
\item [\checkbox]  Python Standard Library | \textbf{ Built-in Exceptions
}
\item [\checkbox]  Python Standard Library | \textbf{ Text Processing Services
}
\item [\checkbox]  Python Standard Library | \textbf{ Binary Data Services
}
\item [\checkbox]  Python Standard Library | \textbf{ Data Types
}
\item [\checkbox]  Python Standard Library | \textbf{ Numeric and Mathematical Modules
}
\item [\checkbox]  Python Standard Library | \textbf{ Functional Programming Modules
}
\item [\checkbox]  Python Standard Library | \textbf{ File and Directory Access
}
\item [\checkbox]  Python Standard Library | \textbf{ Data Persistence
}
\item [\checkbox]  Python Standard Library | \textbf{ Data Compression and Archiving
}
\item [\checkbox]  Python Standard Library | \textbf{ File Formats
}
\item [\checkbox]  Python Standard Library | \textbf{ Cryptographic Services
}
\item [\checkbox]  Python Standard Library | \textbf{ Generic Operating System Services
}
\item [\checkbox]  Python Standard Library | \textbf{ Concurrent Execution
}
\item [\checkbox]  Python Standard Library | \textbf{ contextvars — Context Variables
}
\item [\checkbox]  Python Standard Library | \textbf{ Networking and Interprocess Communication
}
\item [\checkbox]  Python Standard Library | \textbf{ Internet Data Handling
}
\item [\checkbox]  Python Standard Library | \textbf{ Structured Markup Processing Tools
}
\item [\checkbox]  Python Standard Library | \textbf{ Internet Protocols and Support
}
\item [\checkbox]  Python Standard Library | \textbf{ Multimedia Services
}
\item [\checkbox]  Python Standard Library | \textbf{ Internationalization
}
\item [\checkbox]  Python Standard Library | \textbf{ Program Frameworks
}
\item [\checkbox]  Python Standard Library | \textbf{ Graphical User Interfaces with Tk
}
\item [\checkbox]  Python Standard Library | \textbf{ Development Tools
}
\item [\checkbox]  Python Standard Library | \textbf{ Debugging and Profiling
}
\item [\checkbox]  Python Standard Library | \textbf{ Software Packaging and Distribution
}
\item [\checkbox]  Python Standard Library | \textbf{ Python Runtime Services
}
\item [\checkbox]  Python Standard Library | \textbf{ Custom Python Interpreters
}
\item [\checkbox]  Python Standard Library | \textbf{ Importing Modules
}
\item [\checkbox]  Python Standard Library | \textbf{ Python Language Services
}
\item [\checkbox]  Python Standard Library | \textbf{ Miscellaneous Services
}
\item [\checkbox]  Python Standard Library | \textbf{ MS Windows Specific Services
}
\item [\checkbox]  Python Standard Library | \textbf{ Unix Specific Services
}
\item [\checkbox]  Python Standard Library | \textbf{ Superseded Modules
}
\item [\checkbox]  Python Standard Library | \textbf{ Undocumented Modules
}
\item [\checkbox]  Python HOWTOs  | \textbf{ Porting Python 2 Code to Python 3
}
\item [\checkbox]  Python HOWTOs  | \textbf{ Porting Extension Modules to Python 3
}
\item [\checkbox]  Python HOWTOs  | \textbf{ Curses Programming with Python
}
\item [\checkbox]  Python HOWTOs  | \textbf{ Descriptor HowTo Guide
}
\item [\checkbox]  Python HOWTOs  | \textbf{ Functional Programming HOWTO
}
\item [\checkbox]  Python HOWTOs  | \textbf{ Logging HOWTO
}
\item [\checkbox]  Python HOWTOs  | \textbf{ Logging Cookbook
}
\item [\checkbox]  Python HOWTOs  | \textbf{ Regular Expression HOWTO
}
\item [\checkbox]  Python HOWTOs  | \textbf{ Socket Programming HOWTO
}
\item [\checkbox]  Python HOWTOs  | \textbf{ Sorting HOW TO
}
\item [\checkbox]  Python HOWTOs  | \textbf{ Unicode HOWTO
}
\item [\checkbox]  Python HOWTOs  | \textbf{ HOWTO Fetch Internet Resources Using The urllib Package
}
\item [\checkbox]  Python HOWTOs  | \textbf{ Argparse Tutorial
}
\item [\checkbox]  Python HOWTOs  | \textbf{ An introduction to the ipaddress module
}
\item [\checkbox]  Python HOWTOs  | \textbf{ Argument Clinic How-To
}
\item [\checkbox]  Python HOWTOs  | \textbf{ Instrumenting CPython with DTrace and SystemTap
}
\item [\checkbox]  Embedding Python | \textbf{ 1. Embedding Python in Another Application
}
\item [\checkbox]  Embedding Python | \textbf{ 1.1. Very High Level Embedding
}
\item [\checkbox]  Embedding Python | \textbf{ 1.2. Beyond Very High Level Embedding: An overview
}
\item [\checkbox]  Embedding Python | \textbf{ 1.3. Pure Embedding
}
\item [\checkbox]  Embedding Python | \textbf{ 1.4. Extending Embedded Python
}
\item [\checkbox]  Embedding Python | \textbf{ 1.5. Embedding Python in C++
}
\item [\checkbox]  Embedding Python | \textbf{ 1.6. Compiling and Linking under Unix-like systems
}
\item [\checkbox]  Python Glossary | \textbf{
}
\item [\checkbox]  Python/C API | \textbf{ Introduction
}
\item [\checkbox]  Python/C API | \textbf{ Coding standards
}
\item [\checkbox]  Python/C API | \textbf{ Include Files
}
\item [\checkbox]  Python/C API | \textbf{ Useful macros
}
\item [\checkbox]  Python/C API | \textbf{ Objects, Types and Reference Counts
}
\item [\checkbox]  Python/C API | \textbf{ Exceptions
}
\item [\checkbox]  Python/C API | \textbf{ Embedding Python
}
\item [\checkbox]  Python/C API | \textbf{ Debugging Builds
}
\item [\checkbox]  Python/C API | \textbf{ Stable Application Binary Interface
}
\item [\checkbox]  Python/C API | \textbf{ The Very High Level Layer
}
\item [\checkbox]  Python/C API | \textbf{ Reference Counting
}
\item [\checkbox]  Python/C API | \textbf{ Exception Handling
}
\item [\checkbox]  Python/C API | \textbf{ Printing and clearing
}
\item [\checkbox]  Python/C API | \textbf{ Raising exceptions
}
\item [\checkbox]  Python/C API | \textbf{ Issuing warnings
}
\item [\checkbox]  Python/C API | \textbf{ Querying the error indicator
}
\item [\checkbox]  Python/C API | \textbf{ Signal Handling
}
\item [\checkbox]  Python/C API | \textbf{ Exception Classes
}
\item [\checkbox]  Python/C API | \textbf{ Exception Objects
}
\item [\checkbox]  Python/C API | \textbf{ Unicode Exception Objects
}
\item [\checkbox]  Python/C API | \textbf{ Recursion Control
}
\item [\checkbox]  Python/C API | \textbf{ Standard Exceptions
}
\item [\checkbox]  Python/C API | \textbf{ Standard Warning Categories
}
\item [\checkbox]  Python/C API | \textbf{ Utilities
}
\item [\checkbox]  Python/C API | \textbf{ Operating System Utilities
}
\item [\checkbox]  Python/C API | \textbf{ System Functions
}
\item [\checkbox]  Python/C API | \textbf{ Process Control
}
\item [\checkbox]  Python/C API | \textbf{ Importing Modules
}
\item [\checkbox]  Python/C API | \textbf{ Data marshalling support
}
\item [\checkbox]  Python/C API | \textbf{ Parsing arguments and building values
}
\item [\checkbox]  Python/C API | \textbf{ String conversion and formatting
}
\item [\checkbox]  Python/C API | \textbf{ Reflection
}
\item [\checkbox]  Python/C API | \textbf{ Codec registry and support functions
}
\item [\checkbox]  Python/C API | \textbf{ Abstract Objects Layer
}
\item [\checkbox]  Python/C API | \textbf{ Object Protocol
}
\item [\checkbox]  Python/C API | \textbf{ Call Protocol
}
\item [\checkbox]  Python/C API | \textbf{ Number Protocol
}
\item [\checkbox]  Python/C API | \textbf{ Sequence Protocol
}
\item [\checkbox]  Python/C API | \textbf{ Mapping Protocol
}
\item [\checkbox]  Python/C API | \textbf{ Iterator Protocol
}
\item [\checkbox]  Python/C API | \textbf{ Buffer Protocol
}
\item [\checkbox]  Python/C API | \textbf{ Old Buffer Protocol
}
\item [\checkbox]  Python/C API | \textbf{ Concrete Objects Layer
}
\item [\checkbox]  Python/C API | \textbf{ Fundamental Objects
}
\item [\checkbox]  Python/C API | \textbf{ Numeric Objects
}
\item [\checkbox]  Python/C API | \textbf{ Sequence Objects
}
\item [\checkbox]  Python/C API | \textbf{ Container Objects
}
\item [\checkbox]  Python/C API | \textbf{ Function Objects
}
\item [\checkbox]  Python/C API | \textbf{ Other Objects
}
\item [\checkbox]  Python/C API | \textbf{ Initialization, Finalization, and Threads
}
\item [\checkbox]  Python/C API | \textbf{ Before Python Initialization
}
\item [\checkbox]  Python/C API | \textbf{ Global configuration variables
}
\item [\checkbox]  Python/C API | \textbf{ Initializing and finalizing the interpreter
}
\item [\checkbox]  Python/C API | \textbf{ Process-wide parameters
}
\item [\checkbox]  Python/C API | \textbf{ Thread State and the Global Interpreter Lock
}
\item [\checkbox]  Python/C API | \textbf{ Sub-interpreter support
}
\item [\checkbox]  Python/C API | \textbf{ Asynchronous Notifications
}
\item [\checkbox]  Python/C API | \textbf{ Profiling and Tracing
}
\item [\checkbox]  Python/C API | \textbf{ Advanced Debugger Support
}
\item [\checkbox]  Python/C API | \textbf{ Thread Local Storage Support
}
\item [\checkbox]  Python/C API | \textbf{ Python Initialization Configuration
}
\item [\checkbox]  Python/C API | \textbf{ PyWideStringList
}
\item [\checkbox]  Python/C API | \textbf{ PyStatus
}
\item [\checkbox]  Python/C API | \textbf{ PyPreConfig
}
\item [\checkbox]  Python/C API | \textbf{ Preinitialization with PyPreConfig
}
\item [\checkbox]  Python/C API | \textbf{ PyConfig
}
\item [\checkbox]  Python/C API | \textbf{ Initialization with PyConfig
}
\item [\checkbox]  Python/C API | \textbf{ Isolated Configuration
}
\item [\checkbox]  Python/C API | \textbf{ Python Configuration
}
\item [\checkbox]  Python/C API | \textbf{ Path Configuration
}
\item [\checkbox]  Python/C API | \textbf{ Py_RunMain()
}
\item [\checkbox]  Python/C API | \textbf{ Py_GetArgcArgv()
}
\item [\checkbox]  Python/C API | \textbf{ Multi-Phase Initialization Private Provisional API
}
\item [\checkbox]  Python/C API | \textbf{ Memory Management
}
\item [\checkbox]  Python/C API | \textbf{ Overview
}
\item [\checkbox]  Python/C API | \textbf{ Raw Memory Interface
}
\item [\checkbox]  Python/C API | \textbf{ Memory Interface
}
\item [\checkbox]  Python/C API | \textbf{ Object allocators
}
\item [\checkbox]  Python/C API | \textbf{ Default Memory Allocators
}
\item [\checkbox]  Python/C API | \textbf{ Customize Memory Allocators
}
\item [\checkbox]  Python/C API | \textbf{ The pymalloc allocator
}
\item [\checkbox]  Python/C API | \textbf{ tracemalloc C API
}
\item [\checkbox]  Python/C API | \textbf{ Examples
}
\item [\checkbox]  Python/C API | \textbf{ Object Implementation Support
}
\item [\checkbox]  Python/C API | \textbf{ Allocating Objects on the Heap
}
\item [\checkbox]  Python/C API | \textbf{ Common Object Structures
}
\item [\checkbox]  Python/C API | \textbf{ Type Objects
}
\item [\checkbox]  Python/C API | \textbf{ Number Object Structures
}
\item [\checkbox]  Python/C API | \textbf{ Mapping Object Structures
}
\item [\checkbox]  Python/C API | \textbf{ Sequence Object Structures
}
\item [\checkbox]  Python/C API | \textbf{ Buffer Object Structures
}
\item [\checkbox]  Python/C API | \textbf{ Async Object Structures
}
\item [\checkbox]  Python/C API | \textbf{ Slot Type typedefs
}
\item [\checkbox]  Python/C API | \textbf{ Examples
}
\item [\checkbox]  Python/C API | \textbf{ Supporting Cyclic Garbage Collection
}
\item [\checkbox]  Python/C API | \textbf{ API and ABI Versioning
}
\item [\checkbox]  Julia Docs | \textbf{ 1. Introduction
}
\item [\checkbox]  Julia Docs | \textbf{ 2. Getting Started
}
\item [\checkbox]  Julia Docs | \textbf{ 3. Variables
}
\item [\checkbox]  Julia Docs | \textbf{ 4. Integers and Floating-Point Numbers
}
\item [\checkbox]  Julia Docs | \textbf{ 5. Mathematical Operations and Elementary Functions
}
\item [\checkbox]  Julia Docs | \textbf{ 6. Complex and Rational Numbers
}
\item [\checkbox]  Julia Docs | \textbf{ 7. Strings
}
\item [\checkbox]  Julia Docs | \textbf{ 8. Functions
}
\item [\checkbox]  Julia Docs | \textbf{ 9. Control Flow
}
\item [\checkbox]  Julia Docs | \textbf{ 10. Scope of Variables
}
\item [\checkbox]  Julia Docs | \textbf{ 11. Types
}
\item [\checkbox]  Julia Docs | \textbf{ 12. Methods
}
\item [\checkbox]  Julia Docs | \textbf{ 13. Constructors
}
\item [\checkbox]  Julia Docs | \textbf{ 14. Conversion and Promotion
}
\item [\checkbox]  Julia Docs | \textbf{ 15. Interfaces
}
\item [\checkbox]  Julia Docs | \textbf{ 16. Modules
}
\item [\checkbox]  Julia Docs | \textbf{ 17. Documentation
}
\item [\checkbox]  Julia Docs | \textbf{ 18. Metaprogramming
}
\item [\checkbox]  Julia Docs | \textbf{ 19. Multi-dimensional Arrays
}
\item [\checkbox]  Julia Docs | \textbf{ 20. Missing Values
}
\item [\checkbox]  Julia Docs | \textbf{ 21. Networking and Streams
}
\item [\checkbox]  Julia Docs | \textbf{ 22. Parallel Computing
}
\item [\checkbox]  Julia Docs | \textbf{ 24. Multi-Threading
}
\item [\checkbox]  Julia Docs | \textbf{ 25. Multi-processing and Distributed Computing
}
\item [\checkbox]  Julia Docs | \textbf{ 26. Running External Programs
}
\item [\checkbox]  Julia Docs | \textbf{ 27. Calling C and Fortran Code
}
\item [\checkbox]  Julia Docs | \textbf{ 28. Handling Operating System Variation
}
\item [\checkbox]  Julia Docs | \textbf{ 29. Environment Variables
}
\item [\checkbox]  Julia Docs | \textbf{ 30. Embedding Julia
}
\item [\checkbox]  Julia Docs | \textbf{ 31. Code Loading
}
\item [\checkbox]  Julia Docs | \textbf{ 32. Profiling
}
\item [\checkbox]  Julia Docs | \textbf{ 33. Memory allocation analysis
}
\item [\checkbox]  Julia Docs | \textbf{ 34. External Profiling
}
\item [\checkbox]  Julia Docs | \textbf{ 35. Stack Traces
}
\item [\checkbox]  Julia Docs | \textbf{ 36. Performance Tips
}
\item [\checkbox]  Julia Docs | \textbf{ 37. Checking for equality with a singleton
}
\item [\checkbox]  Julia Docs | \textbf{ 38. Workflow Tips
}
\item [\checkbox]  Julia Docs | \textbf{ 39. Style Guide
}
\item [\checkbox]  Julia Docs | \textbf{ 40. Frequently Asked Questions
}
\item [\checkbox]  Julia Docs | \textbf{ 41. Noteworthy Differences from other Languages
}
\item [\checkbox]  Julia Docs | \textbf{ 42. Unicode Input
}
\item [\checkbox]  Julia Docs | \textbf{ 43. Essentials
}
\item [\checkbox]  Julia Docs | \textbf{ 44. Collections and Data Structures
}
\item [\checkbox]  Julia Docs | \textbf{ 45. Mathematics
}
\item [\checkbox]  Julia Docs | \textbf{ 46. Examples
}
\item [\checkbox]  Julia Docs | \textbf{ 47. Numbers
}
\item [\checkbox]  Julia Docs | \textbf{ 48. Strings
}
\item [\checkbox]  Julia Docs | \textbf{ 49. Arrays
}
\item [\checkbox]  Julia Docs | \textbf{ 50. Tasks
}
\item [\checkbox]  Julia Docs | \textbf{ 51. Multi-Threading
}
\item [\checkbox]  Julia Docs | \textbf{ 52. Constants
}
\item [\checkbox]  Julia Docs | \textbf{ 53. Filesystem
}
\item [\checkbox]  Julia Docs | \textbf{ 54. I/O and Network
}
\item [\checkbox]  Julia Docs | \textbf{ 55. Punctuation
}
\item [\checkbox]  Julia Docs | \textbf{ 56. Sorting and Related Functions
}
\item [\checkbox]  Julia Docs | \textbf{ 57. Iteration utilities
}
\item [\checkbox]  Julia Docs | \textbf{ 58. C Interface
}
\item [\checkbox]  Julia Docs | \textbf{ 59. LLVM Interface
}
\item [\checkbox]  Julia Docs | \textbf{ 60. C Standard Library
}
\item [\checkbox]  Julia Docs | \textbf{ 61. StackTraces
}
\item [\checkbox]  Julia Docs | \textbf{ 62. SIMD Support
}
\item [\checkbox]  Julia Docs | \textbf{ 63. Base64
}
\item [\checkbox]  Julia Docs | \textbf{ 64. CRC32c
}
\item [\checkbox]  Julia Docs | \textbf{ 65. Dates
}
\item [\checkbox]  Julia Docs | \textbf{ 66. API reference
}
\item [\checkbox]  Julia Docs | \textbf{ 67. Delimited Files
}
\item [\checkbox]  Julia Docs | \textbf{ 68. Distributed Computing
}
\item [\checkbox]  Julia Docs | \textbf{ 69. File Events
}
\item [\checkbox]  Julia Docs | \textbf{ 70. Future
}
\item [\checkbox]  Julia Docs | \textbf{ 71. Interactive Utilities
}
\item [\checkbox]  Julia Docs | \textbf{ 72. LibGit2
}
\item [\checkbox]  Julia Docs | \textbf{ 73. Dynamic Linker
}
\item [\checkbox]  Julia Docs | \textbf{ 74. Linear Algebra
}
\item [\checkbox]  Julia Docs | \textbf{ 75. Logging
}
\item [\checkbox]  Julia Docs | \textbf{ 76. Markdown
}
\item [\checkbox]  Julia Docs | \textbf{ 77. Memory-mapped I/O
}
\item [\checkbox]  Julia Docs | \textbf{ 78. Pkg 1117
}
\item [\checkbox]  Julia Docs | \textbf{ 79. Printf 1121
}
\item [\checkbox]  Julia Docs | \textbf{ 80. Profiling 1123
}
\item [\checkbox]  Julia Docs | \textbf{ 81. The Julia REPL
}
\item [\checkbox]  Julia Docs | \textbf{ 82. Random Numbers
}
\item [\checkbox]  Julia Docs | \textbf{ 83. Reproducibility
}
\item [\checkbox]  Julia Docs | \textbf{ 84. SHA
}
\item [\checkbox]  Julia Docs | \textbf{ 85. Serialization
}
\item [\checkbox]  Julia Docs | \textbf{ 86. Shared Arrays
}
\item [\checkbox]  Julia Docs | \textbf{ 87. Sockets
}
\item [\checkbox]  Julia Docs | \textbf{ 88. Sparse Arrays
}
\item [\checkbox]  Julia Docs | \textbf{ 89. Sparse Arrays
}
\item [\checkbox]  Julia Docs | \textbf{ 90. Statistics
}
\item [\checkbox]  Julia Docs | \textbf{ 91. Unit Testing
}
\item [\checkbox]  Julia Docs | \textbf{ 92. UUIDs
}
\item [\checkbox]  Julia Docs | \textbf{ 93. Unicode
}
\item [\checkbox]  Julia Docs | \textbf{ IV. Developer Documentation
}
\item [\checkbox]  Julia Docs | \textbf{ 94. Reflection and introspection
}
\item [\checkbox]  Julia Docs | \textbf{ 95. Documentation of Julia’s Internals
}
\item [\checkbox]  Julia Docs | \textbf{ 96. Developing/debugging Julia’s C code
}
\item [\checkbox]  Julia Docs | \textbf{ 97. New language features
}
\item [\checkbox]  Julia Docs | \textbf{ 98. Language changes
}
\item [\checkbox]  Julia Docs | \textbf{ 99. Compiler/Runtime improvements
}
\item [\checkbox]  Julia Docs | \textbf{ 100. Command-line option changes
}
\item [\checkbox]  Julia Docs | \textbf{ 101. Multi-threading changes
}
\item [\checkbox]  Julia Docs | \textbf{ 102. Build system changes
}
\item [\checkbox]  Julia Docs | \textbf{ 103. New library functions
}
\item [\checkbox]  Julia Docs | \textbf{ 104. New library features
}
\item [\checkbox]  Julia Docs | \textbf{ 105. Standard library changes
}
\item [\checkbox]  Julia Docs | \textbf{ 106. Deprecated or removed
}
\item [\checkbox]  Julia Docs | \textbf{ 107. External dependencies
}
\item [\checkbox]  Julia Docs | \textbf{ 108. Tooling Improvements
}
\item [\checkbox]  Tour of C++ | \textbf{ 1. The Basics
}
\item [\checkbox]  Tour of C++ | \textbf{ 2. User-Defined Types
}
\item [\checkbox]  Tour of C++ | \textbf{ 3. Modularity
}
\item [\checkbox]  Tour of C++ | \textbf{ 4. Classes
}
\item [\checkbox]  Tour of C++ | \textbf{ 5. Essential Operations
}
\item [\checkbox]  Tour of C++ | \textbf{ 6. Templates
}
\item [\checkbox]  Tour of C++ | \textbf{ 7. Concepts and Generic Programming
}
\item [\checkbox]  Tour of C++ | \textbf{ 8. Library Overview
}
\item [\checkbox]  Tour of C++ | \textbf{ 9. Strings and Regular Expressions
}
\item [\checkbox]  Tour of C++ | \textbf{ 10. Input and Output
}
\item [\checkbox]  Tour of C++ | \textbf{ 11. Containers
}
\item [\checkbox]  Tour of C++ | \textbf{ 12. Algorithms
}
\item [\checkbox]  Tour of C++ | \textbf{ 13. Utilities
}
\item [\checkbox]  Tour of C++ | \textbf{ 14. Numerics
}
\item [\checkbox]  Tour of C++ | \textbf{ 15. Concurrency
}
\item [\checkbox]  Tour of C++ | \textbf{ 16. History and Compatibility
}
\item [\checkbox]  C++ by Dissection  | \textbf{ 1. Writing and ANCI C++ Program
}
\item [\checkbox]  C++ by Dissection  | \textbf{ 2. Native Types and Statements
}
\item [\checkbox]  C++ by Dissection  | \textbf{ 3. Functions, Pointers, and Arrays
}
\item [\checkbox]  C++ by Dissection  | \textbf{ 4. Classes and Abstract Data Types
}
\item [\checkbox]  C++ by Dissection  | \textbf{ 5. Ctors, Ctors, Conversions, and Operator Overloading
}
\item [\checkbox]  C++ by Dissection  | \textbf{ 6. Templates and Generic Programming
}
\item [\checkbox]  C++ by Dissection  | \textbf{ 7. Standard Template Library
}
\item [\checkbox]  C++ by Dissection  | \textbf{ 8. Inheritance and OOP
}
\item [\checkbox]  C++ by Dissection  | \textbf{ 9. Input/Output
}
\item [\checkbox]  C++ by Dissection  | \textbf{ 10. Exceptions and Program Correctness
}
\item [\checkbox]  C++ by Dissection  | \textbf{ 11. OOP Using C++
}
\item [\checkbox]  C++ by Dissection  | \textbf{ A. ASCII Character Codes
}
\item [\checkbox]  C++ by Dissection  | \textbf{ B. Operator Precedence aand Associativity
}
\item [\checkbox]  C++ by Dissection  | \textbf{ C. String Library
}
\item [\checkbox]  C++ by Dissection  | \textbf{ D. The tio Library
}
\item [\checkbox]  The C++ Programming Language | \textbf{ 1. Notes to the Reader
}
\item [\checkbox]  The C++ Programming Language | \textbf{ 2. A Tour of C++: The Basics
}
\item [\checkbox]  The C++ Programming Language | \textbf{ 3. A Tour of C++: Abstraction Mechanisms
}
\item [\checkbox]  The C++ Programming Language | \textbf{ 4. A Tour of C++: Containers and Algorithms
}
\item [\checkbox]  The C++ Programming Language | \textbf{ 5. A Tour of C++: Concurrency and Utilities
}
\item [\checkbox]  The C++ Programming Language | \textbf{ 6. Types and Declarations
}
\item [\checkbox]  The C++ Programming Language | \textbf{ 7. Pointers, Arrays, and References
}
\item [\checkbox]  The C++ Programming Language | \textbf{ 8. Structures, Unions, and Enumerations
}
\item [\checkbox]  The C++ Programming Language | \textbf{ 9. Statements
}
\item [\checkbox]  The C++ Programming Language | \textbf{ 10. Expressions
}
\item [\checkbox]  The C++ Programming Language | \textbf{ 11. Select Operations
}
\item [\checkbox]  The C++ Programming Language | \textbf{ 12. Functions
}
\item [\checkbox]  The C++ Programming Language | \textbf{ 13. Exception Handling
}
\item [\checkbox]  The C++ Programming Language | \textbf{ 14. Namespaces
}
\item [\checkbox]  The C++ Programming Language | \textbf{ 15. Source Files and Programs
}
\item [\checkbox]  The C++ Programming Language | \textbf{ 16. Classes
}
\item [\checkbox]  The C++ Programming Language | \textbf{ 17. Construction, Cleanup, Copy, and Move
}
\item [\checkbox]  The C++ Programming Language | \textbf{ 18. Overloading
}
\item [\checkbox]  The C++ Programming Language | \textbf{ 19. Special Operators
}
\item [\checkbox]  The C++ Programming Language | \textbf{ 20. Derived Classes
}
\item [\checkbox]  The C++ Programming Language | \textbf{ 21. Class Hierarchies
}
\item [\checkbox]  The C++ Programming Language | \textbf{ 22. Run-Time Type Information
}
\item [\checkbox]  The C++ Programming Language | \textbf{ 23. Templates
}
\item [\checkbox]  The C++ Programming Language | \textbf{ 24. Generic Programming
}
\item [\checkbox]  The C++ Programming Language | \textbf{ 25. Specialization
}
\item [\checkbox]  The C++ Programming Language | \textbf{ 26. Instantiation
}
\item [\checkbox]  The C++ Programming Language | \textbf{ 27. Templates and Hierarchies
}
\item [\checkbox]  The C++ Programming Language | \textbf{ 28. Metaprogramming
}
\item [\checkbox]  The C++ Programming Language | \textbf{ 29. A Matrix Design
}
\item [\checkbox]  The C++ Programming Language | \textbf{ 30. Standard Library Summary
}
\item [\checkbox]  The C++ Programming Language | \textbf{ 31. STL Containers
}
\item [\checkbox]  The C++ Programming Language | \textbf{ 32. STL Algorithms
}
\item [\checkbox]  The C++ Programming Language | \textbf{ 33. STL Iterators
}
\item [\checkbox]  The C++ Programming Language | \textbf{ 34. Memory and Resources
}
\item [\checkbox]  The C++ Programming Language | \textbf{ 35. Utilities
}
\item [\checkbox]  The C++ Programming Language | \textbf{ 36. Strings
}
\item [\checkbox]  The C++ Programming Language | \textbf{ 37. Regular Expressions
}
\item [\checkbox]  The C++ Programming Language | \textbf{ 38. I/O Streams
}
\item [\checkbox]  The C++ Programming Language | \textbf{ 39. Locales
}
\item [\checkbox]  The C++ Programming Language | \textbf{ 40. Numerics
}
\item [\checkbox]  The C++ Programming Language | \textbf{ 41. Concurrency
}
\item [\checkbox]  The C++ Programming Language | \textbf{ 42. Threads and Tasks
}
\item [\checkbox]  The C++ Programming Language | \textbf{ 43. The C Standard Library
}
\item [\checkbox]  The C++ Programming Language | \textbf{ 44. Compatibility
}
\item [\checkbox]  Programming Principles and Prictice Using C++  | \textbf{ 0. Notes to the reader
}
\item [\checkbox]  Programming Principles and Prictice Using C++  | \textbf{ 1. Computers, People, and Programming
}
\item [\checkbox]  Programming Principles and Prictice Using C++  | \textbf{ 2. Hello world!
}
\item [\checkbox]  Programming Principles and Prictice Using C++  | \textbf{ 3. Objects, types, and values
}
\item [\checkbox]  Programming Principles and Prictice Using C++  | \textbf{ 4. Computation
}
\item [\checkbox]  Programming Principles and Prictice Using C++  | \textbf{ 5. Errors
}
\item [\checkbox]  Programming Principles and Prictice Using C++  | \textbf{ 6. Writing a program
}
\item [\checkbox]  Programming Principles and Prictice Using C++  | \textbf{ 7. Completing a program
}
\item [\checkbox]  Programming Principles and Prictice Using C++  | \textbf{ 8. Technicalities: functions, etc.
}
\item [\checkbox]  Programming Principles and Prictice Using C++  | \textbf{ 9. Technicalities: classes, etc.
}
\item [\checkbox]  Programming Principles and Prictice Using C++  | \textbf{ 10. Input and output streams
}
\item [\checkbox]  Programming Principles and Prictice Using C++  | \textbf{ 11. File streams and string streams
}
\item [\checkbox]  Programming Principles and Prictice Using C++  | \textbf{ 12. Graphs
}
\item [\checkbox]  Programming Principles and Prictice Using C++  | \textbf{ 13. Graph classes
}
\item [\checkbox]  Programming Principles and Prictice Using C++  | \textbf{ 14. Graph class design
}
\item [\checkbox]  Programming Principles and Prictice Using C++  | \textbf{ 15. Graphing functions
}
\item [\checkbox]  Programming Principles and Prictice Using C++  | \textbf{ 16. Graphical user interfaces
}
\item [\checkbox]  Programming Principles and Prictice Using C++  | \textbf{ 17. Vectors: memory management
}
\item [\checkbox]  Programming Principles and Prictice Using C++  | \textbf{ 18. Vectors: arrays
}
\item [\checkbox]  Programming Principles and Prictice Using C++  | \textbf{ 19. Vectors: exceptions and templates
}
\item [\checkbox]  Programming Principles and Prictice Using C++  | \textbf{ 20. STL: containers, iterators, and algorithms
}
\item [\checkbox]  Programming Principles and Prictice Using C++  | \textbf{ 21. STL: maps and algorithms
}
\item [\checkbox]  Programming Principles and Prictice Using C++  | \textbf{ 22. Ideals and history
}
\item [\checkbox]  Programming Principles and Prictice Using C++  | \textbf{ 23. Text manipulation
}
\item [\checkbox]  Programming Principles and Prictice Using C++  | \textbf{ 24. Numerics
}
\item [\checkbox]  Programming Principles and Prictice Using C++  | \textbf{ 25. Embedded systems programming
}
\item [\checkbox]  Programming Principles and Prictice Using C++  | \textbf{ 26. Testing
}
\item [\checkbox]  Programming Principles and Prictice Using C++  | \textbf{ 27. The C programming language
}
\item [\checkbox]  Programming Principles and Prictice Using C++  | \textbf{ A. Language summary
}
\item [\checkbox]  Programming Principles and Prictice Using C++  | \textbf{ B. Standard-library summary
}
\item [\checkbox]  Programming Principles and Prictice Using C++  | \textbf{ C. Getting started with Visual Studio
}
\item [\checkbox]  Programming Principles and Prictice Using C++  | \textbf{ D. Installing FLTK
}
\item [\checkbox]  Programming Principles and Prictice Using C++  | \textbf{ E. GUI Implementation
}
\item [\checkbox]  Programming Principles and Prictice Using C++  | \textbf{ F. Glossary
}
\item [\checkbox]  Object-Oriented vs. Functional Programming | \textbf{ 0. Introduction
}
\item [\checkbox]  Object-Oriented vs. Functional Programming | \textbf{ 1. Lambdas: Parameterizing Code by Behavior
}
\item [\checkbox]  Object-Oriented vs. Functional Programming | \textbf{ 1.1. Why Do I Need to Learn About Lambda Expressions?
}
\item [\checkbox]  Object-Oriented vs. Functional Programming | \textbf{ 1.2. The Basics of Lambda Expressions
}
\item [\checkbox]  Object-Oriented vs. Functional Programming | \textbf{ 1.3. Summary
}
\item [\checkbox]  Object-Oriented vs. Functional Programming | \textbf{ 2. SOLID Principles
}
\item [\checkbox]  Object-Oriented vs. Functional Programming | \textbf{ 2.1. Lambda-Enabled SOLID Principles
}
\item [\checkbox]  Object-Oriented vs. Functional Programming | \textbf{ 2.2. The Single-Responsibility Principle
}
\item [\checkbox]  Object-Oriented vs. Functional Programming | \textbf{ 2.3. The Open/Closed Principle
}
\item [\checkbox]  Object-Oriented vs. Functional Programming | \textbf{ 2.4. The Liskov Substitution Principle
}
\item [\checkbox]  Object-Oriented vs. Functional Programming | \textbf{ 2.5. The Interface-Segregation Principle
}
\item [\checkbox]  Object-Oriented vs. Functional Programming | \textbf{ 2.6. The Dependency-Inversion Principle
}
\item [\checkbox]  Object-Oriented vs. Functional Programming | \textbf{ 2.7. Summary
}
\item [\checkbox]  Object-Oriented vs. Functional Programming | \textbf{ 3. Design Patterns
}
\item [\checkbox]  Object-Oriented vs. Functional Programming | \textbf{ 3.1. Functional Design Patterns
}
\item [\checkbox]  Object-Oriented vs. Functional Programming | \textbf{ 3.2. The Command Pattern
}
\item [\checkbox]  Object-Oriented vs. Functional Programming | \textbf{ 3.3. Strategy Pattern
}
\item [\checkbox]  Object-Oriented vs. Functional Programming | \textbf{ 3.4. Summary
}
\item [\checkbox]  Object-Oriented vs. Functional Programming | \textbf{ 4. Conclusions
}
\item [\checkbox]  Object-Oriented vs. Functional Programming | \textbf{ 4.1. Object-Oriented vs. Functional Languages
}
\item [\checkbox]  Object-Oriented vs. Functional Programming | \textbf{ 4.2. Programming Language Evolution
}
\item [\checkbox]  Happy Learn Haskell | \textbf{ Introduction: How to learn Haskell enjoyably
}
\item [\checkbox]  Happy Learn Haskell | \textbf{ Your First Step (Understanding our first Haskell
}
\item [\checkbox]  Happy Learn Haskell | \textbf{ definition & expression)
}
\item [\checkbox]  Happy Learn Haskell | \textbf{ Types of Jigsaw Pieces (Types and Signatures)
}
\item [\checkbox]  Happy Learn Haskell | \textbf{ The Main Road (IO, purity and actions)
}
\item [\checkbox]  Happy Learn Haskell | \textbf{ Function Magic (Pure functions, Bool, lambdas, currying)
}
\item [\checkbox]  Happy Learn Haskell | \textbf{ Sockets and Plugs (Using functions, arguments, sections)
}
\item [\checkbox]  Happy Learn Haskell | \textbf{ Output Other Things (Typeclasses, Num, Show, print vs putStrLn)
}
\item [\checkbox]  Happy Learn Haskell | \textbf{ Make Decisions (Eq, if, case, guards, function patterns)
}
\item [\checkbox]  Happy Learn Haskell | \textbf{ Shop for Food with List (List, Foldable, (:), (++), matching Lists)
}
\item [\checkbox]  Happy Learn Haskell | \textbf{ A Dream within a Dream (List, recursion, map, intercalate)
}
\item [\checkbox]  Happy Learn Haskell | \textbf{ More Shopping (Type aliases, Tuples, folding)
}
\item [\checkbox]  Happy Learn Haskell | \textbf{ How to Write Programs(Problem solving overview, summary so far)
}
\item [\checkbox]  Happy Learn Haskell | \textbf{ At the Zoo (Sum types, map, where)
}
\item [\checkbox]  Happy Learn Haskell | \textbf{ Cats and Houses (Sum types, product types, guards, function 
}
\item [\checkbox]  composition, pattern matching algebraic data types, Maybe)

\item [\checkbox]  Happy Learn Haskell | \textbf{ Basic Output (Writing programs with simplest output only)
}
\item [\checkbox]  Happy Learn Haskell | \textbf{ Fridge, the Game (Do blocks, full program recursion/looping, input)
}
\item [\checkbox]  Happy Learn Haskell | \textbf{ The People Book (Product types with record syntax, recursion, filter explained, map explained, sort, compare, Ord, flip, sortOn)
}
\item [\checkbox]  Happy Learn Haskell | \textbf{ Times-Table Train of Terror (Lists, tuples, lambdas, zip, (\$), concat, do blocks, program loop with state passing)
}
\item [\checkbox]  Happy Learn Haskell | \textbf{ Skwak the Squirrel (Sum types, product types, tuples, lambdas with type matching, sections, any, (/=), program loop with state passing, (\$) more)
}
\item [\checkbox]  Happy Learn Haskell | \textbf{ Basic Input (Writing programs with simplest input and output)
}
\item [\checkbox]  Happy Learn Haskell | \textbf{ Getting Set Up (How to get started with installing Haskell)
}
\item [\checkbox]  Happy Learn Haskll | \textbf{ Vol 1 Frequently Asked Questions (Answers to the questions we receive all the time)
}
\item [\checkbox]  Happy Learn Haskell | \textbf{ Many Thanks (A Heartfelt Thankyou Message)
}
\item [\checkbox]  Yet Another Haskell Tutorial | \textbf{ Preamble
}
\item [\checkbox]  Yet Another Haskell Tutorial | \textbf{ Introduction
}
\item [\checkbox]  Yet Another Haskell Tutorial | \textbf{ Getting Started
}
\item [\checkbox]  Yet Another Haskell Tutorial | \textbf{ Language Basics (Solutions)
}
\item [\checkbox]  Yet Another Haskell Tutorial | \textbf{ Type Basics (Solutions)
}
\item [\checkbox]  Yet Another Haskell Tutorial | \textbf{ IO (Solutions)
}
\item [\checkbox]  Yet Another Haskell Tutorial | \textbf{ Modules (Solutions)
}
\item [\checkbox]  Yet Another Haskell Tutorial | \textbf{ Advanced Language (Solutions)
}
\item [\checkbox]  Yet Another Haskell Tutorial | \textbf{ Advanced Types (Solutions)
}
\item [\checkbox]  Yet Another Haskell Tutorial | \textbf{ Monads (Solutions)
}
\item [\checkbox]  Yet Another Haskell Tutorial | \textbf{ Advanced IO
}
\item [\checkbox]  Yet Another Haskell Tutorial | \textbf{ Recursion
}
\item [\checkbox]  Yet Another Haskell Tutorial | \textbf{ Complexity
}
\item [\checkbox]  Haskell Report | \textbf{ 0. Preface
}
\item [\checkbox]  Haskell Report | \textbf{ 1 Introduction
}
\item [\checkbox]  Haskell Report | \textbf{ 2 Lexical Structure
}
\item [\checkbox]  Haskell Report | \textbf{ 3 Expressions
}
\item [\checkbox]  Haskell Report | \textbf{ 4 Declarations and Bindings
}
\item [\checkbox]  Haskell Report | \textbf{ 5 Modules
}
\item [\checkbox]  Haskell Report | \textbf{ 6 Predefined Types and Classes
}
\item [\checkbox]  Haskell Report | \textbf{ 7 Basic Input/Output
}
\item [\checkbox]  Haskell Report | \textbf{ 8 Foreign Function Interface
}
\item [\checkbox]  Haskell Report | \textbf{ 9 Standard Prelude
}
\item [\checkbox]  Haskell Report | \textbf{ 10 Syntax Reference
}
\item [\checkbox]  Haskell Report | \textbf{ 11 Specification of Derived Instances
}
\item [\checkbox]  Haskell Report | \textbf{ 12 Compiler Pragmas
}
\item [\checkbox]  Haskell Report | \textbf{ 13 Control.Monad
}
\item [\checkbox]  Haskell Report | \textbf{ 14 Data.Array
}
\item [\checkbox]  Haskell Report | \textbf{ 15 Data.Bits
}
\item [\checkbox]  Haskell Report | \textbf{ 16 Data.Char
}
\item [\checkbox]  Haskell Report | \textbf{ 17 Data.Complex
}
\item [\checkbox]  Haskell Report | \textbf{ 18 Data.Int
}
\item [\checkbox]  Haskell Report | \textbf{ 19 Data.Ix
}
\item [\checkbox]  Haskell Report | \textbf{ 20 Data.List
}
\item [\checkbox]  Haskell Report | \textbf{ 21 Data.Maybe
}
\item [\checkbox]  Haskell Report | \textbf{ 22 Data.Ratio
}
\item [\checkbox]  Haskell Report | \textbf{ 22.1 Specification
}
\item [\checkbox]  Haskell Report | \textbf{ 23 Data.Word
}
\item [\checkbox]  Haskell Report | \textbf{ 24 Foreign
}
\item [\checkbox]  Haskell Report | \textbf{ 25 Foreign.C
}
\item [\checkbox]  Haskell Report | \textbf{ 26 Foreign.C.Error
}
\item [\checkbox]  Haskell Report | \textbf{ 27 Foreign.C.String
}
\item [\checkbox]  Haskell Report | \textbf{ 28 Foreign.C.Types
}
\item [\checkbox]  Haskell Report | \textbf{ 29 Foreign.ForeignPtr
}
\item [\checkbox]  Haskell Report | \textbf{ 30 Foreign.Marshal
}
\item [\checkbox]  Haskell Report | \textbf{ 31 Foreign.Marshal.Alloc
}
\item [\checkbox]  Haskell Report | \textbf{ 32 Foreign.Marshal.Array
}
\item [\checkbox]  Haskell Report | \textbf{ 33 Foreign.Marshal.Error
}
\item [\checkbox]  Haskell Report | \textbf{ 34 Foreign.Marshal.Utils
}
\item [\checkbox]  Haskell Report | \textbf{ 35 Foreign.Ptr
}
\item [\checkbox]  Haskell Report | \textbf{ 36 Foreign.StablePtr
}
\item [\checkbox]  Haskell Report | \textbf{ 37 Foreign.Storable
}
\item [\checkbox]  Haskell Report | \textbf{ 38 Numeric
}
\item [\checkbox]  Haskell Report | \textbf{ 39 System.Environment
}
\item [\checkbox]  Haskell Report | \textbf{ 40 System.Exit
}
\item [\checkbox]  Eloquent JavaScript | \textbf{ 0. Introduction
}
\item [\checkbox]  Eloquent JavaScript | \textbf{ 1. Values, Types, and Operators
}
\item [\checkbox]  Eloquent JavaScript | \textbf{ 2. Program Structure
}
\item [\checkbox]  Eloquent JavaScript | \textbf{ 3. Functions
}
\item [\checkbox]  Eloquent JavaScript | \textbf{ 4. Data Structures: Objects and Arrays
}
\item [\checkbox]  Eloquent JavaScript | \textbf{ 5. Higher-order Functions
}
\item [\checkbox]  Eloquent JavaScript | \textbf{ 6. The Secret Life of Objects
}
\item [\checkbox]  Eloquent JavaScript | \textbf{ 7. Project: A Robot
}
\item [\checkbox]  Eloquent JavaScript | \textbf{ 8. Bugs and Errors
}
\item [\checkbox]  Eloquent JavaScript | \textbf{ 9. Regular Expressions
}
\item [\checkbox]  Eloquent JavaScript | \textbf{ 10. Modules
}
\item [\checkbox]  Eloquent JavaScript | \textbf{ 11. Asynchronous Programming
}
\item [\checkbox]  Eloquent JavaScript | \textbf{ 12. Project: A Programming Language
}
\item [\checkbox]  Eloquent JavaScript | \textbf{ 13. JavaScript and the Browser
}
\item [\checkbox]  Eloquent JavaScript | \textbf{ 14. The Document Object Model
}
\item [\checkbox]  Eloquent JavaScript | \textbf{ 15. Handling Events
}
\item [\checkbox]  Eloquent JavaScript | \textbf{ 16. Project: A Platform Game
}
\item [\checkbox]  Eloquent JavaScript | \textbf{ 17. Drawing on Canvas
}
\item [\checkbox]  Eloquent JavaScript | \textbf{ 18. HTTP and Forms
}
\item [\checkbox]  Eloquent JavaScript | \textbf{ 19. Project: A Pixel Art Editor
}
\item [\checkbox]  Eloquent JavaScript | \textbf{ 20. Node.js
}
\item [\checkbox]  Eloquent JavaScript | \textbf{ 21. Project: Skill-Sharing Website
}
\item [\checkbox]  Java Pocket Guide  | \textbf{ 1. Naming Conventions
}
\item [\checkbox]  Java Pocket Guide  | \textbf{ 2. Lexical Elements
}
\item [\checkbox]  Java Pocket Guide  | \textbf{ 3. Fundamental Types
}
\item [\checkbox]  Java Pocket Guide  | \textbf{ 4. Reference Types
}
\item [\checkbox]  Java Pocket Guide  | \textbf{ 5. Object-Oriented Programming
}
\item [\checkbox]  Java Pocket Guide  | \textbf{ 6. Statements and Blocks
}
\item [\checkbox]  Java Pocket Guide  | \textbf{ 7. Exception Handling
}
\item [\checkbox]  Java Pocket Guide  | \textbf{ 8. Java Modifiers
}
\item [\checkbox]  Java Pocket Guide  | \textbf{ 9. Java Platform, Standard Edition
}
\item [\checkbox]  Java Pocket Guide  | \textbf{ 10. Development Basics
}
\item [\checkbox]  Java Pocket Guide  | \textbf{ 11. Memory Management
}
\item [\checkbox]  Java Pocket Guide  | \textbf{ 12. Basic Input and Output
}
\item [\checkbox]  Java Pocket Guide  | \textbf{ 13. New I/O API (NIO.2)
}
\item [\checkbox]  Java Pocket Guide  | \textbf{ 14. Concurrency
}
\item [\checkbox]  Java Pocket Guide  | \textbf{ 15. Java Collections Framework
}
\item [\checkbox]  Java Pocket Guide  | \textbf{ 16. Generics Framework
}
\item [\checkbox]  Java Pocket Guide  | \textbf{ 17. The Java Scripting API
}
\item [\checkbox]  Java Pocket Guide  | \textbf{ 18. Date and Time API
}
\item [\checkbox]  Java Pocket Guide  | \textbf{ 19. Lambda Expressions
}
\item [\checkbox]  Java Pocket Guide  | \textbf{ 20. JShell: the Java Shell
}
\item [\checkbox]  Java Pocket Guide  | \textbf{ 21. Java Module System
}
\item [\checkbox]  Tour of Scala  | \textbf{ Introduction
}
\item [\checkbox]  Tour of Scala  | \textbf{ Basics
}
\item [\checkbox]  Tour of Scala  | \textbf{ Unified Types
}
\item [\checkbox]  Tour of Scala  | \textbf{ Classes
}
\item [\checkbox]  Tour of Scala  | \textbf{ Default Parameter Values
}
\item [\checkbox]  Tour of Scala  | \textbf{ Named Arguments
}
\item [\checkbox]  Tour of Scala  | \textbf{ Traits
}
\item [\checkbox]  Tour of Scala  | \textbf{ Tuples
}
\item [\checkbox]  Tour of Scala  | \textbf{ Class Composition with Mixins
}
\item [\checkbox]  Tour of Scala  | \textbf{ Higher-order Functions
}
\item [\checkbox]  Tour of Scala  | \textbf{ Nested Methods
}
\item [\checkbox]  Tour of Scala  | \textbf{ Multiple Parameter Lists (Currying)
}
\item [\checkbox]  Tour of Scala  | \textbf{ Case Classes
}
\item [\checkbox]  Tour of Scala  | \textbf{ Pattern Matching
}
\item [\checkbox]  Tour of Scala  | \textbf{ Singleton Objects
}
\item [\checkbox]  Tour of Scala  | \textbf{ Regular Expression Patterns
}
\item [\checkbox]  Tour of Scala  | \textbf{ Extractor Objects
}
\item [\checkbox]  Tour of Scala  | \textbf{ For Comprehensions
}
\item [\checkbox]  Tour of Scala  | \textbf{ Generic Classes
}
\item [\checkbox]  Tour of Scala  | \textbf{ Variances
}
\item [\checkbox]  Tour of Scala  | \textbf{ Upper Type Bounds
}
\item [\checkbox]  Tour of Scala  | \textbf{ Lower Type Bounds
}
\item [\checkbox]  Tour of Scala  | \textbf{ Inner Classes
}
\item [\checkbox]  Tour of Scala  | \textbf{ Abstract Type Members
}
\item [\checkbox]  Tour of Scala  | \textbf{ Compound Types
}
\item [\checkbox]  Tour of Scala  | \textbf{ Self-type
}
\item [\checkbox]  Tour of Scala  | \textbf{ Implicit Parameters
}
\item [\checkbox]  Tour of Scala  | \textbf{ Implicit Conversions
}
\item [\checkbox]  Tour of Scala  | \textbf{ Polymorphic Methods
}
\item [\checkbox]  Tour of Scala  | \textbf{ Type Inference
}
\item [\checkbox]  Tour of Scala  | \textbf{ Operators
}
\item [\checkbox]  Tour of Scala  | \textbf{ By-name Parameters
}
\item [\checkbox]  Tour of Scala  | \textbf{ Annotations
}
\item [\checkbox]  Tour of Scala  | \textbf{ Packages and Imports
}
\item [\checkbox]  Tour of Scala  | \textbf{ Package Objects
}
\item [\checkbox]  Scala Book | \textbf{ Introduction
}
\item [\checkbox]  Scala Book | \textbf{ Prelude꞉ A Taste of Scala
}
\item [\checkbox]  Scala Book | \textbf{ Preliminaries
}
\item [\checkbox]  Scala Book | \textbf{ Control Structures
}
\item [\checkbox]  Scala Book | \textbf{ Scala Classes
}
\item [\checkbox]  Scala Book | \textbf{ Scala Collections
}
\item [\checkbox]  Scala Book | \textbf{ A Few Miscellaneous Items
}
\item [\checkbox]  Scala Book | \textbf{ sbt and ScalaTest
}
\item [\checkbox]  Scala Book | \textbf{ Functional Programming
}
\item [\checkbox]  Scala Book | \textbf{ Case Classes
}
\item [\checkbox]  Scala Book | \textbf{ Concurrency
}
\item [\checkbox]  Scala Book | \textbf{ Where To Go Next
}
\item [\checkbox]  Rust Book  | \textbf{ 0. Introduction
}
\item [\checkbox]  Rust Book  | \textbf{ 1. Getting Started
}
\item [\checkbox]  Rust Book  | \textbf{ 2. Programming a Guessing Game
}
\item [\checkbox]  Rust Book  | \textbf{ 3. Common Programming Concepts
}
\item [\checkbox]  Rust Book  | \textbf{ 4. Understanding Ownership
}
\item [\checkbox]  Rust Book  | \textbf{ 5. Using Structs to Structure Related Data
}
\item [\checkbox]  Rust Book  | \textbf{ 6. Enums and Pattern Matching
}
\item [\checkbox]  Rust Book  | \textbf{ 7. Managing Growing Projects with Packages, Crates, and Modules
}
\item [\checkbox]  Rust Book  | \textbf{ 8. Common Collections
}
\item [\checkbox]  Rust Book  | \textbf{ 9. Error Handling
}
\item [\checkbox]  Rust Book  | \textbf{ 10. Generic Types, Traits, and Lifetimes
}
\item [\checkbox]  Rust Book  | \textbf{ 11. Writing Automated Tests
}
\item [\checkbox]  Rust Book  | \textbf{ 12. An I/O Project: Building a Command Line Program
}
\item [\checkbox]  Rust Book  | \textbf{ 13. Functional Language Features: Iterators and Closures
}
\item [\checkbox]  Rust Book  | \textbf{ 14. More about Cargo and Crates.io
}
\item [\checkbox]  Rust Book  | \textbf{ 15. Smart Pointers
}
\item [\checkbox]  Rust Book  | \textbf{ 16. Fearless Concurrency
}
\item [\checkbox]  Rust Book  | \textbf{ 17. Object Oriented Programming Features of Rust
}
\item [\checkbox]  Rust Book  | \textbf{ 18. Patterns and Matching
}
\item [\checkbox]  Rust Book  | \textbf{ 19. Advanced Features
}
\item [\checkbox]  Rust Book  | \textbf{ 20. Final Project: Building a Multithreaded Web Server
}
\item [\checkbox]  Rust Book  | \textbf{ A. Keywords
}
\item [\checkbox]  Rust Book  | \textbf{ B. Operators and Symbols
}
\item [\checkbox]  Rust Book  | \textbf{ C. Derivable Traits
}
\item [\checkbox]  Rust Book  | \textbf{ D. Useful Development Tools
}
\item [\checkbox]  Rust Book  | \textbf{ E. Editions
}
\item [\checkbox]  Rust Book  | \textbf{ F. Translations of the Book
}
\item [\checkbox]  Rust Book  | \textbf{ How Rust is Made and “Nightly Rust”
}
\item [\checkbox]  Inside the Python Virtual Machine  | \textbf{ 1. Introduction
}
\item [\checkbox]  Inside the Python Virtual Machine  | \textbf{ 2. The View From 30,000ft
}
\item [\checkbox]  Inside the Python Virtual Machine  | \textbf{ 3. Compiling Python Source Code
}
\item [\checkbox]  Inside the Python Virtual Machine  | \textbf{ 3.1. From Source To Parse Tree
}
\item [\checkbox]  Inside the Python Virtual Machine  | \textbf{ 3.2. Python tokens
}
\item [\checkbox]  Inside the Python Virtual Machine  | \textbf{ 3.3. From Parse Tree To Abstract Syntax Tree
}
\item [\checkbox]  Inside the Python Virtual Machine  | \textbf{ 3.4. Building The Symbol Table
}
\item [\checkbox]  Inside the Python Virtual Machine  | \textbf{ 3.5. From AST To Code Objects
}
\item [\checkbox]  Inside the Python Virtual Machine  | \textbf{ 4. Python Objects
}
\item [\checkbox]  Inside the Python Virtual Machine  | \textbf{ 4.1. PyObject
}
\item [\checkbox]  Inside the Python Virtual Machine  | \textbf{ 4.2. Dissecting Types
}
\item [\checkbox]  Inside the Python Virtual Machine  | \textbf{ 4.3. Type Object Case Studies
}
\item [\checkbox]  Inside the Python Virtual Machine  | \textbf{ 4.4. Minting type instances
}
\item [\checkbox]  Inside the Python Virtual Machine  | \textbf{ 4.5. Objects and their attributes
}
\item [\checkbox]  Inside the Python Virtual Machine  | \textbf{ 4.6. Method Resolution Order (MRO)
}
\item [\checkbox]  Inside the Python Virtual Machine  | \textbf{ 5. Code Objects
}
\item [\checkbox]  Inside the Python Virtual Machine  | \textbf{ 5.1. Exploring code objects
}
\item [\checkbox]  Inside the Python Virtual Machine  | \textbf{ 5.2. Code Objects within other code objects
}
\item [\checkbox]  Inside the Python Virtual Machine  | \textbf{ 5.3. Code Objects in the VM
}
\item [\checkbox]  Inside the Python Virtual Machine  | \textbf{ 6. Frame Objects
}
\item [\checkbox]  Inside the Python Virtual Machine  | \textbf{ 6.1. Allocating Frame Objects
}
\item [\checkbox]  Inside the Python Virtual Machine  | \textbf{ 7. Interpreter and Thread States
}
\item [\checkbox]  Inside the Python Virtual Machine  | \textbf{ 7.1. The Interpreter state
}
\item [\checkbox]  Inside the Python Virtual Machine  | \textbf{ 7.2. The Thread state
}
\item [\checkbox]  Inside the Python Virtual Machine  | \textbf{ 8. Intermezzo: The abstract.c Module
}
\item [\checkbox]  Inside the Python Virtual Machine  | \textbf{ 9. The evaluation loop, ceval.c
}
\item [\checkbox]  Inside the Python Virtual Machine  | \textbf{ 9.1. Putting names in place
}
\item [\checkbox]  Inside the Python Virtual Machine  | \textbf{ 9.2. The parts of the machine
}
\item [\checkbox]  Inside the Python Virtual Machine  | \textbf{ 9.3. The Evaluation loop
}
\item [\checkbox]  Inside the Python Virtual Machine  | \textbf{ 9.4. A sampling of opcodes
}
\item [\checkbox]  Inside the Python Virtual Machine  | \textbf{ 10. The Block Stack
}
\item [\checkbox]  Inside the Python Virtual Machine  | \textbf{ 10.1. A Short Note on Exception Handling
}
\item [\checkbox]  Inside the Python Virtual Machine  | \textbf{ 11. From Class code to bytecode
}
\item [\checkbox]  Inside the Python Virtual Machine  | \textbf{ 12. Generators: Behind the scenes.
}
\item [\checkbox]  Inside the Python Virtual Machine  | \textbf{ 12.1. The Generator object
}
\item [\checkbox]  Inside the Python Virtual Machine  | \textbf{ 12.2. Running a generator
}
\item [\checkbox]  Inside the Python Virtual Machine  | \textbf{ A. Notes
}
\item [\checkbox]  Inside the Java Virtual Machine | \textbf{ 1. Introduction to Java's Architecture
}
\item [\checkbox]  Inside the Java Virtual Machine | \textbf{ 2. Platform Independence
}
\item [\checkbox]  Inside the Java Virtual Machine | \textbf{ 3. Security
}
\item [\checkbox]  Inside the Java Virtual Machine | \textbf{ 4. Network Mobility
}
\item [\checkbox]  Inside the Java Virtual Machine | \textbf{ 5. The Java Virtual Machine
}
\item [\checkbox]  Inside the Java Virtual Machine | \textbf{ 6. The Java Class File
}
\item [\checkbox]  Inside the Java Virtual Machine | \textbf{ 7. The Lifetime of a Type
}
\item [\checkbox]  Inside the Java Virtual Machine | \textbf{ 8. The Linking Model
}
\item [\checkbox]  Inside the Java Virtual Machine | \textbf{ 9. Garbage Collection
}
\item [\checkbox]  Inside the Java Virtual Machine | \textbf{ 10. Stack and Local Variable Operations
}
\item [\checkbox]  Inside the Java Virtual Machine | \textbf{ 11. Type Conversion
}
\item [\checkbox]  Inside the Java Virtual Machine | \textbf{ 12. Integer Arithmetic
}
\item [\checkbox]  Inside the Java Virtual Machine | \textbf{ 13. Logic
}
\item [\checkbox]  Inside the Java Virtual Machine | \textbf{ 14. Floating Point Arithmetic
}
\item [\checkbox]  Inside the Java Virtual Machine | \textbf{ 15. Objects and Arrays
}
\item [\checkbox]  Inside the Java Virtual Machine | \textbf{ 16. Control Flow
}
\item [\checkbox]  Inside the Java Virtual Machine | \textbf{ 17. Exceptions
}
\item [\checkbox]  Inside the Java Virtual Machine | \textbf{ 18. Finally Clauses
}
\item [\checkbox]  Inside the Java Virtual Machine | \textbf{ 19. Method Invocation and Return
}
\item [\checkbox]  Inside the Java Virtual Machine | \textbf{ 20. Thread Synchronization
}
\item [\checkbox]  Touch of Class | \textbf{ 1. The Industry of Pure Ideas
}
\item [\checkbox]  Touch of Class | \textbf{ 2. Dealing with objects
}
\item [\checkbox]  Touch of Class | \textbf{ 3. Program structure basics
}
\item [\checkbox]  Touch of Class | \textbf{ 4. The interface of a class
}
\item [\checkbox]  Touch of Class | \textbf{ 5. Just Enough Logic
}
\item [\checkbox]  Touch of Class | \textbf{ 6. Creating objects and executing systems
}
\item [\checkbox]  Touch of Class | \textbf{ 7. Control structures
}
\item [\checkbox]  Touch of Class | \textbf{ 8. Routines, functional abstraction and information hiding
}
\item [\checkbox]  Touch of Class | \textbf{ 9. Variables, assignment and references
}
\item [\checkbox]  Touch of Class | \textbf{ 10. Just enough hardware
}
\item [\checkbox]  Touch of Class | \textbf{ 11. Describing syntax
}
\item [\checkbox]  Touch of Class | \textbf{ 12. Programming languages and tools
}
\item [\checkbox]  Touch of Class | \textbf{ 13. Fundamental data structures, genericity, and algorithm complexity
}
\item [\checkbox]  Touch of Class | \textbf{ 14. Recursion and trees
}
\item [\checkbox]  Touch of Class | \textbf{ 15. Devising and engineering an algorithm: Topological Sort
}
\item [\checkbox]  Touch of Class | \textbf{ 16. Inheritance
}
\item [\checkbox]  Touch of Class | \textbf{ 17. Operations as objects: agents and lambda calculus
}
\item [\checkbox]  Touch of Class | \textbf{ 18. Event-driven design
}
\item [\checkbox]  Touch of Class | \textbf{ 19. Introduction to software engineering
}
\item [\checkbox]  Touch of Class | \textbf{ 20. An introduction to Java (from material by Marco Piccioni)
}
\item [\checkbox]  Touch of Class | \textbf{ 21. An introduction to C# (from material by Benjamin Morandi)
}
\item [\checkbox]  Touch of Class | \textbf{ 22. An introduction to C++ (from material by Nadia Polikarpova)
}
\item [\checkbox]  Touch of Class | \textbf{ 23. From C++ to C
}
\item [\checkbox]  Touch of Class | \textbf{ 24. Using the EiffelStudio environment
}
\item [\checkbox]  Introduction to the Theory of Formal Languages and Automata (Levelt) | \textbf{ 1. Grammars as Formal Systems
}
\item [\checkbox]  Introduction to the Theory of Formal Languages and Automata (Levelt) | \textbf{ 2. The Hierarchy of Grammars
}
\item [\checkbox]  Introduction to the Theory of Formal Languages and Automata (Levelt) | \textbf{ 3. Probabilistic Grammars
}
\item [\checkbox]  Introduction to the Theory of Formal Languages and Automata (Levelt) | \textbf{ 4. Finite Automata
}
\item [\checkbox]  Introduction to the Theory of Formal Languages and Automata (Levelt) | \textbf{ 5. Push-Down Automata
}
\item [\checkbox]  Introduction to the Theory of Formal Languages and Automata (Levelt) | \textbf{ 6. Linear-Bounded Automata
}
\item [\checkbox]  Introduction to the Theory of Formal Languages and Automata (Levelt) | \textbf{ 7. Turing Machines
}
\item [\checkbox]  Introduction to the Theory of Formal Languages and Automata (Levelt) | \textbf{ 8. Grammatical Inference
}
\item [\checkbox]  Introduction to the Theory of Formal Languages and Automata (Levelt) | \textbf{ 9. Historical and Bibliographical Remarks
}
\item [\checkbox]  Introduction to the Theory of Formal Languages and Automata (Levelt) | \textbf{ A. Some References to New Developments
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 1. Regular Languages and Regular Expressions
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 1.1. Basic Definitions
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 1.2. Regular Expressions in Theory
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 1.3. Regular Expressions in Practice
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 1.4. Regular Expressions in Software Products
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 1.5. Conclusions
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 2. Finite Automata
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 2.1. Deterministic Finite Automata
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 2.2. Nondeterministic Finite Automata
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 2.3. The JFLAP Project and Finite Automata
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 2.4. Conclusions
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 3. The Relationship Between Finite 
Automata and Regular Expressions
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 3.1. Conversion of a Regular 
Expression to a Finite Automaton
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 3.2. Conversion of a Finite Automaton to a Regular Expression
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 3.3. Searching Substrings Satisfying the Given Regular Expression
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 3.4. Conversion Functions in JFLAP
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 3.5. Conclusions
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 4. Finite-State Machines in Practice
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 4.1. Simple Finite-State Models
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 4.2. About FSM-Based Programming
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 4.3. Conclusions
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 5. Nonregular Languages and Context-Free Grammars
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 5.1. Nonregular Languages. The Pumping Lemma
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 5.2. Languages and Problems, Models of Computation
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 5.3. Context-Free Grammars
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 5.4. Regular Grammars
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 5.5. Conclusions
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 6. Pushdown Automata
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 6.1. Organization of a Pushdown Automaton
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 6.2. Conversion of a Context-Free Grammar to a Pushdown Automaton
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 6.3. Conversion of a Pushdown Automaton to a Context-Free Grammar
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 6.4. Deterministic and Nondeterministic Pushdown Automata. Two Big Differences
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 6.5. Pushdown Automata in JFLAP
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 6.6. Recognition of Deterministic Context-Free Languages
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 6.7. Conclusions
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 7. Parsing
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 7.1. Unambiguous and Ambiguous Grammars
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 7.2. Leftmost Derivation, Rightmost Derivation
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 7.3. LL, LR, and Other Technical Details
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 7.4. A Parser for LR(1) Grammars
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 7.5. LR(1) Parser and Pushdown Automaton
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 7.6. Parser for LL(1) Grammars
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 7.7. Parser for Any Context-Free Grammar
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 7.8. Conclusions
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 8. Compiler Generation
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 8.1. Translators, Compilers, Interpreters
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 8.2. The Coco/R Project
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 8.3. Ideology of Compilers
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 8.4. A Practical Example. A Translator for an Elementary Programming Language
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 8.5. Conclusions
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 9. The Lindenmayer Systems (L-Systems)
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 9.1. Grammars as a Method of String Generation
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 9.2. Graphical String Interpretation
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 9.3. Inner L-System Organization
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 9.4. L-System Visualization Instruments
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 9.5. Fractal Patterns
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 9.6. Varieties and Additional Capabilities of L-Systems
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 9.7. Conclusions
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 10. Turing Machines
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 10.1. Looking Back
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 10.2. Beyond Context-Free Languages
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 10.3. Deterministic Turing Machine
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 10.4. The Turing Machine and Language Recognition
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 10.5. Formal Definition of the Turing Machine
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 10.6. Turing Machine Emulator
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 10.7. Programming a Turing Machine
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 10.8. Nondeterministic Turing Machine
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 10.9. Turing Machine Variations
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 10.10. Emulation of the Turing Machine with JFLAP
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 10.11. Encoding Machines and Universal Turing Machines
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 10.12. Conclusions
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 11. Decidability and Complexity
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 11.1. Decidability and Undecidability of Languages
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 11.2. The Halting Problem
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 11.3. The Turing Machine and Decidability
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 11.4. What Is an Algorithm?
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 11.5. The Turing Machine and a Personal Computer
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 11.6. The Halting Problem and Programmers
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 11.7. Church Formalism and Functional Programming
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 11.8. Complexity of Problems and Systems
}
\item [\checkbox]  Algorithms, Languages, Automata, and Compilers | \textbf{ 11.9. Conclusions
}
\item [\checkbox]  An Introduction to Formal Languages and Automata | \textbf{ 1. Introduction to the Theory of Computation
}
\item [\checkbox]  An Introduction to Formal Languages and Automata | \textbf{ 2. Finite Automata
}
\item [\checkbox]  An Introduction to Formal Languages and Automata | \textbf{ 3. Regular Languages and Regular Grammars
}
\item [\checkbox]  An Introduction to Formal Languages and Automata | \textbf{ 4. Properties of Regular Languages
}
\item [\checkbox]  An Introduction to Formal Languages and Automata | \textbf{ 5. Context-Free Languages
}
\item [\checkbox]  An Introduction to Formal Languages and Automata | \textbf{ 6. Simplification of Context-Free Grammars and Normal Forms
}
\item [\checkbox]  An Introduction to Formal Languages and Automata | \textbf{ 7. Pushdown Automata
}
\item [\checkbox]  An Introduction to Formal Languages and Automata | \textbf{ 8. Properties of Context-Free Languages
}
\item [\checkbox]  An Introduction to Formal Languages and Automata | \textbf{ 9. Turing Machines
}
\item [\checkbox]  An Introduction to Formal Languages and Automata | \textbf{ 10. Other Models of Turing Machines
}
\item [\checkbox]  An Introduction to Formal Languages and Automata | \textbf{ 11. Hierarchy of Formal Languages and Automata
}
\item [\checkbox]  An Introduction to Formal Languages and Automata | \textbf{ 12. Limits of Algorithmic Computation
}
\item [\checkbox]  An Introduction to Formal Languages and Automata | \textbf{ 13. Other Models of Computation
}
\item [\checkbox]  An Introduction to Formal Languages and Automata | \textbf{ 14. An Overview of Computational Complexity
}
\item [\checkbox]  An Introduction to Formal Languages and Automata | \textbf{ A. Finite-State Transducers
}
\item [\checkbox]  An Introduction to Formal Languages and Automata | \textbf{ B. JFLAP: A Useful Tool
}
\item [\checkbox]  A Course in Formal Languages, Automata, and Groups (Chiswell)  | \textbf{ 1. Grammars and Machine Recognition
}
\item [\checkbox]  A Course in Formal Languages, Automata, and Groups (Chiswell)  | \textbf{ 2. Recursive Functions
}
\item [\checkbox]  A Course in Formal Languages, Automata, and Groups (Chiswell)  | \textbf{ 3. Recursively Enumerable Sets and Languages
}
\item [\checkbox]  A Course in Formal Languages, Automata, and Groups (Chiswell)  | \textbf{ 4. Context-free Languages
}
\item [\checkbox]  A Course in Formal Languages, Automata, and Groups (Chiswell)  | \textbf{ 5. Connections with Group Theory
}
\item [\checkbox]  Intro to Automata Theory, Languages, and Computation (Hopcroft) | \textbf{ 1. Automata: The Methods and the Madness
}
\item [\checkbox]  Intro to Automata Theory, Languages, and Computation (Hopcroft) | \textbf{ 2. Finite Automata
}
\item [\checkbox]  Intro to Automata Theory, Languages, and Computation (Hopcroft) | \textbf{ 3. Regular Expressions and Languages.
}
\item [\checkbox]  Intro to Automata Theory, Languages, and Computation (Hopcroft) | \textbf{ 4. Properties of Regular Languages.
}
\item [\checkbox]  Intro to Automata Theory, Languages, and Computation (Hopcroft) | \textbf{ 5. Context-Free Grammars and Languages.
}
\item [\checkbox]  Intro to Automata Theory, Languages, and Computation (Hopcroft) | \textbf{ 6. Pushdown Automata.
}
\item [\checkbox]  Intro to Automata Theory, Languages, and Computation (Hopcroft) | \textbf{ 7. Properties of Context-Free Languages.
}
\item [\checkbox]  Intro to Automata Theory, Languages, and Computation (Hopcroft) | \textbf{ 8.Introduction to Turing Machines.
}
\item [\checkbox]  Intro to Automata Theory, Languages, and Computation (Hopcroft) | \textbf{ 9. Undecidability.
}
\item [\checkbox]  Intro to Automata Theory, Languages, and Computation (Hopcroft) | \textbf{ 10. Intractable Problems.
}
\item [\checkbox]  Intro to Automata Theory, Languages, and Computation (Hopcroft) | \textbf{ 11. Additional Classes of Problems.
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 1. Another Pleasant Valley Saturday
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 1.1. It's All in the Plan
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 1.2. Had This Been the Real Thing...
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 1.3. Do Not Pass Go
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 1.4. Assembly Language Programming As a Board Game
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 2. Alien Bases
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 2.1. The Return of the New Math Monster
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 2.2. Counting in Martian
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 2.3. Octal: How the Grinch Stole Eight and Nine
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 2.4. Hexadecimal: Solving the Digit Shortage
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 2.5. From Hex to Decimal and from Decimal to Hex
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 2.6. Arithmetic in Hex
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 2.7. Binary
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 2.8. Hexadecimal As Shorthand for Binary
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 3. Lifting the Hood
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 3.1. RAXie, We Hardly Knew Ye...
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 3.2. Switches, Transistors, and Memory
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 3.3. The Shop Foreman and the Assembly Line
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 3.4. The Box That Follows a Plan
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 3.5. What vs. How: Architecture and Microarchitecture
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 3.6. Enter the Plant Manager
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 4. Location, Location, Location
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 4.1. The Joy of Memory Models
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 4.2. The Nature of Segments
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 4.3. 16-Bit and 32-Bit Registers
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 4.4. The Three Major Assembly Programming Models
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 4.5. What Protected Mode Won't Let Us Do Anymore
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 4.6. Looking Ahead: 64-Bit "Long Mode"
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 5. The Right to Assemble
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 5.1. Files and What's Inside Them
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 5.2. Text In, Code Out
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 5.3. The Assembly Language Development Process
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 5.4. Taking a Trip Down Assembly Lane
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 6. A Place to Stand, with Access to Tools
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 6.1. The Kate Editor
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 6.2. Linux and Terminals
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 6.3. Using Linux Make
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 6.4. The Insight Debugger
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 7. Following Your Instructions
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 7.1. Build Yourself a Sandbox
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 7.2. Instructions and Their Operands
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 7.3. Rally Round the Flags, Boys!
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 7.4. Signed and Unsigned Values
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 7.5. Implicit Operands and MUL
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 7.6. Reading and Using an Assembly Language Reference
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 7.7. NEG: Negate (Two's Complement; i.e., Multiply by −1)
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 8. Our Object All Sublime
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 8.1. The Bones of an Assembly Language Program
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 8.2. Last In, First Out via the Stack
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 8.3. Using Linux Kernel Services Through INT80
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 8.4. Designing a Non-Trivial Program
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 9. Bits, Flags, Branches, and Tables
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 9.1. Bits Is Bits (and Bytes Is Bits)
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 9.2. Shifting Bits
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 9.3. Bit-Bashing in Action
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 9.4. Flags, Tests, and Branches
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 9.5. Protected Mode Memory Addressing in Detail
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 9.6. Character Table Translation
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 9.7. Tables Instead of Calculations
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 10. Dividing and Conquering
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 10.1. Boxes within Boxes
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 10.2. Calling and Returning
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 10.3. Local Labels and the Lengths of Jumps
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 10.4. Building External Procedure Libraries
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 10.5. The Art of Crafting Procedures
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 10.6. Simple Cursor Control in the Linux Console
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 10.7. Creating and Using Macros
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 11. Strings and Things
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 11.1. The Notion of an Assembly Language String
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 11.2. REP STOSB, the Software Machine Gun
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 11.3. The Semiautomatic Weapon: STOSB without REP
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 11.4. MOVSB: Fast Block Copies
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 11.5. Storing Data to Discontinuous Strings
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 11.6. Command-Line Arguments and Examining the Stack
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 11.7. String Searches with SCASB
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 12. Heading Out to C
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 12.1. What's GNU?
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 12.2. Linking to the Standard C Library
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 12.3. Formatted Text Output with printf()
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 12.4. Data In with fgets() and scanf()
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 12.5. Be a Time Lord
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 12.6. Understanding AT&T Instruction Mnemonics
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 12.7. Generating Random Numbers
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 12.8. How C Sees Command-Line Arguments
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 12.9. Simple File I/O
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ 13. Conclusion: Not the End, But Only the Beginning
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A. Partial x86 Instruction Set Reference
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.1. Notes on the Instruction Set Reference
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.2. AAA: Adjust AL after BCD Addition
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.3. ADC: Arithmetic Addition with Carry
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.4. ADD: Arithmetic Addition
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.5. AND: Logical AND
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.6. BT: Bit Test
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.7. CALL: Call Procedure
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.8. CLC: Clear Carry Flag (CF)
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.9. CLD: Clear Direction Flag (DF)
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.10. CMP: Arithmetic Comparison
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.11. DEC: Decrement Operand
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.12. DIV: Unsigned Integer Division
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.13. INC: Increment Operand
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.14. INT: Software Interrupt
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.15. IRET: Return from Interrupt
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.16. J?: Jump on Condition
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.17. JCXZ: Jump If CX = 0
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.18. JECXZ: Jump If ECX = 0
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.19. JMP: Unconditional Jump
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.20. LEA: Load Effective Address
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.21. LOOP: Loop until CX/ECX = 0
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.22. LOOPNZ/LOOPNE: Loop While CX/ECX > 0 and ZF = 0
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.23. LOOPZ/LOOPE: Loop While CX/ECX > 0 and ZF = 1
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.24. MOV: Move (Copy) Right Operand into Left Operand
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.25. MOVS: Move String
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.26. MOVSX: Move (Copy) with Sign Extension
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.27. MUL: Unsigned Integer Multiplication
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.28. NEG: Negate (Two's Complement; i.e., Multiply by -1)
}
\item [\checkbox] Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.29. NOP: No Operation
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.30. NOT: Logical NOT (One's Complement)
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.31. OR: Logical OR
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.32. POP: Pop Top of Stack into Operand
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.33. POPA/POPAD: Pop All GP Registers
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.34. POPF: Pop Top of Stack into 16-Bit Flags
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.35. POPFD: Pop Top of Stack into EFlags
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.36. PUSH: Push Operand onto Top of Stack
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.37. PUSHA: Push All 16-Bit GP Registers
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.38. PUSHAD: Push All 32-Bit GP Registers
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.39. PUSHF: Push 16-Bit Flags onto Stack
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.40. PUSHFD: Push 32-Bit EFlags onto Stack
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.41. RET: Return from Procedure
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.42. ROL: Rotate Left
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.43. ROR: Rotate Right
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.44. SBB: Arithmetic Subtraction with Borrow
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.45. SHL: Shift Left
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.46. SHR: Shift Right
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.47. STC: Set Carry Flag (CF)
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.48. STD: Set Direction Flag (DF)
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.49. STOS: Store String
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.50. SUB: Arithmetic Subtraction
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.51. XCHG: Exchange Operands
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.52. XLAT: Translate Byte via Table
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ A.53. XOR: Exclusive Or
}
\item [\checkbox]  Assembly Language Step-by-Step. Programming with Linux | \textbf{ B. Character Set Charts
}
\item [\checkbox]  The Art of Assembly Language Programming | \textbf{ 1. Hello, World of Assembly Language
}
\item [\checkbox]  The Art of Assembly Language Programming | \textbf{ 2. Data Representation
}
\item [\checkbox]  The Art of Assembly Language Programming | \textbf{ 3. Memory Access and Organization
}
\item [\checkbox]  The Art of Assembly Language Programming | \textbf{ 4. Constants, Variables, and Data Types
}
\item [\checkbox]  The Art of Assembly Language Programming | \textbf{ 5. Procedures and Units
}
\item [\checkbox]  The Art of Assembly Language Programming | \textbf{ 6. Arithmetic
}
\item [\checkbox]  The Art of Assembly Language Programming | \textbf{ 7. Low-Level Control Structures
}
\item [\checkbox]  The Art of Assembly Language Programming | \textbf{ 8. Advanced Arithmetic
}
\item [\checkbox]  The Art of Assembly Language Programming | \textbf{ 9. Macros and the HLA Compile-Time Language
}
\item [\checkbox]  The Art of Assembly Language Programming | \textbf{ 10. Bit Manipulation
}
\item [\checkbox]  The Art of Assembly Language Programming | \textbf{ 11. The String Instructions
}
\item [\checkbox]  The Art of Assembly Language Programming | \textbf{ 12. Classes and Objects
}
\item [\checkbox]  The Annotated Turing | \textbf{ 1. This Tomb Holds Diophantus
}
\item [\checkbox]  The Annotated Turing | \textbf{ 2. The Irrational and the Transcendental
}
\item [\checkbox]  The Annotated Turing | \textbf{ 3. Centuries of Progress
}
\item [\checkbox]  The Annotated Turing | \textbf{ 4. The Education of Alan Turing
}
\item [\checkbox]  The Annotated Turing | \textbf{ 5. Machines at Work
}
\item [\checkbox]  The Annotated Turing | \textbf{ 6. Addition and Multiplication
}
\item [\checkbox]  The Annotated Turing | \textbf{ 7. Also Known as Subroutines
}
\item [\checkbox]  The Annotated Turing | \textbf{ 8. Everything is a Number
}
\item [\checkbox]  The Annotated Turing | \textbf{ 9. The Universal Machine
}
\item [\checkbox]  The Annotated Turing | \textbf{ 10. Computers and Computability
}
\item [\checkbox]  The Annotated Turing | \textbf{ 11. Of Machines and Men
}
\item [\checkbox]  The Annotated Turing | \textbf{ 12. Logic and Computability
}
\item [\checkbox]  The Annotated Turing | \textbf{ 13. Computable Functions
}
\item [\checkbox]  The Annotated Turing | \textbf{ 14. The Major Proof
}
\item [\checkbox]  The Annotated Turing | \textbf{ 15. The Lambda Calculus
}
\item [\checkbox]  The Annotated Turing | \textbf{ 16. Conceiving the Continuum
}
\item [\checkbox]  The Annotated Turing | \textbf{ 17. Is Everything a Turing Machine?
}
\item [\checkbox]  The Annotated Turing | \textbf{ 18. The Long Sleep of Diophantus
}
\item [\checkbox]  Processor Microarchitecture | \textbf{ 1. Introduction
}
\item [\checkbox]  Processor Microarchitecture | \textbf{ 2. Caches
}
\item [\checkbox]  Processor Microarchitecture | \textbf{ 3. The Instruction Fetch Unit
}
\item [\checkbox]  Processor Microarchitecture | \textbf{ 4. Decode
}
\item [\checkbox]  Processor Microarchitecture | \textbf{ 5. Allocation
}
\item [\checkbox]  Processor Microarchitecture | \textbf{ 6. The Issue Stage
}
\item [\checkbox]  Processor Microarchitecture | \textbf{ 7. Execute
}
\item [\checkbox]  Processor Microarchitecture | \textbf{ 8. The Commit Stage
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 1.1. STRUCTURED COMPUTER ORGANIZATION 2
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 1.2. MILESTONES IN COMPUTER ARCHITECTURE 13
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 1.3. THE COMPUTER ZOO 28
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 1.4. EXAMPLE COMPUTER FAMILIES 39
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 1.5. METRIC UNITS 49
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 1.6. OUTLINE OF THIS BOOK 50
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 2.2. PRIMARYMEMORY 73
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 2.3. SECONDARYMEMORY 86
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 2.4. INPUT/OUTPUT 108
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 2.5. SUMMARY 142
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 3.1. GATES AND BOOLEAN ALGEBRA 147
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 3.3. MEMORY 169
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 3.4. CPU CHIPS AND BUSES 185
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 3.5. EXAMPLE CPU CHIPS 201
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 3.6. EXAMPLE BUSES 214
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 3.7. INTERFACING 232
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 3.8. SUMMARY 235
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 4.1. AN EXAMPLE MICROARCHITECTURE 243
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 4.2. AN EXAMPLE ISA: IJVM 258
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 4.3. AN EXAMPLE IMPLEMENTATION 267
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 4.4. DESIGN OF THE MICROARCHITECTURE LEVEL 283
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 4.5. IMPROVING PERFORMANCE 305
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 4.6. EXAMPLES OF THE MICROARCHITECTURE LEVEL 324
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 4.7. COMPARISON OF THE I7, OMAP4430, AND ATMEGA168 338
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 4.8. SUMMARY 339
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 5.1. OVERVIEW OF THE ISA LEVEL
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 5.2. DATA TYPES
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 5.3. INSTRUCTION FORMATS
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 5.4. ADDRESSING
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 5.5. INSTRUCTION TYPES
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 5.6. FLOWOF CONTROL
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 5.7. A DETAILED EXAMPLE: THE TOWERS OF HANOI
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 5.8. THE IA-64 ARCHITECTURE AND THE ITANIUM 2
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 5.9. SUMMARY
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 6.1. VIRTUAL MEMORY
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 6.2. VIRTUAL I/O INSTRUCTIONS
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 6.3. VIRTUAL INSTRUCTIONS FOR PARALLEL PROCESSING
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 6.4. EXAMPLE OPERATING SYSTEMS
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 6.5. SUMMARY
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 7.1. INTRODUCTION TO ASSEMBLY LANGUAGE
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 7.2. MACROS
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 7.3. THE ASSEMBLY PROCESS
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 7.4. LINKING AND LOADING
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 7.5. SUMMARY
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 8.1. ON-CHIP PARALELLISM
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 8.2. COPROCESSORS
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 8.3. SHARED-MEMORYMULTIPROCESSORS
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 8.4. MESSAGE-PASSING MULTICOMPUTERS
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 8.5. GRID COMPUTING
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 8.6. SUMMARY
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 9.1. SUGGESTIONS FOR FURTHER READING
}
\item [\checkbox]  Structured Computer Organization | \textbf{ 9.2. ALPHABETICAL BIBLIOGRAPHY
}
\item [\checkbox]  Structured Computer Organization | \textbf{ A.1. FINITE-PRECISION NUMBERS
}
\item [\checkbox]  Structured Computer Organization | \textbf{ A.2. RADIX NUMBER SYSTEMS
}
\item [\checkbox]  Structured Computer Organization | \textbf{ A.3. CONVERSION FROM ONE RADIX TO ANOTHER
}
\item [\checkbox]  Structured Computer Organization | \textbf{ A.4. NEGATIVE BINARY NUMBERS
}
\item [\checkbox]  Structured Computer Organization | \textbf{ A.5. BINARY ARITHMETIC
}
\item [\checkbox]  Structured Computer Organization | \textbf{ B.1. PRINCIPLES OF FLOATING POINT
}
\item [\checkbox]  Structured Computer Organization | \textbf{ B.2. IEEE FLOATING-POINT STANDARD 754
}
\item [\checkbox]  Structured Computer Organization | \textbf{ C.1. OVERVIEW
}
\item [\checkbox]  Structured Computer Organization | \textbf{ C.2. THE 8088 PROCESSOR
}
\item [\checkbox]  Structured Computer Organization | \textbf{ C.3. MEMORY AND ADDRESSING
}
\item [\checkbox]  Structured Computer Organization | \textbf{ C.4. THE 8088 INSTRUCTION SET
}
\item [\checkbox]  Structured Computer Organization | \textbf{ C.5. THE ASSEMBLER
}
\item [\checkbox]  Structured Computer Organization | \textbf{ C.6. THE TRACER
}
\item [\checkbox]  Structured Computer Organization | \textbf{ C.7. GETTING STARTED
}
\item [\checkbox]  Structured Computer Organization | \textbf{ C.8. EXAMPLES
}
\end{itemize}
\end{document}