\documentclass[a4, landscape, 12pt]{article}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[margin=2cm]{geometry}
\usepackage{amssymb}
\usepackage{pifont}
\usepackage{hyperref}
\newcommand{\cmark}{\ding{51}}%
%\newcommand{\xmark}{\ding{55}}%
\newcommand{\checkbox}{$\square$}%
%\newcommand{\checked}{ \rlap{$\square$}{\hspace{1pt}\cmark} }
\newcommand{\checked}{\rlap{\raisebox{0.3ex}{\hspace{0.4ex}\tiny \ding{52}}}$\square$}


\title{Data Science Roadmap}
\author{Isaac Riley}
\date{Last edited on \today}

\begin{document}
\maketitle
\begin{itemize}
\item [\checkbox]  \href{https://nthu-datalab.github.io/ml/slides/Notation.pdf}{\textbf{Notation Sheet}
}
\item [\checkbox]  The Data Science Design Manual \textbf{ 1. What is Data Science?
}
\item [\checkbox]  The Data Science Design Manual \textbf{ 2. Mathematical Preliminaries
}
\item [\checkbox]  The Data Science Design Manual \textbf{ 3. Data Munging
}
\item [\checkbox]  The Data Science Design Manual \textbf{ 4. Scores and Rankings
}
\item [\checkbox]  The Data Science Design Manual \textbf{ 5. Statistical Analysis
}
\item [\checkbox]  The Data Science Design Manual \textbf{ 6. Visualizing Data
}
\item [\checkbox]  The Data Science Design Manual \textbf{ 7. Mathematical Models
}
\item [\checkbox]  The Data Science Design Manual \textbf{ 8. Linear Algebra
}
\item [\checkbox]  The Data Science Design Manual \textbf{ 9. Linear and Logistic Regression
}
\item [\checkbox]  The Data Science Design Manual \textbf{ 10. Distance and Network Methods
}
\item [\checkbox]  The Data Science Design Manual \textbf{ 11. Machine Learning
}
\item [\checkbox]  The Data Science Design Manual \textbf{ 12. Big Data: Achieving Scale
}
\item [\checkbox]  The Data Science Design Manual \textbf{ 13. Coda
}
\item [\checkbox]  Mathematics for Machine Learning \textbf{ 1. Introduction and Motivation
}
\item [\checkbox]  Mathematics for Machine Learning \textbf{ 2. Linear Algebra
}
\item [\checkbox]  Mathematics for Machine Learning \textbf{ 3. Analytic Geometry
}
\item [\checkbox]  Mathematics for Machine Learning \textbf{ 4. Matrix Decompositions
}
\item [\checkbox]  Mathematics for Machine Learning \textbf{ 5. Vector Calculus
}
\item [\checkbox]  Mathematics for Machine Learning \textbf{ 6. Probability and Distributions
}
\item [\checkbox]  Mathematics for Machine Learning \textbf{ 7. Continuous Optimization
}
\item [\checkbox]  Mathematics for Machine Learning \textbf{ 8. When Models Meet Data
}
\item [\checkbox]  Mathematics for Machine Learning \textbf{ 9. Linear Regression
}
\item [\checkbox]  Mathematics for Machine Learning \textbf{ 10. Dimensionality Reduction with PCA
}
\item [\checkbox]  Mathematics for Machine Learning \textbf{ 11. Density Estimation with GMMs
}
\item [\checkbox]  Mathematics for Machine Learning \textbf{ 12. Classification with SVMs
}
\item [\checkbox]  Computing with Data \textbf{ 2. Essential Knowledge: Hardware
}
\item [\checkbox]  Computing with Data \textbf{ 3. Essential Knowledge: Operating Systems
}
\item [\checkbox]  Computing with Data \textbf{ 4. Learning C++
}
\item [\checkbox]  Computing with Data \textbf{ 5. Learning Java
}
\item [\checkbox]  Computing with Data \textbf{ 6. Learning Python and a Few More Things
}
\item [\checkbox]  Computing with Data \textbf{ 7. Learning R
}
\item [\checkbox]  Computing with Data \textbf{ 8. Visualizing Data in R and Python
}
\item [\checkbox]  Computing with Data \textbf{ 9. Processing Data in R and Python
}
\item [\checkbox]  Computing with Data \textbf{ 10. Essential Knowledge: Parallel Programming
}
\item [\checkbox]  Computing with Data \textbf{ 11. Essential Knowledge: Testing
}
\item [\checkbox]  Computing with Data \textbf{ 12. A Few More Things about Programming
}
\item [\checkbox]  Computing with Data \textbf{ 13. Essential Knowledge: Data Stores
}
\item [\checkbox]  Computing with Data \textbf{ 14. Thoughts on System Design for Big Data
}
\item [\checkbox]  Computing with Data \textbf{ 15. Thoughts on Software Craftsmanship
}
\item [\checkbox]  A Concise Introduction to ML (Faul) \textbf{ 1. Introduction
}
\item [\checkbox]  A Concise Introduction to ML (Faul) \textbf{ 2. Probability Theory
}
\item [\checkbox]  A Concise Introduction to ML (Faul) \textbf{ 3. Sampling
}
\item [\checkbox]  A Concise Introduction to ML (Faul) \textbf{ 4. Linear Classification
}
\item [\checkbox]  A Concise Introduction to ML (Faul) \textbf{ 5. Non-Linear Classification
}
\item [\checkbox]  A Concise Introduction to ML (Faul) \textbf{ 6. Clustering
}
\item [\checkbox]  A Concise Introduction to ML (Faul) \textbf{ 7. Dimensionality Reduction
}
\item [\checkbox]  A Concise Introduction to ML (Faul) \textbf{ 8. Regression
}
\item [\checkbox]  A Concise Introduction to ML (Faul) \textbf{ 9. Feature Learning
}
\item [\checkbox]  A Concise Introduction to ML (Faul) \textbf{ A. Matrix Formulae
}
\item [\checkbox]  Data Science Handbook (Shan et al.) \textbf{ 1.
}
\item [\checkbox]  Data Science Handbook (Shan et al.) \textbf{ 2.
}
\item [\checkbox]  Data Science Handbook (Shan et al.) \textbf{ 3.
}
\item [\checkbox]  Data Science Handbook (Shan et al.) \textbf{ 4.
}
\item [\checkbox]  Data Science Handbook (Shan et al.) \textbf{ 5.
}
\item [\checkbox]  Data Science Handbook (Shan et al.) \textbf{ 6.
}
\item [\checkbox]  Data Science Handbook (Shan et al.) \textbf{ 7.
}
\item [\checkbox]  Data Science Handbook (Shan et al.) \textbf{ 8
}
\item [\checkbox]  Data Science Handbook (Shan et al.) \textbf{ 9.
}
\item [\checkbox]  Data Science Handbook (Shan et al.) \textbf{ 10
}
\item [\checkbox]  Data Science Handbook (Shan et al.) \textbf{ 11.
}
\item [\checkbox]  Data Science Handbook (Shan et al.) \textbf{ 12.
}
\item [\checkbox]  Data Science Handbook (Shan et al.) \textbf{ 13.
}
\item [\checkbox]  Data Science Handbook (Shan et al.) \textbf{ 14.
}
\item [\checkbox]  Data Science Handbook (Shan et al.) \textbf{ 15.
}
\item [\checkbox]  Data Science Handbook (Shan et al.) \textbf{ 16.
}
\item [\checkbox]  Data Science Handbook (Shan et al.) \textbf{ 17.
}
\item [\checkbox]  Data Science Handbook (Shan et al.) \textbf{ 18.
}
\item [\checkbox]  Data Science Handbook (Shan et al.) \textbf{ 19.
}
\item [\checkbox]  Data Science Handbook (Shan et al.) \textbf{ 20.
}
\item [\checkbox]  Data Science Handbook (Shan et al.) \textbf{ 21.
}
\item [\checkbox]  Data Science Handbook (Shan et al.) \textbf{ 22.
}
\item [\checkbox]  Data Science Handbook (Shan et al.) \textbf{ 23.
}
\item [\checkbox]  Data Science Handbook (Shan et al.) \textbf{ 24.
}
\item [\checkbox]  Data Science Handbook (Shan et al.) \textbf{ 25.
}
\item [\checkbox]  Mastering ML with Python in Six Steps \textbf{ 1. Getting Started in Python
}
\item [\checkbox]  Mastering ML with Python in Six Steps \textbf{ 2. Introduction to Machine Learning
}
\item [\checkbox]  Mastering ML with Python in Six Steps \textbf{ 3. Fundamentals of Machine Learning
}
\item [\checkbox]  Mastering ML with Python in Six Steps \textbf{ 4. Model Diagnosis and Tuning
}
\item [\checkbox]  Mastering ML with Python in Six Steps \textbf{ 5. Text Mining and Recommender Systems
}
\item [\checkbox]  Mastering ML with Python in Six Steps \textbf{ 6. Deep and Reinforcement Learning
}
\item [\checkbox]  Mastering ML with Python in Six Steps \textbf{ 7. Conclusion
}
\item [\checkbox]  The Data Science Handbook (Cady) \textbf{ 1. Introduction: Becoming a Unicorn
}
\item [\checkbox]  The Data Science Handbook (Cady) \textbf{ 2. The Data Science Road Map
}
\item [\checkbox]  The Data Science Handbook (Cady) \textbf{ 3. Programming Languages
}
\item [\checkbox]  The Data Science Handbook (Cady) \textbf{ 3a. Interlude: My Personal Toolkit
}
\item [\checkbox]  The Data Science Handbook (Cady) \textbf{ 4. Data Munging
}
\item [\checkbox]  The Data Science Handbook (Cady) \textbf{ 5. Visualizations and Simple Metrics
}
\item [\checkbox]  The Data Science Handbook (Cady) \textbf{ 6. Machine Learning Overview
}
\item [\checkbox]  The Data Science Handbook (Cady) \textbf{ 7. Interlude: Feature Extraction Ideas
}
\item [\checkbox]  The Data Science Handbook (Cady) \textbf{ 8. Machine Learning Classification
}
\item [\checkbox]  The Data Science Handbook (Cady) \textbf{ 9. Technical Communication and Documentation
}
\item [\checkbox]  The Data Science Handbook (Cady) \textbf{ 10. Unsupervised Learning
}
\item [\checkbox]  The Data Science Handbook (Cady) \textbf{ 11. Regression
}
\item [\checkbox]  The Data Science Handbook (Cady) \textbf{ 12. Data Encodings and File Formats
}
\item [\checkbox]  The Data Science Handbook (Cady) \textbf{ 13. Big Data
}
\item [\checkbox]  The Data Science Handbook (Cady) \textbf{ 14. Databases
}
\item [\checkbox]  The Data Science Handbook (Cady) \textbf{ 15. Software Engineering Best Practices
}
\item [\checkbox]  The Data Science Handbook (Cady) \textbf{ 16. Natural Language Processing
}
\item [\checkbox]  The Data Science Handbook (Cady) \textbf{ 17. Time Series Analysis
}
\item [\checkbox]  The Data Science Handbook (Cady) \textbf{ 18. Probability
}
\item [\checkbox]  The Data Science Handbook (Cady) \textbf{ 19. Statistics
}
\item [\checkbox]  The Data Science Handbook (Cady) \textbf{ 20. Programming Language Concepts
}
\item [\checkbox]  The Data Science Handbook (Cady) \textbf{ 21. Performance and Computer Memory
}
\item [\checkbox]  The Data Science Handbook (Cady) \textbf{ 22. Computer Memory and Data Structures
}
\item [\checkbox]  The Data Science Handbook (Cady) \textbf{ Maximum Likelihood Estimation and Optimization
}
\item [\checkbox]  The Data Science Handbook (Cady) \textbf{ Advanced Classifiers
}
\item [\checkbox]  The Data Science Handbook (Cady) \textbf{ 25. Stochastic Modeling
}
\item [\checkbox]  The Data Science Handbook (Cady) \textbf{ 25a. Parting Words
}
\item [\checkbox]  Hands-On Machine Learning with Scikit-Learn and TensorFlow 2 \textbf{ The Machine Learning Landscape
}
\item [\checkbox]  Hands-On Machine Learning with Scikit-Learn and TensorFlow 3 \textbf{ End-to-End Machine Learning Project
}
\item [\checkbox]  Hands-On Machine Learning with Scikit-Learn and TensorFlow 4 \textbf{ Classification
}
\item [\checkbox]  Hands-On Machine Learning with Scikit-Learn and TensorFlow 5 \textbf{ Training Models
}
\item [\checkbox]  Hands-On Machine Learning with Scikit-Learn and TensorFlow 6 \textbf{ Support Vector Machines
}
\item [\checkbox]  Hands-On Machine Learning with Scikit-Learn and TensorFlow 7 \textbf{ Decision Trees
}
\item [\checkbox]  Hands-On Machine Learning with Scikit-Learn and TensorFlow 8 \textbf{ Ensemble Learning and Random Forests
}
\item [\checkbox]  Hands-On Machine Learning with Scikit-Learn and TensorFlow 9 \textbf{ Dimensionality Reduction
}
\item [\checkbox]  Hands-On Machine Learning with Scikit-Learn and TensorFlow 10 \textbf{ Unsupervised Learning Techniques
}
\item [\checkbox]  Hands-On Machine Learning with Scikit-Learn and TensorFlow 11 \textbf{ 10. Introduction to Artificial Neural Networks with Keras
}
\item [\checkbox]  Hands-On Machine Learning with Scikit-Learn and TensorFlow 12 \textbf{ 11. Training Deep Neural Networks
}
\item [\checkbox]  Hands-On Machine Learning with Scikit-Learn and TensorFlow 13 \textbf{ 12. Custom Models and Training with TensorFlow
}
\item [\checkbox]  Hands-On Machine Learning with Scikit-Learn and TensorFlow 14 \textbf{ 13. Loading and Preprocessing with TensorFlow
}
\item [\checkbox]  Hands-On Machine Learning with Scikit-Learn and TensorFlow 15 \textbf{ 14. Deep Computer Vision Using Convolutional Neural Networks
}
\item [\checkbox]  Hands-On Machine Learning with Scikit-Learn and TensorFlow 16 \textbf{ 15. Processing Sequences Using RNNs and CNNs
}
\item [\checkbox]  Hands-On Machine Learning with Scikit-Learn and TensorFlow 17 \textbf{ 16. Natural Language Processing with RNNs and Attention
}
\item [\checkbox]  Hands-On Machine Learning with Scikit-Learn and TensorFlow 18 \textbf{ 17. Representation Learning and Generative Learning Using Autoencoders and GANs
}
\item [\checkbox]  Hands-On Machine Learning with Scikit-Learn and TensorFlow 19 \textbf{ 18. Reinforcement Learning
}
\item [\checkbox]  Hands-On Machine Learning with Scikit-Learn and TensorFlow 20 \textbf{ 19. Training and Deploying TensorFlow Models at Scale
}
\item [\checkbox]  Hands-On Machine Learning with Scikit-Learn and TensorFlow 21 \textbf{ A. Exercise Solutions
}
\item [\checkbox]  Hands-On Machine Learning with Scikit-Learn and TensorFlow 22 \textbf{ B. Machine Learning Project Checklist
}
\item [\checkbox]  Hands-On Machine Learning with Scikit-Learn and TensorFlow 23 \textbf{ C. SVM Dual Problem
}
\item [\checkbox]  Hands-On Machine Learning with Scikit-Learn and TensorFlow 24 \textbf{ D. Autodiff
}
\item [\checkbox]  Hands-On Machine Learning with Scikit-Learn and TensorFlow 25 \textbf{ E. Other Popular ANN Architectures
}
\item [\checkbox]  Hands-On Machine Learning with Scikit-Learn and TensorFlow 26 \textbf{ F. Special Data Structures
}
\item [\checkbox]  Hands-On Machine Learning with Scikit-Learn and TensorFlow 27 \textbf{ G. TensorFlow Graphs
}
\item [\checkbox]  Introduction to Applied Linear Algebra Julia Companion \textbf{ 1. Vectors
}
\item [\checkbox]  Introduction to Applied Linear Algebra Julia Companion \textbf{ 2. Linear Functions
}
\item [\checkbox]  Introduction to Applied Linear Algebra Julia Companion \textbf{ 3. Norm and Distance
}
\item [\checkbox]  Introduction to Applied Linear Algebra Julia Companion \textbf{ 4. Clustering
}
\item [\checkbox]  Introduction to Applied Linear Algebra Julia Companion \textbf{ 5. Linear Independence
}
\item [\checkbox]  Introduction to Applied Linear Algebra Julia Companion \textbf{ 6. Matrices
}
\item [\checkbox]  Introduction to Applied Linear Algebra Julia Companion \textbf{ 7. Matrix Examples
}
\item [\checkbox]  Introduction to Applied Linear Algebra Julia Companion \textbf{ 8. Linear Equations
}
\item [\checkbox]  Introduction to Applied Linear Algebra Julia Companion \textbf{ 9. Linear Dynamical Systems
}
\item [\checkbox]  Introduction to Applied Linear Algebra Julia Companion \textbf{ 10. Matrix Multiplication
}
\item [\checkbox]  Introduction to Applied Linear Algebra Julia Companion \textbf{ 11. Matrix Inverses
}
\item [\checkbox]  Introduction to Applied Linear Algebra Julia Companion \textbf{ 12. Least Squares
}
\item [\checkbox]  Introduction to Applied Linear Algebra Julia Companion \textbf{ 13. Least Squares Data Fitting
}
\item [\checkbox]  Introduction to Applied Linear Algebra Julia Companion \textbf{ 14. Least Squares Classification
}
\item [\checkbox]  Introduction to Applied Linear Algebra Julia Companion \textbf{ 15. Multi-Objective Least Squares
}
\item [\checkbox]  Introduction to Applied Linear Algebra Julia Companion \textbf{ 16. Constrained Least Squares
}
\item [\checkbox]  Introduction to Applied Linear Algebra Julia Companion \textbf{ 17. Constrained Least Squares Applications
}
\item [\checkbox]  Introduction to Applied Linear Algebra Julia Companion \textbf{ 18. Nonlinear Least Squares
}
\item [\checkbox]  Introduction to Applied Linear Algebra Julia Companion \textbf{ 19. Constrained Nonlinear Least Squares
}
\item [\checkbox]  Introduction to Applied Linear Algebra Julia Companion \textbf{ A. The VMLS Package
}
\item [\checkbox]  Statistics with Julia \textbf{ 1. Introducing Julia
}
\item [\checkbox]  Statistics with Julia \textbf{ 2. Basic Probability
}
\item [\checkbox]  Statistics with Julia \textbf{ 3. Probabilistic Distributions
}
\item [\checkbox]  Statistics with Julia \textbf{ 4. Processing and Summarizing Data
}
\item [\checkbox]  Statistics with Julia \textbf{ 5. Statistical Inference Concepts
}
\item [\checkbox]  Statistics with Julia \textbf{ 6. Confidence Intervals
}
\item [\checkbox]  Statistics with Julia \textbf{ 7. Hypothesis Testing
}
\item [\checkbox]  Statistics with Julia \textbf{ 8. Linear Regression and Extensions
}
\item [\checkbox]  Statistics with Julia \textbf{ 9. Machine Learning Basics
}
\item [\checkbox]  Statistics with Julia \textbf{ 10. Simulation of Dynamic Models
}
\item [\checkbox]  Statistics with Julia \textbf{ 11. Appendix A - How-to in Julia
}
\item [\checkbox]  Statistics with Julia \textbf{ 12. Appendix B - Additional Julia Features
}
\item [\checkbox]  Statistics with Julia \textbf{ 13. Appendix C - Additional Packages
}
\item [\checkbox]  Julia for Data Science \textbf{ 1: The Groundwork – Julia's Environment
}
\item [\checkbox]  Julia for Data Science \textbf{ 2: Data Munging
}
\item [\checkbox]  Julia for Data Science \textbf{ 3: Data Exploration
}
\item [\checkbox]  Julia for Data Science \textbf{ 4: Deep Dive into Inferential Statistics
}
\item [\checkbox]  Julia for Data Science \textbf{ 5: Making Sense of Data Using Visualization
}
\item [\checkbox]  Julia for Data Science \textbf{ 6: Supervised Machine Learning
}
\item [\checkbox]  Julia for Data Science \textbf{ 7: Unsupervised Machine Learning
}
\item [\checkbox]  Julia for Data Science \textbf{ 8: Creating Ensemble Models
}
\item [\checkbox]  Julia for Data Science \textbf{ 9: Time Series
}
\item [\checkbox]  Julia for Data Science \textbf{ 10: Collaborative Filtering and Recommendation System
}
\item [\checkbox]  Julia for Data Science \textbf{ 11: Introduction to Deep Learning
}
\item [\checkbox]  Flux.jl Docs \textbf{ Building Models - Basics
}
\item [\checkbox]  Flux.jl Docs \textbf{ Building Models - Recurrence
}
\item [\checkbox]  Flux.jl Docs \textbf{ Building Models - Model Reference
}
\item [\checkbox]  Flux.jl Docs \textbf{ Building Models - Loss Functions
}
\item [\checkbox]  Flux.jl Docs \textbf{ Building Models - Regularization
}
\item [\checkbox]  Flux.jl Docs \textbf{ Building Models - Advanced Model Building
}
\item [\checkbox]  Flux.jl Docs \textbf{ Building Models - NNLib
}
\item [\checkbox]  Flux.jl Docs \textbf{ Handling Data - One-Hot Encoding
}
\item [\checkbox]  Flux.jl Docs \textbf{ Handling Data - DataLoader
}
\item [\checkbox]  Flux.jl Docs \textbf{ Training Models - Optimizers
}
\item [\checkbox]  Flux.jl Docs \textbf{ Training Models - Training
}
\item [\checkbox]  Flux.jl Docs \textbf{ GPU Support
}
\item [\checkbox]  Flux.jl Docs \textbf{ Saving and Loading
}
\item [\checkbox]  Flux.jl Docs \textbf{ The Julia Ecosystem
}
\item [\checkbox]  Flux.jl Docs \textbf{ Utility Functions
}
\item [\checkbox]  Flux.jl Docs \textbf{ Performance Tips
}
\item [\checkbox]  Flux.jl Docs \textbf{ Datasets
}
\item [\checkbox]  Flux.jl Docs \textbf{ Community
}
\item [\checkbox]  Artificial Intelligence, Machine Learning, and Deep Learning (Campesato) \textbf{ 1. Introduction to AI
}
\item [\checkbox]  Artificial Intelligence, Machine Learning, and Deep Learning (Campesato) \textbf{ 2. Introduction to Machine Learning
}
\item [\checkbox]  Artificial Intelligence, Machine Learning, and Deep Learning (Campesato) \textbf{ 3. Classifiers in Machine Learning
}
\item [\checkbox]  Artificial Intelligence, Machine Learning, and Deep Learning (Campesato) \textbf{ 4. Deep Learning Introduction
}
\item [\checkbox]  Artificial Intelligence, Machine Learning, and Deep Learning (Campesato) \textbf{ 5. Deep Learning: RNNs and LSTMs
}
\item [\checkbox]  Artificial Intelligence, Machine Learning, and Deep Learning (Campesato) \textbf{ 6. NLP and Reinforcement Learning
}
\item [\checkbox]  Artificial Intelligence, Machine Learning, and Deep Learning (Campesato) \textbf{ 7. A. Introduction to Keras
}
\item [\checkbox]  Artificial Intelligence, Machine Learning, and Deep Learning (Campesato) \textbf{ B. Introduction to TF2
}
\item [\checkbox]  Artificial Intelligence, Machine Learning, and Deep Learning (Campesato) \textbf{ C. Introduction to Pandas
}
\item [\checkbox]  Practical Deep Learning for Cloud, Mobile, & Edge \textbf{ 1. Exploring the Landscape of Artificial Intelligence
}
\item [\checkbox]  Practical Deep Learning for Cloud, Mobile, & Edge \textbf{ 2. What’s in the Picture: Image Classification with Keras
}
\item [\checkbox]  Practical Deep Learning for Cloud, Mobile, & Edge \textbf{ 3. Cats versus Dogs: Transfer Learning in 30 Lines with Keras
}
\item [\checkbox]  Practical Deep Learning for Cloud, Mobile, & Edge \textbf{ 4. Building a Reverse Image Search Engine: Understanding Embeddings
}
\item [\checkbox]  Practical Deep Learning for Cloud, Mobile, & Edge \textbf{ 5. From Novice to Master Predictor: Maximizing Convolutional Neural Network Accuracy
}
\item [\checkbox]  Practical Deep Learning for Cloud, Mobile, & Edge \textbf{ 6. Maximizing Speed and Performance of TensorFlow: A Handy Checklist
}
\item [\checkbox]  Practical Deep Learning for Cloud, Mobile, & Edge \textbf{ 7. Practical Tools, Tips, and Tricks
}
\item [\checkbox]  Practical Deep Learning for Cloud, Mobile, & Edge \textbf{ 8. Cloud APIs for Computer Vision: Up and Running in 15 Minutes
}
\item [\checkbox]  Practical Deep Learning for Cloud, Mobile, & Edge \textbf{ 9. Scalable Inference Serving on Cloud with TensorFlow Serving and KubeFlow
}
\item [\checkbox]  Practical Deep Learning for Cloud, Mobile, & Edge \textbf{ 10. AI in the Browser with TensorFlow.js and ml5.js
}
\item [\checkbox]  Practical Deep Learning for Cloud, Mobile, & Edge \textbf{ 11. Real-Time Object Classification on iOS with Core ML
}
\item [\checkbox]  Practical Deep Learning for Cloud, Mobile, & Edge \textbf{ 12. Not Hotdog on iOS with Core ML and Create ML
}
\item [\checkbox]  Practical Deep Learning for Cloud, Mobile, & Edge \textbf{ 13. Shazam for Food: Developing Android Apps with TensorFlow Lite and ML Kit
}
\item [\checkbox]  Practical Deep Learning for Cloud, Mobile, & Edge \textbf{ 14. Building the Purrfect Cat Locator App with TensorFlow Object Detection API
}
\item [\checkbox]  Practical Deep Learning for Cloud, Mobile, & Edge \textbf{ 15. Becoming a Maker: Exploring Embedded AI at the Edge
}
\item [\checkbox]  Practical Deep Learning for Cloud, Mobile, & Edge \textbf{ 16. Simulating a Self-Driving Car using End-to-End Deep Learning with Keras
}
\item [\checkbox]  Practical Deep Learning for Cloud, Mobile, & Edge \textbf{ 17. Building an Autonomous Car in Under an Hour: Reinforcement Learning with AWS DeepRacer
}
\item [\checkbox]  Pragmatic AI \textbf{ 1. Introduction to Pragmatic AI
}
\item [\checkbox]  Pragmatic AI \textbf{ 2. AI and ML Toolchain
}
\item [\checkbox]  Pragmatic AI \textbf{ 3. Spartan AI Lifecycle
}
\item [\checkbox]  Pragmatic AI \textbf{ 4. Cloud AI Development with Google Cloud Platform
}
\item [\checkbox]  Pragmatic AI \textbf{ 5. Cloud Ai Development with Amazon Web Services
}
\item [\checkbox]  Pragmatic AI \textbf{ 6. Predicting Social-Media Influence in the NBA
}
\item [\checkbox]  Pragmatic AI \textbf{ 7. Creating an Intelligent Slackbot on AWS
}
\item [\checkbox]  Pragmatic AI \textbf{ 8. Finding Project Management Insights from a Github Organization
}
\item [\checkbox]  Pragmatic AI \textbf{ 9. Dynamically Optimizing EC2 Instances on AWS
}
\item [\checkbox]  Pragmatic AI \textbf{ 10. Real Estate
}
\item [\checkbox]  Pragmatic AI \textbf{ 11. Production AI for User Generated Content (UGC)
}
\item [\checkbox]  Pragmatic AI \textbf{ A. AI Accelerators
}
\item [\checkbox]  Pragmatic AI \textbf{ B. Deciding on Cluster Size
}
\item [\checkbox]  Deep Learning with TensorFlow 2 and Keras \textbf{ 1: Neural Network Foundations with TensorFlow 2.0
}
\item [\checkbox]  Deep Learning with TensorFlow 2 and Keras \textbf{ 2: TensorFlow 1.x and 2.x
}
\item [\checkbox]  Deep Learning with TensorFlow 2 and Keras \textbf{ 3: Regression
}
\item [\checkbox]  Deep Learning with TensorFlow 2 and Keras \textbf{ 4: Convolutional Neural Networks
}
\item [\checkbox]  Deep Learning with TensorFlow 2 and Keras \textbf{ 5: Advanced Convolutional Neural Networks
}
\item [\checkbox]  Deep Learning with TensorFlow 2 and Keras \textbf{ 6: Generative Adversarial Networks
}
\item [\checkbox]  Deep Learning with TensorFlow 2 and Keras \textbf{ 7: Word Embeddings
}
\item [\checkbox]  Deep Learning with TensorFlow 2 and Keras \textbf{ 8: Recurrent Neural Networks
}
\item [\checkbox]  Deep Learning with TensorFlow 2 and Keras \textbf{ 9: Autoencoders
}
\item [\checkbox]  Deep Learning with TensorFlow 2 and Keras \textbf{ 10: Unsupervised Learning
}
\item [\checkbox]  Deep Learning with TensorFlow 2 and Keras \textbf{ 11: Reinforcement Learning
}
\item [\checkbox]  Deep Learning with TensorFlow 2 and Keras \textbf{ 12: TensorFlow and Cloud
}
\item [\checkbox]  Deep Learning with TensorFlow 2 and Keras \textbf{ 13: TensorFlow for Mobile and IoT and TensorFlow.js
}
\item [\checkbox]  Deep Learning with TensorFlow 2 and Keras \textbf{ 14: An introduction to AutoML
}
\item [\checkbox]  Deep Learning with TensorFlow 2 and Keras \textbf{ 15: The Math Behind Deep Learning
}
\item [\checkbox]  Deep Learning with TensorFlow 2 and Keras \textbf{ 16: Tensor Processing Unit
}
\item [\checkbox]  Deep Learning (Goodfellow et al., 2016) \textbf{ 1 Introduction
}
\item [\checkbox]  Deep Learning (Goodfellow et al., 2016) \textbf{ 2 Linear Algebra
}
\item [\checkbox]  Deep Learning (Goodfellow et al., 2016) \textbf{ 3 Probability and Information Theory
}
\item [\checkbox]  Deep Learning (Goodfellow et al., 2016) \textbf{ 4 Numerical Computation
}
\item [\checkbox]  Deep Learning (Goodfellow et al., 2016) \textbf{ 5 Machine Learning Basics
}
\item [\checkbox]  Deep Learning (Goodfellow et al., 2016) \textbf{ 6 Feedforward Deep Networks
}
\item [\checkbox]  Deep Learning (Goodfellow et al., 2016) \textbf{ 7 Regularization of Deep or Distributed Models
}
\item [\checkbox]  Deep Learning (Goodfellow et al., 2016) \textbf{ 8 Optimization for Training Deep Models
}
\item [\checkbox]  Deep Learning (Goodfellow et al., 2016) \textbf{ 9 Convolutional Networks
}
\item [\checkbox]  Deep Learning (Goodfellow et al., 2016) \textbf{ 10 Sequence Modeling: Recurrent and Recursive Nets
}
\item [\checkbox]  Deep Learning (Goodfellow et al., 2016) \textbf{ 11 Practical methodology
}
\item [\checkbox]  Deep Learning (Goodfellow et al., 2016) \textbf{ 12 Applications
}
\item [\checkbox]  Deep Learning (Goodfellow et al., 2016) \textbf{ 13 Structured Probabilistic Models for Deep Learning
}
\item [\checkbox]  Deep Learning (Goodfellow et al., 2016) \textbf{ 14 Monte Carlo Methods
}
\item [\checkbox]  Deep Learning (Goodfellow et al., 2016) \textbf{ 15 Linear Factor Models and Auto-Encoders
}
\item [\checkbox]  Deep Learning (Goodfellow et al., 2016) \textbf{ 16 Representation Learning
}
\item [\checkbox]  Deep Learning (Goodfellow et al., 2016) \textbf{ 17 The Manifold Perspective on Representation Learning
}
\item [\checkbox]  Deep Learning (Goodfellow et al., 2016) \textbf{ 18 Confronting the Partition Function
}
\item [\checkbox]  Deep Learning (Goodfellow et al., 2016) \textbf{ 19 Approximate inference
}
\item [\checkbox]  Deep Learning (Goodfellow et al., 2016) \textbf{ 20 Deep Generative Models
}
\item [\checkbox]  Neural Networks and Deep Learning (Michael Nielsen) \textbf{ 1. Using neural nets to recognize handwritten digits
}
\item [\checkbox]  Neural Networks and Deep Learning (Michael Nielsen) \textbf{ 2. How the backpropagation algorithm works
}
\item [\checkbox]  Neural Networks and Deep Learning (Michael Nielsen) \textbf{ 3. Improving the way neural networks learn
}
\item [\checkbox]  Neural Networks and Deep Learning (Michael Nielsen) \textbf{ 4. A visual proof that neural nets can compute any function
}
\item [\checkbox]  Neural Networks and Deep Learning (Michael Nielsen) \textbf{ 5. Why are deep neural networks hard to train?
}
\item [\checkbox]  Neural Networks and Deep Learning (Michael Nielsen) \textbf{ 6. Deep learning
}
\item [\checkbox]  Neural Networks and Deep Learning (Michael Nielsen) \textbf{ A. Is there a simple algorithm for intelligence?
}
\item [\checkbox]  Intro to Deep Learning (Skansi) \textbf{ 1 From Logic to Cognitive Science
}
\item [\checkbox]  Intro to Deep Learning (Skansi) \textbf{ 2 Mathematical and Computational Prerequisites
}
\item [\checkbox]  Intro to Deep Learning (Skansi) \textbf{ 3 Machine Learning Basics
}
\item [\checkbox]  Intro to Deep Learning (Skansi) \textbf{ 4 Feedforward Neural Networks
}
\item [\checkbox]  Intro to Deep Learning (Skansi) \textbf{ 5 Modifications and Extensions to a Feed-Forward Neural Network
}
\item [\checkbox]  Intro to Deep Learning (Skansi) \textbf{ 6 Convolutional Neural Networks
}
\item [\checkbox]  Intro to Deep Learning (Skansi) \textbf{ 7 Recurrent Neural Networks
}
\item [\checkbox]  Intro to Deep Learning (Skansi) \textbf{ 8 Autoencoders
}
\item [\checkbox]  Intro to Deep Learning (Skansi) \textbf{ 9 Neural Language Models
}
\item [\checkbox]  Intro to Deep Learning (Skansi) \textbf{ 10 An Overview of Different Neural Network Architectures
}
\item [\checkbox]  Intro to Deep Learning (Skansi) \textbf{ 11 Conclusion
}
\item [\checkbox]  Deep Learning (Aggarwal) \textbf{ 1. An Introduction to Neural Networks
}
\item [\checkbox]  Deep Learning (Aggarwal) \textbf{ 2. Machine Learning with Shallow Neural Networks
}
\item [\checkbox]  Deep Learning (Aggarwal) \textbf{ 3. Training Deep Neural Networks
}
\item [\checkbox]  Deep Learning (Aggarwal) \textbf{ 4. Teaching Deep Learners to Generalize
}
\item [\checkbox]  Deep Learning (Aggarwal) \textbf{ 5. Radial Basis Function Networks
}
\item [\checkbox]  Deep Learning (Aggarwal) \textbf{ 6. Restricted Boltzmann Machines
}
\item [\checkbox]  Deep Learning (Aggarwal) \textbf{ 7. Recurrent Neural Networks
}
\item [\checkbox]  Deep Learning (Aggarwal) \textbf{ 8. Convolutional Neural Networks
}
\item [\checkbox]  Deep Learning (Aggarwal) \textbf{ 9. Deep Reinforcement Learning
}
\item [\checkbox]  Deep Learning (Aggarwal) \textbf{ 10. Advanced Topics in Deep Learning
}
\item [\checkbox]  Deep Learning for Coders with Fastai and PyTorch \textbf{ 1. Your Deep Learning Journey
}
\item [\checkbox]  Deep Learning for Coders with Fastai and PyTorch \textbf{ 2. From Model to Production
}
\item [\checkbox]  Deep Learning for Coders with Fastai and PyTorch \textbf{ 3. Data Ethics
}
\item [\checkbox]  Deep Learning for Coders with Fastai and PyTorch \textbf{ 4. Under the Hood: Training a Digit Classifier
}
\item [\checkbox]  Deep Learning for Coders with Fastai and PyTorch \textbf{ 5. Image Classification
}
\item [\checkbox]  Deep Learning for Coders with Fastai and PyTorch \textbf{ 6. Other Computer Vision Problems
}
\item [\checkbox]  Deep Learning for Coders with Fastai and PyTorch \textbf{ 7. Training a State-of-the-Art Model
}
\item [\checkbox]  Deep Learning for Coders with Fastai and PyTorch \textbf{ 8. Collaborative Filtering Deep Dive
}
\item [\checkbox]  Deep Learning for Coders with Fastai and PyTorch \textbf{ 9. Tabular Modeling Deep Dive
}
\item [\checkbox]  Deep Learning for Coders with Fastai and PyTorch \textbf{ 10. Data Munging with fastai's Mid-Level API
}
\item [\checkbox]  Deep Learning for Coders with Fastai and PyTorch \textbf{ 11. A Language Model from Scratch
}
\item [\checkbox]  Deep Learning for Coders with Fastai and PyTorch \textbf{ 12. Convolutional Neural Networks
}
\item [\checkbox]  Deep Learning for Coders with Fastai and PyTorch \textbf{ 13. ResNets
}
\item [\checkbox]  Deep Learning for Coders with Fastai and PyTorch \textbf{ 14. Application Architectures Deep Dive
}
\item [\checkbox]  Deep Learning for Coders with Fastai and PyTorch \textbf{ 15. The Training Process
}
\item [\checkbox]  Deep Learning for Coders with Fastai and PyTorch \textbf{ 16. A Neural Net from the Foundations
}
\item [\checkbox]  Deep Learning for Coders with Fastai and PyTorch \textbf{ 17. CNN Interpretation with CAM
}
\item [\checkbox]  Deep Learning for Coders with Fastai and PyTorch \textbf{ 18. A fastai Learner from Scratch
}
\item [\checkbox]  Deep Learning for Coders with Fastai and PyTorch \textbf{ 19. Concluding Thoughts
}
\item [\checkbox]  Pattern Recognition and Machine Learning (Bishop) \textbf{ 1 Introduction
}
\item [\checkbox]  Pattern Recognition and Machine Learning (Bishop) \textbf{ 2 Probability Distributions
}
\item [\checkbox]  Pattern Recognition and Machine Learning (Bishop) \textbf{ 3 Linear Models for Regression
}
\item [\checkbox]  Pattern Recognition and Machine Learning (Bishop) \textbf{ 4 Linear Models for Classification
}
\item [\checkbox]  Pattern Recognition and Machine Learning (Bishop) \textbf{ 5 Neural Networks
}
\item [\checkbox]  Pattern Recognition and Machine Learning (Bishop) \textbf{ 6 Kernel Methods
}
\item [\checkbox]  Pattern Recognition and Machine Learning (Bishop) \textbf{ 7 Sparse Kernel Machines
}
\item [\checkbox]  Pattern Recognition and Machine Learning (Bishop) \textbf{ 8 Graphical Models
}
\item [\checkbox]  Pattern Recognition and Machine Learning (Bishop) \textbf{ 9 Mixture Models and EM
}
\item [\checkbox]  Pattern Recognition and Machine Learning (Bishop) \textbf{ 10 Approximate Inference
}
\item [\checkbox]  Pattern Recognition and Machine Learning (Bishop) \textbf{ 11 Sampling Methods
}
\item [\checkbox]  Pattern Recognition and Machine Learning (Bishop) \textbf{ 12 Continuous Latent Variables
}
\item [\checkbox]  Pattern Recognition and Machine Learning (Bishop) \textbf{ 13 Sequential Data
}
\item [\checkbox]  Pattern Recognition and Machine Learning (Bishop) \textbf{ 14 Combining Model
}
\item [\checkbox]  Pattern Recognition and Machine Learning (Bishop) \textbf{ A Data Sets
}
\item [\checkbox]  Pattern Recognition and Machine Learning (Bishop) \textbf{ B Probability Distributions
}
\item [\checkbox]  Pattern Recognition and Machine Learning (Bishop) \textbf{ C Properties of Matrices
}
\item [\checkbox]  Pattern Recognition and Machine Learning (Bishop) \textbf{ D Calculus of Variations
}
\item [\checkbox]  Pattern Recognition and Machine Learning (Bishop) \textbf{ E Lagrange Multipliers
}
\item [\checkbox]  Machine Learning - An Applied Mathematics Introduction \textbf{ 1. Introduction
}
\item [\checkbox]  Machine Learning - An Applied Mathematics Introduction \textbf{ 2. General Matters
}
\item [\checkbox]  Machine Learning - An Applied Mathematics Introduction \textbf{ 3. K Nearest Neighbors
}
\item [\checkbox]  Machine Learning - An Applied Mathematics Introduction \textbf{ 4. K Means Clustering
}
\item [\checkbox]  Machine Learning - An Applied Mathematics Introduction \textbf{ 5. Naïve Bayes Classifier
}
\item [\checkbox]  Machine Learning - An Applied Mathematics Introduction \textbf{ 6. Regression Methods
}
\item [\checkbox]  Machine Learning - An Applied Mathematics Introduction \textbf{ 7. Support Vector Machines
}
\item [\checkbox]  Machine Learning - An Applied Mathematics Introduction \textbf{ 8. Self-Organizing Maps
}
\item [\checkbox]  Machine Learning - An Applied Mathematics Introduction \textbf{ 9. Decision Trees
}
\item [\checkbox]  Machine Learning - An Applied Mathematics Introduction \textbf{ 10. Neural Networks
}
\item [\checkbox]  Machine Learning - An Applied Mathematics Introduction \textbf{ 11. Reinforcement Learning
}
\item [\checkbox]  Machine Learning - An Applied Mathematics Introduction \textbf{ A. Datasets
}
\item [\checkbox]  Understanding Machine Learning \textbf{ 1. Introduction
}
\item [\checkbox]  Understanding Machine Learning \textbf{ 2. A Gentle Start
}
\item [\checkbox]  Understanding Machine Learning \textbf{ 3. A Formal Learning Model
}
\item [\checkbox]  Understanding Machine Learning \textbf{ 4. Learning via Uniform Convergence
}
\item [\checkbox]  Understanding Machine Learning \textbf{ 5. The Bias-Complexity Trade-off
}
\item [\checkbox]  Understanding Machine Learning \textbf{ 6. The VC-Dimension
}
\item [\checkbox]  Understanding Machine Learning \textbf{ 7. Nonuniform Learnability
}
\item [\checkbox]  Understanding Machine Learning \textbf{ 8. The Runtime of Learning
}
\item [\checkbox]  Understanding Machine Learning \textbf{ 9. Linear Predictors
}
\item [\checkbox]  Understanding Machine Learning \textbf{ 10. Boosting
}
\item [\checkbox]  Understanding Machine Learning \textbf{ 11. Model Selection and Validation
}
\item [\checkbox]  Understanding Machine Learning \textbf{ 12. Convex Learning Problems
}
\item [\checkbox]  Understanding Machine Learning \textbf{ 13. Regularization and Stabiity
}
\item [\checkbox]  Understanding Machine Learning \textbf{ 14. Stochastic Gradient Descent
}
\item [\checkbox]  Understanding Machine Learning \textbf{ 15. Support Vector Machines
}
\item [\checkbox]  Understanding Machine Learning \textbf{ 16. Kernel Methods
}
\item [\checkbox]  Understanding Machine Learning \textbf{ 17. Multiclass, Ranking, and Complex Prediction Problems
}
\item [\checkbox]  Understanding Machine Learning \textbf{ 18. Decision Trees
}
\item [\checkbox]  Understanding Machine Learning \textbf{ 19. Nearest Neighbor
}
\item [\checkbox]  Understanding Machine Learning \textbf{ 20. Neural Networks
}
\item [\checkbox]  Understanding Machine Learning \textbf{ 21. Online Learning
}
\item [\checkbox]  Understanding Machine Learning \textbf{ 22. Clustering
}
\item [\checkbox]  Understanding Machine Learning \textbf{ 23. Dimensionality Reduction
}
\item [\checkbox]  Understanding Machine Learning \textbf{ 24. Generative Models
}
\item [\checkbox]  Understanding Machine Learning \textbf{ 25. Feature Selection and Generation
}
\item [\checkbox]  Understanding Machine Learning \textbf{ 26. Rademacher Complexities
}
\item [\checkbox]  Understanding Machine Learning \textbf{ 27. Covering Numbers
}
\item [\checkbox]  Understanding Machine Learning \textbf{ 28. Proof of the Fundamental Theorem of Learning Theory
}
\item [\checkbox]  Understanding Machine Learning \textbf{ 29. Multiclass Learnability
}
\item [\checkbox]  Understanding Machine Learning \textbf{ 30. Compression Bounds
}
\item [\checkbox]  Understanding Machine Learning \textbf{ 31. PAC-Bayes
}
\item [\checkbox]  Understanding Machine Learning \textbf{ A. Technical Lemmas
}
\item [\checkbox]  Understanding Machine Learning \textbf{ B. Measure Concentration
}
\item [\checkbox]  Understanding Machine Learning \textbf{ C. Linear Algebra
}
\item [\checkbox]  Introduction to Statistical Learning \textbf{ 1. Introduction
}
\item [\checkbox]  Introduction to Statistical Learning \textbf{ 2. Statistical Learning
}
\item [\checkbox]  Introduction to Statistical Learning \textbf{ 3. Linear Regression
}
\item [\checkbox]  Introduction to Statistical Learning \textbf{ 4. Classification
}
\item [\checkbox]  Introduction to Statistical Learning \textbf{ 5. Resampling Methods
}
\item [\checkbox]  Introduction to Statistical Learning \textbf{ 6. Linear Model Selection and Regularization
}
\item [\checkbox]  Introduction to Statistical Learning \textbf{ 7. Moving Beynd Linearity
}
\item [\checkbox]  Introduction to Statistical Learning \textbf{ 8. Tree-Based Methods
}
\item [\checkbox]  Introduction to Statistical Learning \textbf{ 9. Support Vector Machines
}
\item [\checkbox]  Introduction to Statistical Learning \textbf{ 10. Unsupervised Learning
}
\item [\checkbox]  Elements of Statistical Learning \textbf{ 1. Introduction
}
\item [\checkbox]  Elements of Statistical Learning \textbf{ 2. Overview of Supervised Learning
}
\item [\checkbox]  Elements of Statistical Learning \textbf{ 3. Linear Methods for Regression
}
\item [\checkbox]  Elements of Statistical Learning \textbf{ 4. Linear Methods for Classification
}
\item [\checkbox]  Elements of Statistical Learning \textbf{ 5. Basis Expansions and Regularization
}
\item [\checkbox]  Elements of Statistical Learning \textbf{ 6. Kernel Smoothing Methods
}
\item [\checkbox]  gElements of Statistical Learning \textbf{ 7. Model Assessment and Selection
}
\item [\checkbox]  Elements of Statistical Learning \textbf{ 8. Model Inference and Averaging
}
\item [\checkbox]  Elements of Statistical Learning \textbf{ 9. Additive Models, Trees, and Related Methods
}
\item [\checkbox]  Elements of Statistical Learning \textbf{ 10. Boosting and Additive Trees
}
\item [\checkbox]  Elements of Statistical Learning \textbf{ 11. Neural Networks
}
\item [\checkbox]  Elements of Statistical Learning \textbf{ 12. Support Vector Machines and Flexible Discriminants
}
\item [\checkbox]  Elements of Statistical Learning \textbf{ 13. Prototype Methods and Nearest-Neighbors
}
\item [\checkbox]  Elements of Statistical Learning \textbf{ 14. Unsupervised Learning
}
\item [\checkbox]  Elements of Statistical Learning \textbf{ 15. Random Forests
}
\item [\checkbox]  Elements of Statistical Learning \textbf{ 16. Ensemble Learning
}
\item [\checkbox]  Elements of Statistical Learning \textbf{ 17. Undirected Graphical Models
}
\item [\checkbox]  Foundations of Machine Learning \textbf{ 1. Introduction
}
\item [\checkbox]  Foundations of Machine Learning \textbf{ 2. The PAC Learning Framework
}
\item [\checkbox]  Foundations of Machine Learning \textbf{ 3. Rademacher Complexity and VC-Cimension
}
\item [\checkbox]  Foundations of Machine Learning \textbf{ 4. Model Selection
}
\item [\checkbox]  Foundations of Machine Learning \textbf{ 5. Support Vector Machines
}
\item [\checkbox]  Foundations of Machine Learning \textbf{ 6. Kernel Methods
}
\item [\checkbox]  Foundations of Machine Learning \textbf{ 7. Boosting
}
\item [\checkbox]  Foundations of Machine Learning \textbf{ 8. On-Line Learning
}
\item [\checkbox]  Foundations of Machine Learning \textbf{ 9. Multi-Class Classification
}
\item [\checkbox]  Foundations of Machine Learning \textbf{ 10. Ranking
}
\item [\checkbox]  Foundations of Machine Learning \textbf{ 11. Regression
}
\item [\checkbox]  Foundations of Machine Learning \textbf{ 12. Maximum Entropy Models
}
\item [\checkbox]  Foundations of Machine Learning \textbf{ 13. Conditional Maximum Entropy Models
}
\item [\checkbox]  Foundations of Machine Learning \textbf{ 14. Algorithmic Stability
}
\item [\checkbox]  Foundations of Machine Learning \textbf{ 15. Dimensionality Reduction
}
\item [\checkbox]  Foundaions of Machine Learning \textbf{ 16. Learning Automata and Languages
}
\item [\checkbox]  Foundations of Machine Learning \textbf{ 17. Reinforcement Learning
}
\item [\checkbox]  Foundations of Machine Learning \textbf{ A. Linear Algebra Review
}
\item [\checkbox]  Foundations of Machine Learning \textbf{ B. Convex Optimization
}
\item [\checkbox]  Foundations of Machine Learning \textbf{ C. Probability Review
}
\item [\checkbox]  Foundations of Machine Learning \textbf{ D. Concentration Inequalities
}
\item [\checkbox]  Foundations of Machine Learning \textbf{ E. Notions of Information Theory
}
\item [\checkbox]  Reinforcement Learning. An Introduction \textbf{ 1. The Reinforcement Learning Problem
}
\item [\checkbox]  Reinforcement Learning. An Introduction \textbf{ 2. Multi-Armed Bandits
}
\item [\checkbox]  Reinforcement Learning. An Introduction \textbf{ 3. Finite Markov Decision Processes
}
\item [\checkbox]  Reinforcement Learning. An Introduction \textbf{ 4. Dynamic Programming
}
\item [\checkbox]  Reinforcement Learning. An Introduction \textbf{ 5. Monte Carlo Methods
}
\item [\checkbox]  Reinforcement Learning. An Introduction \textbf{ 6. Temporal-Difference Learning
}
\item [\checkbox]  Reinforcement Learning. An Introduction \textbf{ 7. Multi-Step Bootstrapping
}
\item [\checkbox]  Reinforcement Learning. An Introduction \textbf{ 8. Planning and Learning with Tabular Methods
}
\item [\checkbox]  Reinforcement Learning. An Introduction \textbf{ 9. On-Policy Prediction with Approximation
}
\item [\checkbox]  Reinforcement Learning. An Introduction \textbf{ 10. On-Policy Control with Approximation
}
\item [\checkbox]  Reinforcement Learning. An Introduction \textbf{ 11. Off-Policy Methods with Approximation
}
\item [\checkbox]  Reinforcement Learning. An Introduction \textbf{ 12. Eligibility Traces
}
\item [\checkbox]  Reinforcement Learning. An Introduction \textbf{ 13. Policy Gradient Methods
}
\item [\checkbox]  Reinforcement Learning. An Introduction \textbf{ 14. Psychology
}
\item [\checkbox]  Reinforcement Learning. An Introduction \textbf{ 15. Neuroscience
}
\item [\checkbox]  Reinforcement Learning. An Introduction \textbf{ 16. Applications and Case Studies
}
\item [\checkbox]  Reinforcement Learning. An Introduction \textbf{ 17. Frontiers
}
\item [\checkbox]  Introduction to Machine Learning (Alpaydin) \textbf{ 1. Introduction
}
\item [\checkbox]  Introduction to Machine Learning (Alpaydin) \textbf{ 2. Supervised Learning
}
\item [\checkbox]  Introduction to Machine Learning (Alpaydin) \textbf{ 3. Bayesian Decision Theory
}
\item [\checkbox]  Introduction to Machine Learning (Alpaydin) \textbf{ 4. Parametric Methods
}
\item [\checkbox]  Introduction to Machine Learning (Alpaydin) \textbf{ 5. Multivariate Methods
}
\item [\checkbox]  Introduction to Machine Learning (Alpaydin) \textbf{ 6. Dimensionality Reduction
}
\item [\checkbox]  Introduction to Machine Learning (Alpaydin) \textbf{ 7. Clustering
}
\item [\checkbox]  Introduction to Machine Learning (Alpaydin) \textbf{ 8. Nonparametric Methods
}
\item [\checkbox]  Introduction to Machine Learning (Alpaydin) \textbf{ 9. Decision Trees
}
\item [\checkbox]  Introduction to Machine Learning (Alpaydin) \textbf{ 10. Linear Discrimination
}
\item [\checkbox]  Introduction to Machine Learning (Alpaydin) \textbf{ 11. Multilayer Perceptrons
}
\item [\checkbox]  Introduction to Machine Learning (Alpaydin) \textbf{ 12. Local Models
}
\item [\checkbox]  Introduction to Machine Learning (Alpaydin) \textbf{ 13. Kernel Machines
}
\item [\checkbox]  Introduction to Machine Learning (Alpaydin) \textbf{ 14. Graphical Models
}
\item [\checkbox]  Introduction to Machine Learning (Alpaydin) \textbf{ 15. Hidden Markov Models
}
\item [\checkbox]  Introduction to Machine Learning (Alpaydin) \textbf{ 16. Bayesian Estimation
}
\item [\checkbox]  Introduction to Machine Learning (Alpaydin) \textbf{ 17. Combining Multiple Learners
}
\item [\checkbox]  Introduction to Machine Learning (Alpaydin) \textbf{ 18. Reinforcement Learning
}
\item [\checkbox]  Introduction to Machine Learning (Alpaydin) \textbf{ 19. Design and Analysis of Machine Learning Experiments
}
\item [\checkbox]  Introduction to Machine Learning (Alpaydin) \textbf{ A. Probability
}
\item [\checkbox]  Machine Learning (Alpaydin 2020) \textbf{ 1. Introduction
}
\item [\checkbox]  Machine Learning (Alpaydin 2020) \textbf{ 2. Supervised Learning
}
\item [\checkbox]  Machine Learning (Alpaydin 2020) \textbf{ 3. Bayesian Decision Theory
}
\item [\checkbox]  Machine Learning (Alpaydin 2020) \textbf{ 4. Parametric Methods
}
\item [\checkbox]  Machine Learning (Alpaydin 2020) \textbf{ 5. Multivariate Methods
}
\item [\checkbox]  Machine Learning (Alpaydin 2020) \textbf{ 6. Dimensionality Reduction
}
\item [\checkbox]  Machine Learning (Alpaydin 2020) \textbf{ 7. Clustering
}
\item [\checkbox]  Machine Learning (Alpaydin 2020) \textbf{ 8. Nonparametric Methods
}
\item [\checkbox]  Machine Learning (Alpaydin 2020) \textbf{ 9. Decision Trees
}
\item [\checkbox]  Machine Learning (Alpaydin 2020) \textbf{ 10. Linear Discrimination
}
\item [\checkbox]  Machine Learning (Alpaydin 2020) \textbf{ 11. Multilayer Perceptrons
}
\item [\checkbox]  Machine Learning (Alpaydin 2020) \textbf{ 12. Deep Learning
}
\item [\checkbox]  Machine Learning (Alpaydin 2020) \textbf{ 13. Local Models
}
\item [\checkbox]  Machine Learning (Alpaydin 2020) \textbf{ 14. Kernel Machines
}
\item [\checkbox]  Machine Learning (Alpaydin 2020) \textbf{ 15. Graphical Models
}
\item [\checkbox]  Machine Learning (Alpaydin 2020) \textbf{ 16. Hidden Markov Models
}
\item [\checkbox]  Machine Learning (Alpaydin 2020) \textbf{ 17. Bayesian Estimation
}
\item [\checkbox]  Machine Learning (Alpaydin 2020) \textbf{ 18. Combining Multiple Learners
}
\item [\checkbox]  Machine Learning (Alpaydin 2020) \textbf{ 19. Reinforcement Learning
}
\item [\checkbox]  Machine Learning (Alpaydin 2020) \textbf{ 20. Design and Analysis of Machine Learning Experiments
}
\item [\checkbox]  Machine Learning (Alpaydin 2020) \textbf{ A. Probability
}
\item [\checkbox]  Machine Learning (Alpaydin 2020) \textbf{ B. Linear Algebra
}
\item [\checkbox]  Machine Learning (Alpaydin 2020) \textbf{ C. Optimization
}
\item [\checkbox]  Artificial Intelligence (Norvig) \textbf{ I. Artificial Intelligence
}
\item [\checkbox]  Artificial Intelligence (Norvig) \textbf{ 1 Introduction
}
\item [\checkbox]  Artificial Intelligence (Norvig) \textbf{ 2 Intelligent Agents
}
\item [\checkbox]  Artificial Intelligence (Norvig) \textbf{ II. Problem-solving
}
\item [\checkbox]  Artificial Intelligence (Norvig) \textbf{ 3 Solving Problems by Searching
}
\item [\checkbox]  Artificial Intelligence (Norvig) \textbf{ 4 Search in Complex Environments
}
\item [\checkbox]  Artificial Intelligence (Norvig) \textbf{ 5 Adversarial Search and Games
}
\item [\checkbox]  Artificial Intelligence (Norvig) \textbf{ 6 Constraint Satisfaction Problems
}
\item [\checkbox]  Artificial Intelligence (Norvig) \textbf{ III. Knowledge, reasoning, and planning
}
\item [\checkbox]  Artificial Intelligence (Norvig) \textbf{ 7 Logical Agents
}
\item [\checkbox]  Artificial Intelligence (Norvig) \textbf{ 8 First-Order Logic
}
\item [\checkbox]  Artificial Intelligence (Norvig) \textbf{ 9 Inference in First-Order Logic
}
\item [\checkbox]  Artificial Intelligence (Norvig) \textbf{ 10 Knowledge Representation
}
\item [\checkbox]  Artificial Intelligence (Norvig) \textbf{ 11 Automated Planning
}
\item [\checkbox]  Artificial Intelligence (Norvig) \textbf{ IV. Uncertain knowledge and reasoning
}
\item [\checkbox]  Artificial Intelligence (Norvig) \textbf{ 12 Quantifying Uncertainty
}
\item [\checkbox]  Artificial Intelligence (Norvig) \textbf{ 13 Probabilistic Reasoning
}
\item [\checkbox]  Artificial Intelligence (Norvig) \textbf{ 14 Probabilistic Reasoning over Time
}
\item [\checkbox]  Artificial Intelligence (Norvig) \textbf{ 15 Probabilistic Programming
}
\item [\checkbox]  Artificial Intelligence (Norvig) \textbf{ 16 Making Simple Decisions
}
\item [\checkbox]  Artificial Intelligence (Norvig) \textbf{ 17 Making Complex Decisions
}
\item [\checkbox]  Artificial Intelligence (Norvig) \textbf{ 18 Multiagent Decision Making
}
\item [\checkbox]  Artificial Intelligence (Norvig) \textbf{ V. Machine Learning
}
\item [\checkbox]  Artificial Intelligence (Norvig) \textbf{ 19 Learning from Examples
}
\item [\checkbox]  Artificial Intelligence (Norvig) \textbf{ 20 Learning Probabilistic Models
}
\item [\checkbox]  Artificial Intelligence (Norvig) \textbf{ 21 Deep Learning
}
\item [\checkbox]  Artificial Intelligence (Norvig) \textbf{ 22 Reinforcement Learning
}
\item [\checkbox]  Artificial Intelligence (Norvig) \textbf{ VI. Communicating, perceiving, and acting
}
\item [\checkbox]  Artificial Intelligence (Norvig) \textbf{ 23 Natural Language Processing
}
\item [\checkbox]  Artificial Intelligence (Norvig) \textbf{ 24 Deep Learning for Natural Language Processin
}
\item [\checkbox]  Artificial Intelligence (Norvig) \textbf{ 25 Computer Vision
}
\item [\checkbox]  Artificial Intelligence (Norvig) \textbf{ 26 Robotics
}
\item [\checkbox]  Artificial Intelligence (Norvig) \textbf{ VII. Conclusions
}
\item [\checkbox]  Artificial Intelligence (Norvig) \textbf{ 27 Philosophy, Ethics, and Safety of AI
}
\item [\checkbox]  Artificial Intelligence (Norvig) \textbf{ 28 The Future of AI
}
\item [\checkbox]  Artificial Intelligence (Norvig) \textbf{ A: Mathematical Background
}
\item [\checkbox]  Artificial Intelligence (Norvig) \textbf{ B: Notes on Languages and Algorithms
}
\item [\checkbox]  Machine Learning Hands-on for Developers and Technical Professionals \textbf{
}
\item [\checkbox]  Machine Learning Hands-on for Developers and Technical Professionals \textbf{ 1. What Is 
Machine Learning?
}
\item [\checkbox]  Machine Learning Hands-on for Developers and Technical Professionals \textbf{ 2. Planning for Machine Learning
}
\item [\checkbox]  Machine Learning Hands-on for Developers and Technical Professionals \textbf{ 3. Data Acquisition Techniques
}
\item [\checkbox]  Machine Learning Hands-on for Developers and Technical Professionals \textbf{ 4. Statistics, Linear Regression, and Randomness
}
\item [\checkbox]  Machine Learning Hands-on for Developers and Technical Professionals \textbf{ 5. Working with Decision Trees
}
\item [\checkbox]  Machine Learning Hands-on for Developers and Technical Professionals \textbf{ 6. Clustering
}
\item [\checkbox]  Machine Learning Hands-on for Developers and Technical Professionals \textbf{ 7. Association Rules Learning
}
\item [\checkbox]  Machine Learning Hands-on for Developers and Technical Professionals \textbf{ 8. Support Vector Machines
}
\item [\checkbox]  Machine Learning Hands-on for Developers and Technical Professionals \textbf{ 9. Artificial Neural Networks
}
\item [\checkbox]  Machine Learning Hands-on for Developers and Technical Professionals \textbf{ 10. Machine Learning with Text Documents
}
\item [\checkbox]  Machine Learning Hands-on for Developers and Technical Professionals \textbf{ 11. Machine Learning with Images
}
\item [\checkbox]  Machine Learning Hands-on for Developers and Technical Professionals \textbf{ 12. Machine Learning Streaming with Kafka
}
\item [\checkbox]  Machine Learning Hands-on for Developers and Technical Professionals \textbf{ 13. Apache Spark
}
\item [\checkbox]  Machine Learning Hands-on for Developers and Technical Professionals \textbf{ 14. Machine Learning with R
}
\item [\checkbox]  Machine Learning Hands-on for Developers and Technical Professionals \textbf{ A. Kafka Quick Start
}
\item [\checkbox]  Machine Learning Hands-on for Developers and Technical Professionals \textbf{ B. The Twitter API Developer Application Configuration
}
\item [\checkbox]  Machine Learning Hands-on for Developers and Technical Professionals \textbf{ C. Useful Unix Commands
}
\item [\checkbox]  Machine Learning Hands-on for Developers and Technical Professionals \textbf{ D. Further Reading
}
\item [\checkbox]  Algorithms for Data Science \textbf{ 1. Introduction
}
\item [\checkbox]  Algorithms for Data Science \textbf{ 2. Data Reduction
}
\item [\checkbox]  Algorithms for Data Science \textbf{ 2.1. Data Mapping and Data Dictionaries
}
\item [\checkbox]  Algorithms for Data Science \textbf{ 2.2. Scalable Algorithms and Associative Statistics
}
\item [\checkbox]  Algorithms for Data Science \textbf{ 2.3. Hadoop and MapReduce
}
\item [\checkbox]  Algorithms for Data Science \textbf{ 3. Extracting Information from Data
}
\item [\checkbox]  Algorithms for Data Science \textbf{ 3.1. Data Visualization
}
\item [\checkbox]  Algorithms for Data Science \textbf{ 3.2. Linear Regression Methods
}
\item [\checkbox]  Algorithms for Data Science \textbf{ 3.3. Healthcare Analytics
}
\item [\checkbox]  Algorithms for Data Science \textbf{ 3.4. Cluster Analysis
}
\item [\checkbox]  Algorithms for Data Science \textbf{ 4.Predictive Analytics
}
\item [\checkbox]  Algorithms for Data Science \textbf{ 4.1. k-Nearest Neighbor Prediction Functions
}
\item [\checkbox]  Algorithms for Data Science \textbf{ 4.2. The Multinomial Naïve Bayes Prediction Function
}
\item [\checkbox]  Algorithms for Data Science \textbf{ 4.3. Forecasting
}
\item [\checkbox]  Algorithms for Data Science \textbf{ 4.4. Real-time Analytics
}
\item [\checkbox]  Machine Learning - An Algorithmic Perspective \textbf{ 1. Introduction
}
\item [\checkbox]  Machine Learning - An Algorithmic Perspective \textbf{ 2. Linear Discriminants
}
\item [\checkbox]  Machine Learning - An Algorithmic Perspective \textbf{ 3. The Multi-Layer Perceptron
}
\item [\checkbox]  Machine Learning - An Algorithmic Perspective \textbf{ 4. Radial Basis Functions and Splines
}
\item [\checkbox]  Machine Learning - An Algorithmic Perspective \textbf{ 5. Support Vector Machines
}
\item [\checkbox]  Machine Learning - An Algorithmic Perspective \textbf{ 6. Learning With Trees
}
\item [\checkbox]  Machine Learning - An Algorithmic Perspective \textbf{ 7. Decision by Committee: Ensemble Learning
}
\item [\checkbox]  Machine Learning - An Algorithmic Perspective \textbf{ 8. Probability and Learning
}
\item [\checkbox]  Machine Learning - An Algorithmic Perspective \textbf{ 9. Unsupervised Learning
}
\item [\checkbox]  Machine Learning - An Algorithmic Perspective \textbf{ 10. Dimensionality Reduction
}
\item [\checkbox]  Machine Learning - An Algorithmic Perspective \textbf{ 11. Optimisation and Search
}
\item [\checkbox]  Machine Learning - An Algorithmic Perspective \textbf{ 12. Evolutionary Learning
}
\item [\checkbox]  Machine Learning - An Algorithmic Perspective \textbf{ 13. Reinforcement Learning
}
\item [\checkbox]  Machine Learning - An Algorithmic Perspective \textbf{ 14. Markov Chain Monte Carlo (MCMC) Methods
}
\item [\checkbox]  Machine Learning - An Algorithmic Perspective \textbf{ 15. Graphical Models
}
\item [\checkbox]  Machine Learning - An Algorithmic Perspective \textbf{ 16. Python
}
\item [\checkbox]  Learning from Data \textbf{ 1. Introduction
}
\item [\checkbox]  Learning from Data \textbf{ 2. Problem Statement, Classical Approaches, and Adaptive Learning
}
\item [\checkbox]  Learning from Data \textbf{ 3. Regularization Framework
}
\item [\checkbox]  Learning from Data \textbf{ 4. Statistical Learning Theory
}
\item [\checkbox]  Learning from Data \textbf{ 5. Nonlinear Optimization Strategies
}
\item [\checkbox]  Learning from Data \textbf{ 6. Methods for Data Reduction and Dimensionality Reduction
}
\item [\checkbox]  Learning from Data \textbf{ 7. Methods for Regression
}
\item [\checkbox]  Learning from Data \textbf{ 8. Classification
}
\item [\checkbox]  Learning from Data \textbf{ 9. Support Vector Machines
}
\item [\checkbox]  Learning from Data \textbf{ 10. Non-Inductive Inference and Alternative Learning Formulations
}
\item [\checkbox]  Learning from Data \textbf{ A. Review of Nonlinear Optimization
}
\item [\checkbox]  Learning from Data \textbf{ B. Eigenvalues and Singular Value Decomposition
}
\item [\checkbox]  \textbf{An Overview of Statistical Learning Theory}

\item [\checkbox]  Statistical Learning Theory Notes (Liang) \textbf{ 1. Overview
}
\item [\checkbox]  Statistical Learning Theory Notes (Liang) \textbf{ 2. Asymptotics
}
\item [\checkbox]  Statistical Learning Theory Notes (Liang) \textbf{ 3. Uniform Convergence
}
\item [\checkbox]  Statistical Learning Theory Notes (Liang) \textbf{ 4. Kernel Methods
}
\item [\checkbox]  Statistical Learning Theory Notes (Liang) \textbf{ 5. Online Learning
}
\item [\checkbox]  Statistical Learning Theory Notes (Liang) \textbf{ 6. Neural Networks
}
\item [\checkbox]  Statistical Learning Theory Notes (Liang) \textbf{ 7. Conclusions and Outlook
}
\item [\checkbox]  Statistical Learning Theory Notes (Liang) \textbf{ A. Appendi
}
\item [\checkbox]  Machine Learning (Flach) \textbf{ Prologue: A machine learning sampler
}
\item [\checkbox]  Machine Learning (Flach) \textbf{ 1. The ingredients of machine learning
}
\item [\checkbox]  Machine Learning (Flach) \textbf{ 2. Binary classification and related tasks
}
\item [\checkbox]  Machine Learning (Flach) \textbf{ 3. Beyond binary classification
}
\item [\checkbox]  Machine Learning (Flach) \textbf{ 4. Concept learning
}
\item [\checkbox]  Machine Learning (Flach) \textbf{ 5. Tree models
}
\item [\checkbox]  Machine Learning (Flach) \textbf{ 6. Rule models
}
\item [\checkbox]  Machine Learning (Flach) \textbf{ 7. Linear models
}
\item [\checkbox]  Machine Learning (Flach) \textbf{ 8. Distance-based models
}
\item [\checkbox]  Machine Learning (Flach) \textbf{ 9. Probabilistic models
}
\item [\checkbox]  Machine Learning (Flach) \textbf{ 10. Features
}
\item [\checkbox]  Machine Learning (Flach) \textbf{ 11. Model ensembles
}
\item [\checkbox]  Machine Learning (Flach) \textbf{ 12. Machine learning experiments
}
\item [\checkbox]  Machine Learning (Flach) \textbf{ A. Epilogue: Where to go from here
}
\item [\checkbox]  Machine Learning (Flach) \textbf{ B. Important points to remember
}
\item [\checkbox]  A Guide to CNNs for CV \textbf{ 1. Introduction
}
\item [\checkbox]  A Guide to CNNs for CV \textbf{ 2. Features and Classifiers
}
\item [\checkbox]  A Guide to CNNs for CV \textbf{ 3. Neural Network Basics
}
\item [\checkbox]  A Guide to CNNs for CV \textbf{ 4. Convolutional Neural Network
}
\item [\checkbox]  A Guide to CNNs for CV \textbf{ 5. CNN Learning
}
\item [\checkbox]  A Guide to CNNs for CV \textbf{ 6. Examples of CNN Architectures
}
\item [\checkbox]  A Guide to CNNs for CV \textbf{ 7. Applications of CNNs in Computer Vision
}
\item [\checkbox]  A Guide to CNNs for CV \textbf{ 8. Deep Learning Tools and Libraries
}
\item [\checkbox]  A Guide to CNNs for CV \textbf{ 9. Conclusion
}
\item [\checkbox]  Mastering Machine Learning Algorithms \textbf{ 1. Machine Learning Model Fundamentals
}
\item [\checkbox]  Mastering Machine Learning Algorithms \textbf{ 2. Introduction to Semi-Supervised Learning
}
\item [\checkbox]  Mastering Machine Learning Algorithms \textbf{ 3. Graph-Based Semi-Supervised Learning
}
\item [\checkbox]  Mastering Machine Learning Algorithms \textbf{ 4. Bayesian Networks and Hidden Markov Models
}
\item [\checkbox]  Mastering Machine Learning Algorithms \textbf{ 5. EM Algorithm and Applications
}
\item [\checkbox]  Mastering Machine Learning Algorithms \textbf{ 6. Hebbian Learning and Self-Organizing Maps
}
\item [\checkbox]  Mastering Machine Learning Algorithms \textbf{ 7. Clustering Algorithms
}
\item [\checkbox]  Mastering Machine Learning Algorithms \textbf{ 8. Ensemble Learnin
}
\item [\checkbox]  Mastering Machine Learning Algorithms \textbf{ 9. Neural Networks for Machine Learning
}
\item [\checkbox]  Mastering Machine Learning Algorithms \textbf{ 10. Advanced Neural Models
}
\item [\checkbox]  Mastering Machine Learning Algorithms \textbf{ 11. Autoencoders
}
\item [\checkbox]  Mastering Machine Learning Algorithms \textbf{ 12. Generative Adversarial Networks
}
\item [\checkbox]  Mastering Machine Learning Algorithms \textbf{ 13. Deep Belief Networks
}
\item [\checkbox]  Mastering Machine Learning Algorithms \textbf{ 14. Introduction to Reinforcement Learning
}
\item [\checkbox]  Mastering Machine Learning Algorithms \textbf{ 15. Advanced Policy Estimation Algorithms
}
\item [\checkbox]  CNNs in Visual Computing \textbf{ 1. Introduction to Visual Computing
}
\item [\checkbox]  CNNs in Visual Computing \textbf{ 2. Learning as a Regression Problem
}
\item [\checkbox]  CNNs in Visual Computing \textbf{ 3. Artificial Neural Networks
}
\item [\checkbox]  CNNs in Visual Computing \textbf{ 4. Convolutional Neural Networks
}
\item [\checkbox]  CNNs in Visual Computing \textbf{ 5. Modern and Novel Usages of CNNs
}
\item [\checkbox]  CNNs in Visual Computing \textbf{ A. Yann
}
\item [\checkbox]  Programming PyTorch for Deep Learning: Creating and Deploying Deep Learning Applications \textbf{ 1. Getting Started with PyTorch
}
\item [\checkbox]  Programming PyTorch for Deep Learning: Creating and Deploying Deep Learning Applications \textbf{ 2. Image Classification with PyTorch
}
\item [\checkbox]  Programming PyTorch for Deep Learning: Creating and Deploying Deep Learning Applications \textbf{ 3. Convoutional Neural Networks
}
\item [\checkbox]  Programming PyTorch for Deep Learning: Creating and Deploying Deep Learning Applications \textbf{ 4. Transfer Learning and Other Tricks
}
\item [\checkbox]  Programming PyTorch for Deep Learning: Creating and Deploying Deep Learning Applications \textbf{ 5. Text Classification
}
\item [\checkbox]  Programming PyTorch for Deep Learning: Creating and Deploying Deep Learning Applications \textbf{ 6. A Journey into Sound
}
\item [\checkbox]  Programming PyTorch for Deep Learning: Creating and Deploying Deep Learning Applications \textbf{ 7. Debugging PyTorch Models
}
\item [\checkbox]  Programming PyTorch for Deep Learning: Creating and Deploying Deep Learning Applications \textbf{ 8. PyTorch in Porduction
}
\item [\checkbox]  Programming PyTorch for Deep Learning: Creating and Deploying Deep Learning Applications \textbf{ 9. PyTorch in the Wild
}
\item [\checkbox]  Learn Tensorflow 2.0 \textbf{ 1 Introduction to TensorFlow 2.0
}
\item [\checkbox]  Learn Tensorflow 2 \textbf{ 2. Supervised Learning with TensorFlow
}
\item [\checkbox]  Learn Tensorflow 2 \textbf{ 3. Neural Networks and Deep Learning with TensorFlow
}
\item [\checkbox]  Learn Tensorflow 2 \textbf{ 4. Images with TensorFlow
}
\item [\checkbox]  Learn Tensorflow 2 \textbf{ 5. Natural Language Processing with TensorFlow 2.0
}
\item [\checkbox]  Learn Tensorflow 2 \textbf{ 6. TensorFlow Models in Production
}
\item [\checkbox]  Advanced DL with TensorFlow 2 \textbf{ 1. Introducing Advanced Deep learning with Keras
}
\item [\checkbox]  Advanced DL with TensorFlow 2 \textbf{ 2. Deep Neural Networks
}
\item [\checkbox]  Advanced DL with TensorFlow 2 \textbf{ 3. Autoencoders
}
\item [\checkbox]  Advanced DL with TensorFlow 2 \textbf{ 4. Generative Adversarial Encoders
}
\item [\checkbox]  Advanced DL with TensorFlow 2 \textbf{ 5. Improved GANs
}
\item [\checkbox]  Advanced DL with TensorFlow 2 \textbf{ 6. Disentangled Representation GANs
}
\item [\checkbox]  Advanced DL with TensorFlow 2 \textbf{ 7. Cross-Domain GANs
}
\item [\checkbox]  Advanced DL with TensorFlow 2 \textbf{ 8. Variational Autoencoders
}
\item [\checkbox]  Advanced DL with TensorFlow 2 \textbf{ 9. Deep Reinforcement Learning
}
\item [\checkbox]  Advanced DL with TensorFlow 2 \textbf{ 10. Policy Gradient Methods
}
\item [\checkbox]  Advanced DL with TensorFlow 2 \textbf{ 11. Object Detection
}
\item [\checkbox]  Advanced DL with TensorFlow 2 \textbf{ 12. Semantic Segmentation
}
\item [\checkbox]  Advanced DL with TensorFlow 2 \textbf{ 13. Unsupervised Learning Using Mutual Information
}
\item [\checkbox]  Deep Learning in Natural Language Processing \textbf{ 1. A Joint Introduction to Natural Language Processing and to Deep Learning
}
\item [\checkbox]  Deep Learning in Natural Language Processing \textbf{ 2. Deep Learning in Conversational Language Understanding
}
\item [\checkbox]  Deep Learning in Natural Language Processing \textbf{ 3. Deep Learning in Spoken and Text-Based Dialog Systems
}
\item [\checkbox]  Deep Learning in Natural Language Processing \textbf{ 4. Deep Learning in Lexical Analysis and Parsing
}
\item [\checkbox]  Deep Learning in Natural Language Processing \textbf{ 5. Deep Learning in Knowledge Graph
}
\item [\checkbox]  Deep Learning in Natural Language Processing \textbf{ 6. Deep Learning in Machine Translation
}
\item [\checkbox]  Deep Learning in Natural Language Processing \textbf{ 7. Deep Learning in Question Answering
}
\item [\checkbox]  Deep Learning in Natural Language Processing \textbf{ 8. Deep Learning in Sentiment Analysis
}
\item [\checkbox]  Deep Learning in Natural Language Processing \textbf{ 9. Deep Learning in Social Computing
}
\item [\checkbox]  Deep Learning in Natural Language Processing \textbf{ 10. Deep Learning in Natural Language Generation from Images
}
\item [\checkbox]  Deep Learning in Natural Language Processing \textbf{ 11. Epilogue: Frontiers of NLP in the Deep Learning Era
}
\item [\checkbox]  Generative Deep Learning \textbf{ 1. Generative Modeling
}
\item [\checkbox]  Generative Deep Learning \textbf{ 2. Deep Learning
}
\item [\checkbox]  Generative Deep Learning \textbf{ 3. Variational Autoencoders
}
\item [\checkbox]  Generative Deep Learning \textbf{ 4. Generative Adversarial Networks
}
\item [\checkbox]  Generative Deep Learning \textbf{ 5. Paint
}
\item [\checkbox]  Generative Deep Learning \textbf{ 6. Write
}
\item [\checkbox]  Generative Deep Learning \textbf{ 7. Compose
}
\item [\checkbox]  Generative Deep Learning \textbf{ 8. Play
}
\item [\checkbox]  Generative Deep Learning \textbf{ 9. The Future of Generative Modeling
}
\item [\checkbox]  Generative Deep Learning \textbf{ 10. Conclusion
}
\item [\checkbox]  Transfer Learning \textbf{ 1. Introduction
}
\item [\checkbox]  Transfer Learning \textbf{ 2. Instance-Based Transfer Learning
}
\item [\checkbox]  Transfer Learning \textbf{ 3. Feature-Based Transfer Learning
}
\item [\checkbox]  Transfer Learning \textbf{ 4. Model-Based Transfer Learning
}
\item [\checkbox]  Transfer Learning \textbf{ 5. Relation-Based Transfer Learning
}
\item [\checkbox]  Transfer Learning \textbf{ 6. Heterogeneous Transfer Learning
}
\item [\checkbox]  Transfer Learning \textbf{ 7. Adversarial Transfer Learning
}
\item [\checkbox]  Transfer Learning \textbf{ 8. Transfer Learning in Reinforcement Learning
}
\item [\checkbox]  Transfer Learning \textbf{ 9. Multi-Task Learning
}
\item [\checkbox]  Transfer Learning \textbf{ 10. Transfer Learning Theory
}
\item [\checkbox]  Transfer Learning \textbf{ 11. Transitive Transfer Learning
}
\item [\checkbox]  Transfer Learning \textbf{ 12. AutoTL: Learning to Transfer Automatically
}
\item [\checkbox]  Transfer Learning \textbf{ 13. Few-Shot Learning
}
\item [\checkbox]  Transfer Learning \textbf{ 14. Lifelong Machine Learning
}
\item [\checkbox]  Transfer Learning \textbf{ 15. Privacy-Preserving Transfer Learning
}
\item [\checkbox]  Transfer Learning \textbf{ 16. Transfer Learning in Computer Vision
}
\item [\checkbox]  Transfer Learning \textbf{ 17. Transfer Learning in Natural Language Processing
}
\item [\checkbox]  Transfer Learning \textbf{ 18. Transfer Learning in Dialogue Systems
}
\item [\checkbox]  Transfer Learning \textbf{ 19. Transfer Learning in Recommender Systems
}
\item [\checkbox]  Transfer Learning \textbf{ 20. Transfer Learning in Bioinformatics
}
\item [\checkbox]  Transfer Learning \textbf{ 21. Transfer Learning in Activity Recognition
}
\item [\checkbox]  Transfer Learning \textbf{ 22. Transfer Learning in Urban Computing
}
\item [\checkbox]  Transfer Learning \textbf{ 23. Concluding Remarks
}
\item [\checkbox]  Data Science Career Guide \textbf{
}
\item [\checkbox]  Data Science with Julia \textbf{ 1. Introduction
}
\item [\checkbox]  Data Science with Julia \textbf{ 2. Core Julia
}
\item [\checkbox]  Data Science with Julia \textbf{ 3. Working with Data
}
\item [\checkbox]  Data Science with Julia \textbf{ 4. Visualizing Data
}
\item [\checkbox]  Data Science with Julia \textbf{ 5. Supervised Learning
}
\item [\checkbox]  Data Science with Julia \textbf{ 6. Unsupervised Learning
}
\item [\checkbox]  Data Science with Julia \textbf{ 7. R Interoperability
}
\item [\checkbox]  Data Science with Julia \textbf{ A. Julia and R Packages Used Herein
}
\item [\checkbox]  Data Science with Julia \textbf{ B. Variables for Food Data
}
\item [\checkbox]  Data Science with Julia \textbf{ C. Useful Mathematical Results
}
\item [\checkbox]  Data Science with Julia \textbf{ D. Performance Tips
}
\item [\checkbox]  Data Science with Julia \textbf{ E. Linear Algebra Functions
}
\item [\checkbox]  Handbook of Data Intensive Computing \textbf{ 1. High Performance Network Architectures for Data Intensive Computing
}
\item [\checkbox]  Handbook of Data Intensive Computing \textbf{ 2. Architecting Data-Intensive Software Systems
}
\item [\checkbox]  Handbook of Data Intensive Computing \textbf{ 3. ECL: A High-Level Programming Language for Data-Intensive Supercomputing
}
\item [\checkbox]  Handbook of Data Intensive Computing \textbf{ 4. Scalable Storage for Data-Intensive Computing
}
\item [\checkbox]  Handbook of Data Intensive Computing \textbf{ 5. Computation and Storage Trade-off for Cost-Effective Storage of Scientific Datasets in the Cloud
}
\item [\checkbox]  Handbook of Data Intensive Computing \textbf{ 6. Load Balancing Techniques for Data Intensive Computing
}
\item [\checkbox]  Handbook of Data Intensive Computing \textbf{ 7. Resource Management for Data Intensive Clouds Through Dynamic Federation: A Game Theoretic Approach
}
\item [\checkbox]  Handbook of Data Intensive Computing \textbf{ 8. SALT: Scalable Automated Linking Technology for Data Intensive Computing
}
\item [\checkbox]  Handbook of Data Intensive Computing \textbf{ 9. Parallel Processing, Multiprocessors and Virtualization in Data-Intensive Computing
}
\item [\checkbox]  Handbook of Data Intensive Computing \textbf{ 10. Challenges in Data Intensive Analysis and Visualization at Scientific Experimental User Facilities
}
\item [\checkbox]  Handbook of Data Intensive Computing \textbf{ 11. Large-Scale Data Analytics Using Ensemble Clustering
}
\item [\checkbox]  Handbook of Data Intensive Computing \textbf{ 12. Specification of Data Intensive Applications with Data Dependency and Abstract Clocks
}
\item [\checkbox]  Handbook of Data Intensive Computing \textbf{ 13. Ensemble Feature Ranking Methods for Data Intensive Computing Applications
}
\item [\checkbox]  Handbook of Data Intensive Computing \textbf{ 14. Record Linkage Methodology and Application
}
\item [\checkbox]  Handbook of Data Intensive Computing \textbf{ 15. Semantic Wrapper: Concise Semantic Querying of Legacy Relational Databases
}
\item [\checkbox]  Handbook of Data Intensive Computing \textbf{ 16. Security in Data Intensive Computing Systems
}
\item [\checkbox]  Handbook of Data Intensive Computing \textbf{ 17. Data Security and Privacy in Data-Intensive Supercomputing Clusters
}
\item [\checkbox]  Handbook of Data Intensive Computing \textbf{ 18. Information Security in Large Scale Distributed Systems
}
\item [\checkbox]  Handbook of Data Intensive Computing \textbf{ 19. Privacy and Security Requirements of Data Intensive Applications in Clouds
}
\item [\checkbox]  Handbook of Data Intensive Computing \textbf{ 20. On the Processing of Extreme Scale Datasets in the Geosciences
}
\item [\checkbox]  Handbook of Data Intensive Computing \textbf{ 21. Parallel Earthquake Simulations on Large-scale Multicore Supercomputers
}
\item [\checkbox]  Handbook of Data Intensive Computing \textbf{ 22. Data Intensive Computing in Bioinformatics: A Biomedical Case Study in Gene Selection and Filtering
}
\item [\checkbox]  Handbook of Data Intensive Computing \textbf{ 23. Design Space Exploration for Efficient Data Intensive Computing on SoCs
}
\item [\checkbox]  Handbook of Data Intensive Computing \textbf{ 24. Discovering Relevant Entities in Large-scale Social Information Systems
}
\item [\checkbox]  Handbook of Data Intensive Computing \textbf{ 25. Geospatial Data Management with Terrafly
}
\item [\checkbox]  Handbook of Data Intensive Computing \textbf{ 26. An Application for Processing Large and Non-uniform Media Objects on MapReduce-based Clusters
}
\item [\checkbox]  Handbook of Data Intensive Computing \textbf{ 27. Feature Selection Algorithms for Mining High-Dimensional DNA Microarray Data
}
\item [\checkbox]  Handbook of Data Intensive Computing \textbf{ 28. Application of Random Matrix Theory to Analyze Biological Data
}
\item [\checkbox]  Handbook of Data Intensive Computing \textbf{ 29. Keyword Search on Large Relational Databases: an OLAP-Oriented Approach
}
\item [\checkbox]  Handbook of Data Intensive Computing \textbf{ 30. A Distributed Publish/Subscribe System for Large Scale Sensor Networks
}
\item [\checkbox]  Machine Learning (Mitchell) \textbf{ 1. Introduction
}
\item [\checkbox]  Machine Learning (Mitchell) \textbf{ 2. Concept Learning and the General-to-Specific Ordering
}
\item [\checkbox]  Machine Learning (Mitchell) \textbf{ 3. Decision Tree Learning
}
\item [\checkbox]  Machine Learning (Mitchell) \textbf{ 4. Artificial Neural Networks
}
\item [\checkbox]  Machine Learning (Mitchell) \textbf{ 5. Evaluating Hypotheses
}
\item [\checkbox]  Machine Learning (Mitchell) \textbf{ 6. Bayesian Learning
}
\item [\checkbox]  Machine Learning (Mitchell) \textbf{ 7. Computational Learning Theory
}
\item [\checkbox]  Machine Learning (Mitchell) \textbf{ 8. Instance-Based Learning
}
\item [\checkbox]  Machine Learning (Mitchell) \textbf{ 9. Genetic Algorithms
}
\item [\checkbox]  Machine Learning (Mitchell) \textbf{ 10. Learning Sets of Rules
}
\item [\checkbox]  Machine Learning (Mitchell) \textbf{ 11. Analytical Learning
}
\item [\checkbox]  Machine Learning (Mitchell) \textbf{ 12. Combining Inductive and Analytical Learning
}
\item [\checkbox]  Machine Learning (Mitchell) \textbf{ 13. Reinforcement Learning
}
\item [\checkbox]  Probabilistic Machine Learning: An Introduction \textbf{ 1. Introduction
}
\item [\checkbox]  Probabilistic Machine Learning: An Introduction \textbf{ 2. Probabilistic Inference
}
\item [\checkbox]  Probabilistic Machine Learning: An Introduction \textbf{ 3. Probabilistic Models
}
\item [\checkbox]  Probabilistic Machine Learning: An Introduction \textbf{ 4. Parameter Estimation
}
\item [\checkbox]  Probabilistic Machine Learning: An Introduction \textbf{ 5. Optimization Algorithms
}
\item [\checkbox]  Probabilistic Machine Learning: An Introduction \textbf{ 6. Information Theory
}
\item [\checkbox]  Probabilistic Machine Learning: An Introduction \textbf{ 7. Bayesian Statistics
}
\item [\checkbox]  Probabilistic Machine Learning: An Introduction \textbf{ 8. Bayesian Decision Theory
}
\item [\checkbox]  Probabilistic Machine Learning: An Introduction \textbf{ 9. Linear Discriminant Analysis
}
\item [\checkbox]  Probabilistic Machine Learning: An Introduction \textbf{ 10. Logistic Regression
}
\item [\checkbox]  Probabilistic Machine Learning: An Introduction \textbf{ 11. Linear Regression
}
\item [\checkbox]  Probabilistic Machine Learning: An Introduction \textbf{ 12. Generalized Linear Models
}
\item [\checkbox]  Probabilistic Machine Learning: An Introduction \textbf{ 13. Neural Networks for Unstructured Data
}
\item [\checkbox]  Probabilistic Machine Learning: An Introduction \textbf{ 14. Neural Networks for Images
}
\item [\checkbox]  Probabilistic Machine Learning: An Introduction \textbf{ 15. Neural Networks for Sequences
}
\item [\checkbox]  Probabilistic Machine Learning: An Introduction \textbf{ IV Nonparametric Models
}
\item [\checkbox]  Probabilistic Machine Learning: An Introduction \textbf{ 16. Exemplar-Based Methods
}
\item [\checkbox]  Probabilistic Machine Learning: An Introduction \textbf{ 17. Kernel Methods
}
\item [\checkbox]  Probabilistic Machine Learning: An Introduction \textbf{ 18. Trees, Forests, Bagging and Boosting
}
\item [\checkbox]  Probabilistic Machine Learning: An Introduction \textbf{ 19. Learning with Fewer Labeled Examples
}
\item [\checkbox]  Probabilistic Machine Learning: An Introduction \textbf{ 20. Dimensionality Reduction
}
\item [\checkbox]  Probabilistic Machine Learning: An Introduction \textbf{ 21. Clustering
}
\item [\checkbox]  Probabilistic Machine Learning: An Introduction \textbf{ 22. Recommender Systems
}
\item [\checkbox]  Probabilistic Machine Learning: An Introduction \textbf{ 23. Graph Embeddings
}
\item [\checkbox]  Probabilistic Machine Learning: An Introduction \textbf{ A. Some Useful Mathematics
}
\item [\checkbox]  Probabilistic Machine Learning: An Introduction \textbf{ B. Linear Algebra
}
\item [\checkbox]  Probabilistic Machine Learning: An Introduction \textbf{ C. Probability
}
\item [\checkbox]  Probabilistic Machine Learning: An Introduction \textbf{ D. Frequentist Statistics
}
\item [\checkbox]  Probabilistic Machine Learning: An Introduction \textbf{ E. Exercises
}
\item [\checkbox]  Machine Learning Refined \textbf{ 1. Introduction to Machine Learning
}
\item [\checkbox]  Machine Learning Refined \textbf{ 2. Zero-Order Optimization Techniques
}
\item [\checkbox]  Machine Learning Refined \textbf{ 3. First-Order Optimization Techniques
}
\item [\checkbox]  Machine Learning Refined \textbf{ 4. Second-Order Optimization Techniques
}
\item [\checkbox]  Machine Learning Refined \textbf{ 5. Linear Regression
}
\item [\checkbox]  Machine Learning Refined \textbf{ 6. Linear Two-Class Classification
}
\item [\checkbox]  Machine Learning Refined \textbf{ 7. Linear Multi-Class Classification
}
\item [\checkbox]  Machine Learning Refined \textbf{ 8. Linear Unsupervised Learning
}
\item [\checkbox]  Machine Learning Refined \textbf{ 9. Feature Engineering and Selection
}
\item [\checkbox]  Machine Learning Refined \textbf{ 10. Principles of Nonlinear Feature Engineering
}
\item [\checkbox]  Machine Learning Refined \textbf{ 11. Principles of Feature Learning
}
\item [\checkbox]  Machine Learning Refined \textbf{ 12. Kernel Methods
}
\item [\checkbox]  Machine Learning Refined \textbf{ 13. Fully Connected Neural Networks
}
\item [\checkbox]  Machine Learning Refined \textbf{ 14. Tree-Based Learners
}
\item [\checkbox]  Machine Learning Refined \textbf{ A. Advanced First- and Second-Order Optimization Methods
}
\item [\checkbox]  Machine Learning Refined \textbf{ B. Derivatives and Automatic Differentiation
}
\item [\checkbox]  Machine Learning Refined \textbf{ C. Linear Algebra
}
\item [\checkbox]  Data Clustering \textbf{ 1. An Introduction to Cluster Analysis
}
\item [\checkbox]  Data Clustering \textbf{ 2. Feature Selection for Clustering: A Review
}
\item [\checkbox]  Data Clustering \textbf{ 3. Probabilistic Models for Clustering
}
\item [\checkbox]  Data Clustering \textbf{ 4. A Survey of Partitional and Hierarchical Clustering Algorithms
}
\item [\checkbox]  Data Clustering \textbf{ 5. Density-Based Clustering
}
\item [\checkbox]  Data Clustering \textbf{ 6. Grid-Based Clustering
}
\item [\checkbox]  Data Clustering \textbf{ 7. Nonnegative Matrix Factorizations for Clustering: A Survey
}
\item [\checkbox]  Data Clustering \textbf{ 8. Spectral Clustering
}
\item [\checkbox]  Data Clustering \textbf{ 9. Clustering High-Dimensional Data
}
\item [\checkbox]  Data Clustering \textbf{ 10. A Survey of Stream Clustering Algorithms
}
\item [\checkbox]  Data Clustering \textbf{ 11. Big Data Clustering
}
\item [\checkbox]  Data Clustering \textbf{ 12. Clustering Categorical Data
}
\item [\checkbox]  Data Clustering \textbf{ 13. Document Clustering: The Next Frontier
}
\item [\checkbox]  Data Clustering \textbf{ 14. Clustering Multimedia Data
}
\item [\checkbox]  Data Clustering \textbf{ 15. Time-Series Data Clustering
}
\item [\checkbox]  Data Clustering \textbf{ 16. Clustering Biological Data
}
\item [\checkbox]  Data Clustering \textbf{ 17. Network Clustering
}
\item [\checkbox]  Data Clustering \textbf{ 18. A Survey of Uncertain Data Clustering Algorithms
}
\item [\checkbox]  Data Clustering \textbf{ 19. Concepts of Visual and Interactive Clustering
}
\item [\checkbox]  Data Clustering \textbf{ 20. Semisupervised Clustering
}
\item [\checkbox]  Data Clustering \textbf{ 21. Alternative Clustering Analysis: A Review
}
\item [\checkbox]  Data Clustering \textbf{ 22. Cluster Ensembles: Theory and Applications
}
\item [\checkbox]  Data Clustering \textbf{ 23. Clustering Validation Measures
}
\item [\checkbox]  Data Clustering \textbf{ 24. Educational and Software Resources for Data Clustering
}
\item [\checkbox]  Machine Learning: A Probabilistic Approach \textbf{ 1. Introduction
}
\item [\checkbox]  Machine Learning: A Probabilistic Approach \textbf{ 2. Probability
}
\item [\checkbox]  Machine Learning: A Probabilistic Approach \textbf{ 3. Generative Models for Discrete Data
}
\item [\checkbox]  Machine Learning: A Probabilistic Approach \textbf{ 4. Gaussian Models
}
\item [\checkbox]  Machine Learning: A Probabilistic Approach \textbf{ 5. Bayesian Statistics
}
\item [\checkbox]  Machine Learning: A Probabilistic Approach \textbf{ 6. Frequentist Statistics
}
\item [\checkbox]  Machine Learning: A Probabilistic Approach \textbf{ 7. Linear Regression
}
\item [\checkbox]  Machine Learning: A Probabilistic Approach \textbf{ 8. Logistic Regression
}
\item [\checkbox]  Machine Learning: A Probabilistic Approach \textbf{ 9. Generalized Linear Models and the Exponential Family
}
\item [\checkbox]  Machine Learning: A Probabilistic Approach \textbf{ 10. Directed GRaphical Models (Bayes Nets)
}
\item [\checkbox]  Machine Learning: A Probabilistic Approach \textbf{ 11. Mixture Models and the EM Algorithm
}
\item [\checkbox]  Machine Learning: A Probabilistic Approach \textbf{ 12. Latent Linear Models
}
\item [\checkbox]  Machine Learning: A Probabilistic Approach \textbf{ 13. Sparse Linear Models
}
\item [\checkbox]  Machine Learning: A Probabilistic Approach \textbf{ 14. Kernels
}
\item [\checkbox]  Machine Learning: A Probabilistic Approach \textbf{ 15. Gaussian Processes
}
\item [\checkbox]  Machine Learning: A Probabilistic Approach \textbf{ 16. Adaptive Basis Function Models
}
\item [\checkbox]  Machine Learning: A Probabilistic Approach \textbf{ 17. Markov and Hidden Markov Models
}
\item [\checkbox]  Machine Learning: A Probabilistic Approach \textbf{ 18. State Space Models
}
\item [\checkbox]  Machine Learning: A Probabilistic Approach \textbf{ 19. Undirected Graphical Models (Markov Random Fields)
}
\item [\checkbox]  Machine Learning: A Probabilistic Approach \textbf{ 20. Exact Inference for Graphical Models
}
\item [\checkbox]  Machine Learning: A Probabilistic Approach \textbf{ 21. Variational Inference
}
\item [\checkbox]  Machine Learning: A Probabilistic Approach \textbf{ 22. More Variational Inference
}
\item [\checkbox]  Machine Learning: A Probabilistic Approach \textbf{ 23. Monte Carlo Inference
}
\item [\checkbox]  Machine Learning: A Probabilistic Approach \textbf{ 24. Markov Chain Monte Carlo (MCMC) Inference
}
\item [\checkbox]  Machine Learning: A Probabilistic Approach \textbf{ 25. Clustering
}
\item [\checkbox]  Machine Learning: A Probabilistic Approach \textbf{ 26. Graphical Model Structure Learning
}
\item [\checkbox]  Machine Learning: A Probabilistic Approach \textbf{ 27. Latent Variable Models for Discrete Data
}
\item [\checkbox]  Machine Learning: A Probabilistic Approach \textbf{ 28. Deep Learning
}
\item [\checkbox]  Machine Learning: A Probabilistic Approach \textbf{ A. Notation
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 1 An Introduction to Data Mining
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 1.1 Introduction
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 1.2 The Data Mining Process
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 1.3 The Basic Data Types
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 1.4 The Major Building Blocks: A Bird’s Eye View
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 1.5 Scalability Issues and the Streaming Scenario
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 1.6 A Stroll Through Some Application Scenarios
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 1.7 Summary
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 1.8 Bibliographic Notes
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 1.9 Exercises
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 2 Data Preparation
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 2.1 Introduction
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 2.2 Feature Extraction and Portability
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 2.3 Data Cleaning
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 2.4 Data Reduction and Transformation
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 2.5 Summary
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 2.6 Bibliographic Notes
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 2.7 Exercises
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 3 Similarity and Distances
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 3.1 Introduction
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 3.2 Multidimensional Data
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 3.3 Text Similarity Measures
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 3.4 Temporal Similarity Measures
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 3.5 Graph Similarity Measures
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 3.6 Supervised Similarity Functions
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 3.7 Summary
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 3.8 Bibliographic Notes
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 3.9 Exercises
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 4 Association Pattern Mining
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 4.1 Introduction
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 4.2 The Frequent Pattern Mining Model
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 4.3 Association Rule Generation Framework
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 4.4 Frequent Itemset Mining Algorithms
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 4.5 Alternative Models: Interesting Patterns
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 4.6 Useful Meta-algorithms
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 4.7 Summary
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 4.8 Bibliographic Notes
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 4.9 Exercises
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 5 Association Pattern Mining: Advanced Concepts
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 5.1 Introduction
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 5.2 Pattern Summarization
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 5.3 Pattern Querying
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 5.4 Putting Associations to Work: Applications
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 5.5 Summary
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 5.6 Bibliographic Notes
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 5.7 Exercises
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 6 Cluster Analysis
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 6.1 Introduction
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 6.2 Feature Selection for Clustering
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 6.3 Representative-Based Algorithms
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 6.4 Hierarchical Clustering Algorithms
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 6.5 Probabilistic Model-Based Algorithms
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 6.6 Grid-Based and Density-Based Algorithms
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 6.7 Graph-Based Algorithms
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 6.8 Non-negative Matrix Factorization
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 6.9 Cluster Validation
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 6.10 Summary
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 6.11 Bibliographic Notes
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 6.12 Exercises
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 7 Cluster Analysis: Advanced Concepts
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 7.1 Introduction
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 7.2 Clustering Categorical Data
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 7.3 Scalable Data Clustering
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 7.4 High-Dimensional Clustering
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 7.5 Semisupervised Clustering
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 7.6 Human and Visually Supervised Clustering
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 7.7 Cluster Ensembles
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 7.8 Putting Clustering to Work: Applications
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 7.9 Summary
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 8 Outlier Analysis
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 8.1 Introduction
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 8.2 Extreme Value Analysis
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 8.3 Probabilistic Models
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 8.4 Clustering for Outlier Detection
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 8.5 Distance-Based Outlier Detection
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 8.6 Density-Based Methods
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 8.7 Information-Theoretic Models
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 8.8 Outlier Validity
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 8.9 Summary
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 9 Outlier Analysis: Advanced Concepts
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 9.1 Introduction
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 9.2 Outlier Detection with Categorical Data
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 9.3 High-Dimensional Outlier Detection
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 9.3.2 Random Subspace Sampling
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 9.4 Outlier Ensembles
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 9.4.3 Normalization and Combination
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 9.5 Putting Outliers to Work: Applications
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 9.6 Summary
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 9.7 Bibliographic Notes
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 9.8 Exercises
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 10 Data Classification
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 10.1 Introduction
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 10.2 Feature Selection for Classification
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 10.3 Decision Trees
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 10.4 Rule-Based Classifiers
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 10.5 Probabilistic Classifiers
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 10.5.2 Logistic Regression
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 10.6 Support Vector Machines
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 10.7 Neural Networks
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 10.8 Instance-Based Learning
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 10.9 Classifier Evaluation
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 10.10 Summary
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 10.11 Bibliographic Notes
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 10.12 Exercises
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 11 Data Classification: Advanced Concepts
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 11.1 Introduction
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 11.2 Multiclass Learning
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 11.3 Rare Class Learning
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 11.4 Scalable Classification
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 11.5 Regression Modeling with Numeric Classes
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 11.6 Semisupervised Learning
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 11.7 Active Learning
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 11.8 Ensemble Methods
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 11.9 Summary
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 11.10 Bibliographic Notes
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 11.11 Exercises
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 12 Mining Data Streams
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 12.1 Introduction
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 12.2 Synopsis Data Structures for Streams
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 12.3 Frequent Pattern Mining in Data Streams
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 12.4 Clustering Data Streams
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 12.5 Streaming Outlier Detection
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 12.6 Streaming Classification
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 12.7 Summary
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 12.8 Bibliographic Notes
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 12.9 Exercises
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 13 Mining Text Data
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 13.1 Introduction
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 13.2 Document Preparation and Similarity
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ Computation
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 13.4 Topic Modeling
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 13.5 Specialized Classification Methods for Text
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 13.6 Novelty and First Story Detection
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 13.7 Summary
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 13.8 Bibliographic Notes
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 13.9 Exercises
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 14 Mining Time Series Data
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 14.1 Introduction
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 14.2 Time Series Preparation and Similarity
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 14.3 Time Series Forecasting
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 14.4 Time Series Motifs
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 14.5 Time Series Clustering
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 14.6 Time Series Outlier Detection
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 14.7 Time Series Classification
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 14.8 Summary
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 14.9 Bibliographic Notes
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 14.10 Exercises
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 15 Mining Discrete Sequences
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 15.1 Introduction
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 15.2 Sequential Pattern Mining
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 15.3 Sequence Clustering
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 15.4 Outlier Detection in Sequences
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 15.5 Hidden Markov Models
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 15.6 Sequence Classification
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 15.7 Summary
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 15.8 Bibliographic Notes
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 15.9 Exercises
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 16 Mining Spatial Data
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 16.1 Introduction
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 16.2 Mining with Contextual Spatial Attributes
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 16.3 Trajectory Mining
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 16.4 Summary
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 16.5 Bibliographic Notes
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 16.6 Exercises
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 17 Mining Graph Data
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 17.1 Introduction
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 17.2 Matching and Distance Computation in Graphs
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 17.3 Transformation-Based Distance Computation
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 17.4 Frequent Substructure Mining in Graphs
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 17.5 Graph Clustering
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 17.6 Graph Classification
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 17.7 Summary
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 17.8 Bibliographic Notes
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 17.9 Exercises
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 18 Mining Web Data
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 18.1 Introduction
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 18.2 Web Crawling and Resource Discovery
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 18.3 Search Engine Indexing and Query Processing
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 18.4 Ranking Algorithms
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 18.5 Recommender Systems
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 18.6 Web Usage Mining
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 18.7 Summary
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 18.8 Bibliographic Notes
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 18.9 Exercises
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 19 Social Network Analysis
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 19.1 Introduction
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 19.2 Social Networks: Preliminaries and Properties
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 19.3 Community Detection
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 19.4 Collective Classification
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 19.5 Link Prediction
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 19.6 Social Influence Analysis
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 19.7 Summary
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 19.8 Bibliographic Notes
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 19.9 Exercises
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 20 Privacy-Preserving Data Mining
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 20.1 Introduction
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 20.2 Privacy During Data Collection
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 20.3 Privacy-Preserving Data Publishing
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 20.4 Output Privacy
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 20.5 Distributed Privacy
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 20.6 Summary
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 20.7 Bibliographic Notes
}
\item [\checkbox]  Data Mining (Aggarwal) \textbf{ 20.8 Exercises
}
\item [\checkbox]  Machine Learning: A Bayesian and Optimization Perspective \textbf{ 1. Introduction
}
\item [\checkbox]  Machine Learning: A Bayesian and Optimization Perspective \textbf{ 2. Probability and Stochastic Processes
}
\item [\checkbox]  Machine Learning: A Bayesian and Optimization Perspective \textbf{ 3. Learning in Parametric 
Modelling: Basic Concepts and Directions
}
\item [\checkbox]  Machine Learning: A Bayesian and Optimization Perspective \textbf{ 4. Mean-Square Error Linear Estimation
}
\item [\checkbox]  Machine Learning: A Bayesian and Optimization Perspective \textbf{ 5. Online Learning: The SGD Family of Algorithms
}
\item [\checkbox]  Machine Learning: A Bayesian and Optimization Perspective \textbf{ 6. The Least-Squares Family
}
\item [\checkbox]  Machine Learning: A Bayesian and Optimization Perspective \textbf{ 7. Classification: Atou of the Classics
}
\item [\checkbox]  Machine Learning: A Bayesian and Optimization Perspective \textbf{ 8. Parameter Learning: A Convex Analytic Path
}
\item [\checkbox]  Machine Learning: A Bayesian and Optimization Perspective \textbf{ 9. Sparsity-Aware Learning: Concepts and Theoretical Foundations
}
\item [\checkbox]  Machine Learning: A Bayesian and Optimization Perspective \textbf{ 10. Sparsity-Aware Learning: Algorithms and Applications
}
\item [\checkbox]  Machine Learning: A Bayesian and Optimization Perspective \textbf{ 11. Learning in Reproducing Kernel Hilbert Spaces
}
\item [\checkbox]  Machine Learning: A Bayesian and Optimization Perspective \textbf{ 12. Bayesian Learning: Inference and the EM Algorithm
}
\item [\checkbox]  Machine Learning: A Bayesian and Optimization Perspective \textbf{ 13. Bayesian Learning: Approximate Inference and Nonparametric Models
}
\item [\checkbox]  Machine Learning: A Bayesian and Optimization Perspective \textbf{ 14. Monte Carlo Methods
}
\item [\checkbox]  Machine Learning: A Bayesian and Optimization Perspective \textbf{ 15. Probabilistic Graphical Models: Part I
}
\item [\checkbox]  Machine Learning: A Bayesian and Optimization Perspective \textbf{ 16. Probabilistic Graphical Models: Part II
}
\item [\checkbox]  Machine Learning: A Bayesian and Optimization Perspective \textbf{ 17. Particle Filtering
}
\item [\checkbox]  Machine Learning: A Bayesian and Optimization Perspective \textbf{ 18. Neural Networks and Deep Learning
}
\item [\checkbox]  Machine Learning: A Bayesian and Optimization Perspective \textbf{ 19. Dimensionality Reduction and Latent Variable Modeling
}
\item [\checkbox]  Linear Algebra and Optimization for Machine Learning: A Textbook \textbf{ 1. Linear Algebra and Optimization: An Introduction
}
\item [\checkbox]  Linear Algebra and Optimization for Machine Learning: A Textbook \textbf{ 2. Linear Transformations and Linear Systems
}
\item [\checkbox]  Linear Algebra and Optimization for Machine Learning: A Textbook \textbf{ 3. Eigenvectors and Diagonalizable Matrices
}
\item [\checkbox]  Linear Algebra and Optimization for Machine Learning: A Textbook \textbf{ 4. Optimization Basics: A Machine Learning View
}
\item [\checkbox]  Linear Algebra and Optimization for Machine Learning: A Textbook \textbf{ 5. Advanced Optimization Solutions
}
\item [\checkbox]  Linear Algebra and Optimization for Machine Learning: A Textbook \textbf{ 6. Constrained Optimization and Duality
}
\item [\checkbox]  Linear Algebra and Optimization for Machine Learning: A Textbook \textbf{ 7. Singular Value Decomposition
}
\item [\checkbox]  Linear Algebra and Optimization for Machine Learning: A Textbook \textbf{ 8. Matrix Factorization
}
\item [\checkbox]  Linear Algebra and Optimization for Machine Learning: A Textbook \textbf{ 9. The Linear Algebra of Similarity
}
\item [\checkbox]  Linear Algebra and Optimization for Machine Learning: A Textbook \textbf{ 10. The Linear Algebra of Graphs
}
\item [\checkbox]  Linear Algebra and Optimization for Machine Learning: A Textbook \textbf{ 11. Optimization in Computational Graphs
}
\item [\checkbox]  Understanding Complex Datasets \textbf{ 1. Data Mining
}
\item [\checkbox]  Understanding Complex Datasets \textbf{ 2. Matrix decompositions
}
\item [\checkbox]  Understanding Complex Datasets \textbf{ 3. Singular Value Decomposition (SVD)
}
\item [\checkbox]  Understanding Complex Datasets \textbf{ 4. Graph Analysis
}
\item [\checkbox]  Understanding Complex Datasets \textbf{ 5. SemiDiscrete Decomposition (SDD)
}
\item [\checkbox]  Understanding Complex Datasets \textbf{ 6. Using SVD and SDD together
}
\item [\checkbox]  Understanding Complex Datasets \textbf{ 7. Independent Component Analysis (ICA)
}
\item [\checkbox]  Understanding Complex Datasets \textbf{ 8. Non-Negative Matrix Factorization (NNMF)
}
\item [\checkbox]  Understanding Complex Datasets \textbf{ 9. Tensors
}
\item [\checkbox]  Understanding Complex Datasets \textbf{ 10. Conclusion
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 1. Introduction
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 2. Groups, Rings, and Fields
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 2.1. Groups, Subgroups, Cosets
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 2.2. Cyclic Groups
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 2.3. Rings and Fields
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 3. Vector Spaces, Bases, Linear Maps
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 3.1. Motivations: Linear Combinations, Linear Independence, Rank
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 3.2. Vector Spaces
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 3.3. Indexed Families; the Sum Notation
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 3.4. Linear Independence, Subspaces
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 3.5. Bases of a Vector Space
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 3.6. Matrices
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 3.7. Linear Maps
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 3.8. Quotient Spaces
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 3.9. Linear Forms and the Dual Space
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 3.10. Summary
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 3.11. Problems
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 4. Matrices and Linear Maps
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 4.1. Representation of Linear Maps by Matrices
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 4.2. Composition of Linear Maps and Matrix Multiplication
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 4.3. Change of Basis Matrix
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 4.4. The Effect of a Change of Bases on Matrices
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 4.5. Summary
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 4.6. Problems
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 5. Haar Bases, Haar Wavelets, Hadamard Matrices
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 5.1. Introduction to Signal Compression Using Haar Wavelets
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 5.2. Haar Matrices, Scaling Properties of Haar Wavelets
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 5.3. Kronecker Product Construction of Haar Matrices
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 5.4. Multiresolution Signal Analysis with Haar Bases
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 5.5. Haar Transform for Digital Images
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 5.6. Hadamard Matrices
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 5.7. Summary
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 5.8. Problems
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 6. Direct Sums
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 6.1. Sums, Direct Sums, Direct Products
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 6.2. The Rank-Nullity Theorem; Grassmann’s Relation
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 6.3. Summary
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 6.4. Problems
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 7. Determinants
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 7.1. Permutations, Signature of a Permutation
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 7.2. Alternating Multilinear Maps
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 7.3. Definition of a Determinant
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 7.4. Inverse Matrices and Determinants
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 7.5. Systems of Linear Equations and Determinants
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 7.6. Determinant of a Linear Map
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 7.7. The Cayley–Hamilton Theorem
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 7.8. Permanents
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 7.9. Summary
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 7.10. Further Readings
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 7.11. Problems
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 8. Gaussian Elimination, LU, Cholesky, Echelon Form
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 8.1. Motivating Example: Curve Interpolation
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 8.2. Gaussian Elimination
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 8.3. Elementary Matrices and Row Operations
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 8.4. LU-Factorization
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 8.5. P A = LU Factorization
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 8.6. Proof of Theorem 8.5
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 8.7. Dealing with Roundoff Errors; Pivoting Strategies
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 8.8. Gaussian Elimination of Tridiagonal Matrices
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 8.9. SPD Matrices and the Cholesky Decomposition
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 8.10. Reduced Row Echelon Form
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 8.11. RREF, Free Variables, Homogeneous Systems
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 8.12. Uniqueness of RREF
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 8.13. Solving Linear Systems Using RREF
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 8.14. Elementary Matrices and Columns Operations
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 8.15. Transvections and Dilatations
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 8.16. Summary
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 8.17. Problems
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 9. Vector Norms and Matrix Norms
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 9.1. Normed Vector Spaces
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 9.2. Matrix Norm
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 9.3. Subordinate Norms
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 9.4. Inequalities Involving Subordinate Norms
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 9.5. Condition Numbers of Matrices
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 9.6. An Application of Norms: Inconsistent Linear Systems
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 9.7. Limits of Sequences and Series
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 9.8. The Matrix Exponential
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 9.9. Summary
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 9.10. Problems
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 10. Iterative Methods for Solving Linear Systems
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 10.1. Convergence of Sequences of Vectors and Matrices
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 10.2. Convergence of Iterative Methods
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 10.3. Methods of Jacobi, Gauss–Seidel, and Relaxation
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 10.4. Convergence of the Methods
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 10.5. Convergence Methods for Tridiagonal Matrices
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 10.6. Summary
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 10.7. Problems
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 11. The Dual Space and Duality
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 11.1. The Dual Space E∗ and Linear Forms
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 11.2. Pairing and Duality Between E and E*
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 11.3. The Duality Theorem and Some Consequences
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 11.4. The Bidual and Canonical Pairings
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 11.5. Hyperplanes and Linear Forms
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 11.6. Transpose of a Linear Map and of a Matrix
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 11.7. Properties of the Double Transpose
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 11.8. The Four Fundamental Subspaces
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 11.9. Summary
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 11.10. Problems
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 12. Euclidean Spaces
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 12.1. Inner Products, Euclidean Spaces
}
\item [\checkbox]  Alebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 12.2. Orthogonality and Duality in Euclidean Spaces
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 12.3. Adjoint of a Linear Map
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 12.4. Existence and Construction of Orthonormal Bases
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 12.5. Linear Isometries (Orthogonal Transformations)
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 12.6. The Orthogonal Group, Orthogonal Matrices
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 12.7. The Rodrigues Formula
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 12.8. QR-Decomposition for Invertible Matrices
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 12.9. Some Applications of Euclidean Geometry
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 12.10. Summary
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 12.11. Problems
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 13. QR-Decomposition for Arbitrary Matrices
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 13.1. Orthogonal Reflections
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 13.2. QR-Decomposition Using Householder Matrices
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 13.3. Summary
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 13.4. Problems
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 14. Hermitian Spaces
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 14.1. Hermitian Spaces, Pre-Hilbert Spaces
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 14.2. Orthogonality, Duality, Adjoint of a Linear Map
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 14.3. Linear Isometries (Also Called Unitary Transformations)
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 14.4. The Unitary Group, Unitary Matrices
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 14.5. Hermitian Reflections and QR-Decomposition
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 14.6. Orthogonal Projections and Involutions
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 14.7. Dual Norms
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 14.8. Summary
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 14.9. Problems
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 15. Eigenvectors and Eigenvalues
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 15.1. Eigenvectors and Eigenvalues of a Linear Map
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 15.2. Reduction to Upper Triangular Form
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 15.3. Location of Eigenvalues
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 15.4. Conditioning of Eigenvalue Problems
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 15.5. Eigenvalues of the Matrix Exponential
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 15.6. Summary
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 15.7. Problems
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 16. Unit Quaternions and Rotations in SO(3
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 16.1. The Group SU(2) and the Skew Field H of Quaternions
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 16.2. Representation of Rotation in SO(3) By Quaternions in SU(2)
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 16.3. Matrix Representation of the Rotation rq
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 16.4. An Algorithm to Find a Quaternion Representing a Rotation
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 16.5. The Exponential Map exp: su(2) → SU(2)
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 16.6. Quaternion Interpolation
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 16.7. Nonexistence of a “Nice” Section from SO(3) to SU(2)
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 16.8. Summary
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 16.9. Problems
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 17. Spectral Theorems
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 17.1. Introduction
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 17.2. Normal Linear Maps: Eigenvalues and Eigenvectors
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 17.3. Spectral Theorem for Normal Linear Maps
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 17.4. Self-Adjoint and Other Special Linear Maps
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 17.5. Normal and Other Special Matrices
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 17.6. Rayleigh–Ritz Theorems and Eigenvalue Interlacing
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 17.7. The Courant–Fischer Theorem; Perturbation Results
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 17.8. Summary
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 17.9. Problems
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 18. Computing Eigenvalues and Eigenvectors
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 18.1. The Basic QR Algorithm
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 18.2. Hessenberg Matrices
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 18.3. Making the QR Method More Efficient Using Shifts
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 18.4. Krylov Subspaces; Arnoldi Iteration
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 18.5. GMRES
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 18.6. The Hermitian Case; Lanczos Iteration
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 18.7. Power Methods
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 18.8. Summary
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 18.9. Problems
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 19. Introduction to The Finite Elements Method
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 19.1. A One-Dimensional Problem: Bending of a Beam
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 19.2. A Two-Dimensional Problem: An Elastic Membrane
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 19.3. Time-Dependent Boundary Problems
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 20. Graphs and Graph Laplacians; Basic Facts
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 20.1. Directed Graphs, Undirected Graphs, Weighted Graphs
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 20.2. Laplacian Matrices of Graphs
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 20.3. Normalized Laplacian Matrices of Graphs
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 20.4. Graph Clustering Using Normalized Cuts
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 20.5. Summary
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 20.6. Problems
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 21. Spectral Graph Drawing
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 21.1. Graph Drawing and Energy Minimization
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 21.2. Examples of Graph Drawings
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 21.3. Summary
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 22. Singular Value Decomposition and Polar Form
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 22.1. Properties of f∗ ◦ f
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 22.2. Singular Value Decomposition for Square Matrices
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 22.3. Polar Form for Square Matrices
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 22.4. Singular Value Decomposition for Rectangular Matrices
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 22.5. Ky Fan Norms and Schatten Norms
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 22.6. Summary
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 22.7. Problems
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 23. Applications of SVD and Pseudo-Inverses
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 23.1. Least Squares Problems and the Pseudo-Inverse
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 23.2. Properties of the Pseudo-Inverse
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 23.3. Data Compression and SVD
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 23.4. Principal Components Analysis (PCA)
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 23.5. Best Affine Approximation
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 23.6. Summary
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 23.7. Problems
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 24. Basics of Affine Geometry
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 24.1. Affine Spaces
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 24.2. Examples of Affine Spaces
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 24.3. Chasles’s Identity
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 24.4. Affine Combinations, Barycenters
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 24.5. Affine Subspaces
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 24.6. Affine Independence and Affine Frames
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 24.7. Affine Maps
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 24.8. Affine Groups
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 24.9. Affine Geometry: A Glimpse
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 24.10. Affine Hyperplanes
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 24.11. Intersection of Affine Spaces
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 25. Embedding an Affine Space in a Vector Space
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 25.1. The “Hat Construction,” or Homogenizing
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 25.2. Affine Frames of E and Bases of Eˆ
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 25.3. Another Construction of Eˆ
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 25.4. Extending Affine Maps to Linear Maps
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 26. Basics of Projective Geometry
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 26.1. Why Projective Spaces?
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 26.2. Projective Spaces
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 26.3. Projective Subspaces
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 26.4. Projective Frames
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 26.5. Projective Maps
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 26.6. Finding a Homography Between Two Projective Frames
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 26.7. Affine Patches
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 26.8. Projective Completion of an Affine Space
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 26.9. Making Good Use of Hyperplanes at Infinity
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 26.10. The Cross-Ratio
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 26.11. Fixed Points of Homographies and Homologies
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 26.12. Duality in Projective Geometry
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 26.13. Cross-Ratios of Hyperplanes
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 26.14. Complexification of a Real Projective Space
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 26.15. Similarity Structures on a Projective Space
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 26.16. Some Applications of Projective Geometry
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 27. The Cartan–Dieudonné Theorem
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 27.1. The Cartan–Dieudonné Theorem for Linear Isometries
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 27.2. Affine Isometries (Rigid Motions)
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 27.3. Fixed Points of Affine Maps
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 27.4. Affine Isometries and Fixed Points
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 27.5. The Cartan–Dieudonné Theorem for Affine Isometries
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 28. Isometries of Hermitian Spaces
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 28.1. The Cartan–Dieudonné Theorem, Hermitian Case
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 28.2. Affine Isometries (Rigid Motions
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 29. The Geometry of Bilinear Forms; Witt’s Theorem
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 29.1. Bilinear Forms
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 29.2. Sesquilinear Forms
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 29.3. Orthogonality
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 29.4. Adjoint of a Linear Map
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 29.5. Isometries Associated with Sesquilinear Forms
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 29.6. Totally Isotropic Subspaces
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 29.7. Witt Decomposition.992
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 29.8. Symplectic Groups000
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 29.9. Orthogonal Groups and the Cartan–Dieudonné Theorem
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 29.10. Witt’s Theorem
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 30. Polynomials, Ideals and PID’s
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 30.1. Multisets
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 30.2. Polynomials
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 30.3. Euclidean Division of Polynomials
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 30.4. Ideals, PID’s, and Greatest Common Divisors
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 30.5. Factorization and Irreducible Factors in K[X]
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 30.6. Roots of Polynomials
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 30.7. Polynomial Interpolation (Lagrange, Newton, Hermite)
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 31. Annihilating Polynomials; Primary Decomposition
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 31.1. Annihilating Polynomials and the Minimal Polynomial
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 31.2. Minimal Polynomials of Diagonalizable Linear Maps
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 31.3. Commuting Families of Linear Maps
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 31.4. The Primary Decomposition Theorem
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 31.5. Jordan Decomposition
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 31.6. Nilpotent Linear Maps and Jordan Form
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 31.7. Summary
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 31.8. Problems
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 32. UFD’s, Noetherian Rings, Hilbert’s Basis Theorem
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 32.1. Unique Factorization Domains (Factorial Rings)
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 32.2. The Chinese Remainder Theorem
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 32.3. Noetherian Rings and Hilbert’s Basis Theorem
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 32.4. Futher Readings
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 33. Tensor Algebras
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 33.1. Linear Algebra Preliminaries: Dual Spaces and Pairings
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 33.2. Tensors Products
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 33.3. Bases of Tensor Products
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 33.4. Some Useful Isomorphisms for Tensor Products
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 33.5. Duality for Tensor Products
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 33.6. Tensor Algebras
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 33.7. Symmetric Tensor Powers
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 33.8. Bases of Symmetric Powers
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 33.9. Some Useful Isomorphisms for Symmetric Powers
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 33.10. Duality for Symmetric Powers
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 33.11. Symmetric Algebras
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 33.12. Problems
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 34. Exterior Tensor Powers and Exterior Algebras
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 34.1. Exterior Tensor Powers
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 34.2. Bases of Exterior Powers
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 34.3. Some Useful Isomorphisms for Exterior Powers
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 34.4. Duality for Exterior Powers
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 34.5. Exterior Algebras
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 34.6. The Hodge ∗-Operator
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 34.7. Left and Right Hooks
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 34.8. Testing Decomposability
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 34.9. The Grassmann-Plücker’s Equations and Grassmannians
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 34.10. Vector-Valued Alternating Forms
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 34.11. Problems
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 35. Introduction to Modules; Modules over a PID
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 35.1. Modules over a Commutative Ring
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 35.2. Finite Presentations of Modules
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 35.3. Tensor Products of Modules over a Commutative Ring
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 35.4. Torsion Modules over a PID; Primary Decomposition
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 35.5. Finitely Generated Modules over a PID
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 35.6. Extension of the Ring of Scalars
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 36. Normal Forms; The Rational Canonical Form
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 36.1. The Torsion Module Associated With An Endomorphism
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 36.2. The Rational Canonical Form
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 36.3. The Rational Canonical Form, Second Version
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 36.4. The Jordan Form Revisited
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 36.5. The Smith Normal Form
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 37. Topology
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 37.1. Metric Spaces and Normed Vector Spaces
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 37.2. Topological Spaces
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 37.3. Continuous Functions, Limits
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 37.4. Connected Sets
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 37.5. Compact Sets and Locally Compact Spaces
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 37.6. Second-Countable and Separable Spaces
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 37.7. Sequential Compactness
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 37.8. Complete Metric Spaces and Compactness
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 37.9. Completion of a Metric Space
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 37.10. The Contraction Mapping Theorem
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 37.11. Continuous Linear and Multilinear Maps
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 37.12. Completion of a Normed Vector Space
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 37.13. Normed Affine Spaces
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 37.14. Futher Readings
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 38. A Detour On Fractals
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 38.1. Iterated Function Systems and Fractals
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 39. Differential Calculus
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 39.1. Directional Derivatives, Total Derivatives
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 39.2. Jacobian Matrices
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 39.3. The Implicit and The Inverse Function Theorems
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 39.4. Tangent Spaces and Differentials
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 39.5. Second-Order and Higher-Order Derivatives
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 39.6. Taylor’s formula, Faà di Bruno's Formula 
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 39.7. Vector Fields, Covariant Derivatives, Lie Brackets
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 39.8. Futher Readings
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 40. Extrema of Real-Valued Functions
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 40.1. Local Extrema and Lagrange Multipliers
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 40.2. Using Second Derivatives to Find Extrema
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 40.3. Using Convexity to Find Extrema
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 40.4. Summary
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 41. Newton’s Method and Its Generalizations
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 41.1. Newton’s Method for Real Functions of a Real Argument
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 41.2. Generalizations of Newton’s Method
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 41.3. Summary
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 42. Quadratic Optimization Problems
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 42.1. Quadratic Optimization: The Positive Definite Case
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 42.2. Quadratic Optimization: The General Case
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 42.3. Maximizing a Quadratic Function on the Unit Sphere
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 42.4. Summary
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 43. Schur Complements and Applications
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 43.1. Schur Complements
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 43.2. SPD Matrices and Schur Complements
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 43.3. SP Semidefinite Matrices and Schur Complements
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 44. Convex Sets, Cones, H-Polyhedra
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 44.1. What is Linear Programming?
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 44.2. Affine Subsets, Convex Sets, Hyperplanes, Half-Spaces
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 44.3. Cones, Polyhedral Cones, and H-Polyhedra
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 45. Linear Programs
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 45.1. Linear Programs, Feasible Solutions, Optimal Solutions
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 45.2. Basic Feasible Solutions and Vertices
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 46. The Simplex Algorithm
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 46.1. The Idea Behind the Simplex Algorithm
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 46.2. The Simplex Algorithm in General
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 46.3. How to Perform a Pivoting Step Efficiently
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 46.4. The Simplex Algorithm Using Tableaux
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 46.5. Computational Efficiency of the Simplex Method
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 47. Linear Programming and Duality
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 47.1. Variants of the Farkas Lemma
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 47.2. The Duality Theorem in Linear Programming
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 47.3. Complementary Slackness Conditions
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 47.4. Duality for Linear Programs in Standard Form
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 47.5. The Dual Simplex Algorithm
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 47.6. The Primal-Dual Algorithm
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 48. Basics of Hilbert Spaces
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 48.1. The Projection Lemma, Duality
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 48.2. Farkas–Minkowski Lemma in Hilbert Spaces
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 49. General Results of Optimization Theory
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 49.1. Optimization Problems; Basic Terminology
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 49.2. Existence of Solutions of an Optimization Problem
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 49.3. Minima of Quadratic Functionals
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 49.4. Elliptic Functionals
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 49.5. Iterative Methods for Unconstrained Problems
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 49.6. Gradient Descent Methods for Unconstrained Problems
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 49.7. Convergence of Gradient Descent with Variable Stepsize
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 49.8. Steepest Descent for an Arbitrary Norm
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 49.9. Newton’s Method For Finding a Minimum
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 49.10. Conjugate Gradient Methods; Unconstrained Problems
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 49.11. Gradient Projection for Constrained Optimization
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 49.12. Penalty Methods for Constrained Optimization
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 49.13. Summary
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 50. Introduction to Nonlinear Optimization
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 50.1. The Cone of Feasible Directions
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 50.2. Active Constraints and Qualified Constraints
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 50.3. The Karush–Kuhn–Tucker Conditions
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 50.4. Equality Constrained Minimization
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 50.5. Hard Margin Support Vector Machine; Version I
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 50.6. Hard Margin Support Vector Machine; Version II
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 50.7. Lagrangian Duality and Saddle Points
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 50.8. Weak and Strong Duality
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 50.9. Handling Equality Constraints Explicitly
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 50.10. Dual of the Hard Margin Support Vector Machines
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 50.11. Conjugate Function and Legendre Dual Function
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 50.12. Some Techniques to Obtain a More Useful Dual Program
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 50.13. Uzawa’s Method
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 50.14. Summary
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 51. Subgradients and Subdifferentials
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 51.1. Extended Real-Valued Convex Functions
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 51.2. Subgradients and Subdifferentials
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 51.3. Basic Properties of Subgradients and Subdifferentials
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 51.4. Additional Properties of Subdifferentials
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 51.5. The Minimum of a Proper Convex Function
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 51.6. Generalization of the Lagrangian Framework
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 51.7. Summary
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 52. Dual Ascent Methods; ADMM
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 52.1. Dual Ascent
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 52.2. Augmented Lagrangians and the Method of Multipliers
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 52.3. ADMM: Alternating Direction Method of Multipliers
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 52.4. Convergence of ADMMs
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 52.5. Stopping Criteria
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 52.6. Some Applications of ADMM
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 52.7. Applications of ADMM to L1-Norm Problems
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 52.8. Summary
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 53. Ridge Regression and Lasso Regression
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 53.1. Ridge Regression
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 53.2. Lasso Regression L1-Regularized Regression)
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 53.3. Summary
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 54. Positive Definite Kernels
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 54.1. Basic Properties of Positive Definite Kernels
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 54.2. Hilbert Space Representation of a Positive Kernel
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 54.3. Kernel PCA
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 54.4. ν-SV Regression
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 55. Soft Margin Support Vector Machines
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 55.1. Soft Margin Support Vector Machines; (SVMs1)
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 55.2. Soft Margin Support Vector Machines; (SVMs2)
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 55.3. Soft Margin Support Vector Machines; (SVMs2)
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 55.4. Soft Margin SVM; (SVMs3)
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 55.5. Soft Margin Support Vector Machines; (SVMs4)
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 55.6. Soft Margin SVM; (SVMs5)
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ 55.7. Summary and Comparison of the SVM Methods
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ A. Total Orthogonal Families in Hilbert Spaces
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ A.1. Total Orthogonal Families, Fourier Coefficients
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ A.2. The Hilbert Space2 (K) and the Riesz-Fischer Theorem
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ B. Zorn’s Lemma; Some Applications
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ B.1. Statement of Zorn’s Lemma.
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ B.2. Proof of the Existence of a Basis in a Vector Space
}
\item [\checkbox]  Algebra, Topology, Differential Calculus, and Optimization Theory for Computer Science and Machine Learning \textbf{ B.3. Existence of Maximal Proper Ideals
}
\item [\checkbox]  Spark: The Definitive Guide (Chambers & Zaharia) \textbf{ 1. What Is Apache Spark?
}
\item [\checkbox]  Spark: The Definitive Guide (Chambers & Zaharia) \textbf{ 2. A Gentle Introduction to Spark
}
\item [\checkbox]  Spark: The Definitive Guide (Chambers & Zaharia) \textbf{ 3. A Tour of Spark’s Toolset
}
\item [\checkbox]  Spark: The Definitive Guide (Chambers & Zaharia) \textbf{ 4. Structured API Overview
}
\item [\checkbox]  Spark: The Definitive Guide (Chambers & Zaharia) \textbf{ 5. Basic Structured Operations
}
\item [\checkbox]  Spark: The Definitive Guide (Chambers & Zaharia) \textbf{ 6. Working with Different Types of Data
}
\item [\checkbox]  Spark: The Definitive Guide (Chambers & Zaharia) \textbf{ 7. Aggregations
}
\item [\checkbox]  Spark: The Definitive Guide (Chambers & Zaharia) \textbf{ 8. Joins
}
\item [\checkbox]  Spark: The Definitive Guide (Chambers & Zaharia) \textbf{ 9. Data Sources
}
\item [\checkbox]  Spark: The Definitive Guide (Chambers & Zaharia) \textbf{ 10. Spark SQL
}
\item [\checkbox]  Spark: The Definitive Guide (Chambers & Zaharia) \textbf{ 11. Datasets
}
\item [\checkbox]  Spark: The Definitive Guide (Chambers & Zaharia) \textbf{ 12. Resilient Distributed Datasets (RDDs)
}
\item [\checkbox]  Spark: The Definitive Guide (Chambers & Zaharia) \textbf{ 13. Advanced RDDs
}
\item [\checkbox]  Spark: The Definitive Guide (Chambers & Zaharia) \textbf{ 14. Distributed Shared Variables
}
\item [\checkbox]  Spark: The Definitive Guide (Chambers & Zaharia) \textbf{ 15. How Spark Runs on a Cluster
}
\item [\checkbox]  Spark: The Definitive Guide (Chambers & Zaharia) \textbf{ 16. Developing Spark Applications
}
\item [\checkbox]  Spark: The Definitive Guide (Chambers & Zaharia) \textbf{ 17. Deploying Spark
}
\item [\checkbox]  Spark: The Definitive Guide (Chambers & Zaharia) \textbf{ 18. Monitoring and Debugging
}
\item [\checkbox]  Spark: The Definitive Guide (Chambers & Zaharia) \textbf{ 19. Performance Tuning
}
\item [\checkbox]  Spark: The Definitive Guide (Chambers & Zaharia) \textbf{ 20. Stream Processing Fundamentals
}
\item [\checkbox]  Spark: The Definitive Guide (Chambers & Zaharia) \textbf{ 21. Structured Streaming Basics
}
\item [\checkbox]  Spark: The Definitive Guide (Chambers & Zaharia) \textbf{ 22. Event-Time and Stateful Processing
}
\item [\checkbox]  Spark: The Definitive Guide (Chambers & Zaharia) \textbf{ 23. Structured Streaming in Production
}
\item [\checkbox]  Spark: The Definitive Guide (Chambers & Zaharia) \textbf{ 24. Advanced Analytics and Machine Learning Overview
}
\item [\checkbox]  Spark: The Definitive Guide (Chambers & Zaharia) \textbf{ 25. Preprocessing and Feature Engineering
}
\item [\checkbox]  Spark: The Definitive Guide (Chambers & Zaharia) \textbf{ 26. Classification
}
\item [\checkbox]  Spark: The Definitive Guide (Chambers & Zaharia) \textbf{ 27. Regression
}
\item [\checkbox]  Spark: The Definitive Guide (Chambers & Zaharia) \textbf{ 28. Recommendation
}
\item [\checkbox]  Spark: The Definitive Guide (Chambers & Zaharia) \textbf{ 29. Unsupervised Learning
}
\item [\checkbox]  Spark: The Definitive Guide (Chambers & Zaharia) \textbf{ 30. Graph Analytics
}
\item [\checkbox]  Spark: The Definitive Guide (Chambers & Zaharia) \textbf{ 31. Deep Learning
}
\item [\checkbox]  Spark: The Definitive Guide (Chambers & Zaharia) \textbf{ 32. Language Specifics: Python (PySpark) and R (SparkR and sparklyr)
}
\item [\checkbox]  Spark: The Definitive Guide (Chambers & Zaharia) \textbf{ 33. Ecosystem and Community
}
\item [\checkbox]  Using MPI: Portable Parallel Programming with the Message-Passing Interface by (Gropp, Lusk, and Skjellum) \textbf{ 1. Background
}
\item [\checkbox]  Using MPI: Portable Parallel Programming with the Message-Passing Interface by (Gropp, Lusk, and Skjellum) \textbf{ 2. Introduction to MPI
}
\item [\checkbox]  Using MPI: Portable Parallel Programming with the Message-Passing Interface by (Gropp, Lusk, and Skjellum) \textbf{ 3. Using MPI in Simple Programs
}
\item [\checkbox]  Using MPI: Portable Parallel Programming with the Message-Passing Interface by (Gropp, Lusk, and Skjellum) \textbf{ 4. Intermediate MPI
}
\item [\checkbox]  Using MPI: Portable Parallel Programming with the Message-Passing Interface by (Gropp, Lusk, and Skjellum) \textbf{ 5. Advanced Message Passing in MPI
}
\item [\checkbox]  Using MPI: Portable Parallel Programming with the Message-Passing Interface by (Gropp, Lusk, and Skjellum) \textbf{ 6. Parallel Libraries
}
\item [\checkbox]  Using MPI: Portable Parallel Programming with the Message-Passing Interface by (Gropp, Lusk, and Skjellum) \textbf{ 7. Other Features of MPI
}
\item [\checkbox]  Using MPI: Portable Parallel Programming with the Message-Passing Interface by (Gropp, Lusk, and Skjellum) \textbf{ 8. Understanding how MPI Implementations Work
}
\item [\checkbox]  Using MPI: Portable Parallel Programming with the Message-Passing Interface by (Gropp, Lusk, and Skjellum) \textbf{ 9. Comparing MPI with Other Systems for Interprocess Communication
}
\item [\checkbox]  Using MPI: Portable Parallel Programming with the Message-Passing Interface by (Gropp, Lusk, and Skjellum) \textbf{ 10. Beyond Message Passing
}
\item [\checkbox]  Using MPI: Portable Parallel Programming with the Message-Passing Interface by (Gropp, Lusk, and Skjellum) \textbf{ 0. Glossary of Selected Terms
}
\item [\checkbox]  Using MPI: Portable Parallel Programming with the Message-Passing Interface by (Gropp, Lusk, and Skjellum) \textbf{ A. Summary of MPI-1 Routines and Their Arguments
}
\item [\checkbox]  Using MPI: Portable Parallel Programming with the Message-Passing Interface by (Gropp, Lusk, and Skjellum) \textbf{ B. The MPICH Implementation of MPI
}
\item [\checkbox]  Using MPI: Portable Parallel Programming with the Message-Passing Interface by (Gropp, Lusk, and Skjellum) \textbf{ C. The MPE Multiprocessing Environment
}
\item [\checkbox]  Using MPI: Portable Parallel Programming with the Message-Passing Interface by (Gropp, Lusk, and Skjellum) \textbf{ D. MPI Resources on the World Wide Web
}
\item [\checkbox]  Using MPI: Portable Parallel Programming with the Message-Passing Interface by (Gropp, Lusk, and Skjellum) \textbf{ E. Language Details
}
\item [\checkbox]  Programming Massively Parallel Processors (Kirk and Hwu) \textbf{ 1. Introduction
}
\item [\checkbox]  Programming Massively Parallel Processors (Kirk and Hwu) \textbf{ 2. Data parallel computing
}
\item [\checkbox]  Programming Massively Parallel Processors (Kirk and Hwu) \textbf{ 3. Scalable parallel execution
}
\item [\checkbox]  Programming Massively Parallel Processors (Kirk and Hwu) \textbf{ 4. Memory and data locality
}
\item [\checkbox]  Programming Massively Parallel Processors (Kirk and Hwu) \textbf{ 5. Performance considerations
}
\item [\checkbox]  Programming Massively Parallel Processors (Kirk and Hwu) \textbf{ 6. Numerical considerations
}
\item [\checkbox]  Programming Massively Parallel Processors (Kirk and Hwu) \textbf{ 7. Parallel patterns: convolution: An introduction to stencil computation
}
\item [\checkbox]  Programming Massively Parallel Processors (Kirk and Hwu) \textbf{ 8. Parallel patterns: prefix sum: An introduction to work efficiency in parallel algorithms
}
\item [\checkbox]  Programming Massively Parallel Processors (Kirk and Hwu) \textbf{ 9. Parallel patterns—parallel histogram computation: An introduction to atomic operations and privatization
}
\item [\checkbox]  Programming Massively Parallel Processors (Kirk and Hwu) \textbf{ 10. Parallel patterns: sparse matrix computation: An introduction to data compression and regularization
}
\item [\checkbox]  Programming Massively Parallel Processors (Kirk and Hwu) \textbf{ 11. Parallel patterns: merge sort: An introduction to tiling with dynamic input data identification
}
\item [\checkbox]  Programming Massively Parallel Processors (Kirk and Hwu) \textbf{ 12. Parallel patterns: graph search
}
\item [\checkbox]  Programming Massively Parallel Processors (Kirk and Hwu) \textbf{ 13. CUDA dynamic parallelism
}
\item [\checkbox]  Programming Massively Parallel Processors (Kirk and Hwu) \textbf{ 14. Application case study—non-
}
\item [\checkbox]  Cartesian magnetic resonance imaging: An introduction to statistical estimation methods
\item [\checkbox] Programming Massively Parallel Processors (Kirk and Hwu) \textbf{ 15. Application case study—molecular visualization and analysis
}
\item [\checkbox]  Programming Massively Parallel Processors (Kirk and Hwu) \textbf{ 16. Application case study—machine learning
}
\item [\checkbox]  Programming Massively Parallel Processors (Kirk and Hwu) \textbf{ 17. Parallel programming and computational thinking
}
\item [\checkbox]  Programming Massively Parallel Processors (Kirk and Hwu) \textbf{ 18. Programming a heterogeneous computing cluster
}
\item [\checkbox]  Programming Massively Parallel Processors (Kirk and Hwu) \textbf{ 19. Parallel programming with OpenACC
}
\item [\checkbox]  Programming Massively Parallel Processors (Kirk and Hwu) \textbf{ 20. More on CUDA and graphics processing unit computing
}
\item [\checkbox]  Programming Massively Parallel Processors (Kirk and Hwu) \textbf{ 21. Conclusion and outlook
}
\item [\checkbox]  Programming Massively Parallel Processors (Kirk and Hwu) \textbf{ A. An introduction to OpenCL
}
\item [\checkbox]  Programming Massively Parallel Processors (Kirk and Hwu) \textbf{ B. THRUST: a productivity-oriented library for CUDA
}
\item [\checkbox]  Programming Massively Parallel Processors (Kirk and Hwu) \textbf{ C. CUDA Fortran
}
\item [\checkbox]  Programming Massively Parallel Processors (Kirk and Hwu) \textbf{ D. An introduction to C++ AMP
}
\item [\checkbox]  Programming Massively Parallel Processors (Kirk and Hwu) \textbf{ 0. Introduction
}
\item [\checkbox]  CUDA for Engineers (Storti & Yurtoglu) \textbf{ 1. First Steps
}
\item [\checkbox]  CUDA for Engineers (Storti & Yurtoglu) \textbf{ 3. From Loops to Grids
}
\item [\checkbox]  CUDA for Engineers (Storti & Yurtoglu) \textbf{ 4. 2D Grids and Interactive Graphics
}
\item [\checkbox]  CUDA for Engineers (Storti & Yurtoglu) \textbf{ 5. Stencils and Shared Memory
}
\item [\checkbox]  CUDA for Engineers (Storti & Yurtoglu) \textbf{ 6. Reduction and Atomic Functions
}
\item [\checkbox]  CUDA for Engineers (Storti & Yurtoglu) \textbf{ 7. Interacting with 3D Data
}
\item [\checkbox]  CUDA for Engineers (Storti & Yurtoglu) \textbf{ 8. Using CUDA Libraries
}
\item [\checkbox]  CUDA for Engineers (Storti & Yurtoglu) \textbf{ 9. Exploring the CUDA Ecosystem
}
\item [\checkbox]  CUDA for Engineers (Storti & Yurtoglu) \textbf{ A. Hardware Setup
}
\item [\checkbox]  CUDA for Engineers (Storti & Yurtoglu) \textbf{ B. Software Setup
}
\item [\checkbox]  CUDA for Engineers (Storti & Yurtoglu) \textbf{ C. Need-to-Know C Programming
}
\item [\checkbox]  CUDA for Engineers (Storti & Yurtoglu) \textbf{ D. CUDA Practicalities. Timing, Profiling, Error Handling, and Debugging
}
\end{itemize}
\end{document}